### 2014-12-10 latex-style-files-spie-manuscript/article.tex
Glory is fleeting, but obscurity is forever.
said Napoleon Bonaparte

%  article.tex (Version 1.00, released 1 October 2013)
%  LaTeX source file to demonstrate formatting for manuscripts 
%  to be submitted to SPIE journals
%  based on the class file spieman.cls, which requires 
%  the following standard packages:  times.sty, float.sty, 
%  ifthen.sty, cite.sty, color.sty, setspace.sty
%
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, for example, to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class 
%  file (spieman.cls) and may not be understood in other classes:
%  \affiliations{}, \sup{},\supit{}, \authorinfo{}, \keywords{},
%  \linkable and \video
%  The bibliography style file is called spiejour.bst 
%  This article.tex file needs the following image files:
%  mcr3b.eps
%  fig2.eps
%  satellite.eps

%%\documentclass[12pt]{spieman}  %>>> 12pt font mandatory; use this for US letter paper 
\documentclass[a4paper,12pt]{spieman}  %>>> use this instead for A4 paper
%%\documentclass[nocompress,12pt]{spieman}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  for example, [dvips], but that may be inappropriate for some LaTeX installations. 
%%\usepackage{amsmath}  %>>> for AMS math formatting, 
%  including bold Greek symbols
\usepackage[]{graphicx}
\usepackage{setspace}
\usepackage{tocloft}

\title{Working title: the most amazzing SPIM and how we built it}

%>>>> The author is responsible for formatting the 
%  author list and their affiliations.  Use \\ to force linebreaks.
%  The correspondence between each author and his/her address
%  can be indicated with a superscript, 
%  which is easily obtained with \supscr{}.
%>>>> After the abstract, the author must include
%  a list of keywords and contact information for the corresponding author.

\author{First Author,\supscr{a} Second Author,\supscr{a} Third Author,\supscr{b} Fourth Author\supscr{a,b}}

\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy, University of Florence, Via Nello Carrara,1, Sesto Fiorentino (Firenze), Italy, 50019\\
\supscrsm{b}National Institute of Optics, National Research Council, Italy\\
\supscrsm{c}Department of Physics and Astronomy, University of Florence, Via Giovanni Sansone, 1, Sesto Fiorentino (Firenze), Italy, 50019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document} 
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
200 words limit. It should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting and indexing databases, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period. The body of the manuscript should be double-spaced and fully justified.   
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

%>>>> Include contact information for corresponding author
{\noindent \footnotesize{\bf Address all correspondence to}: First author, University Name, Faculty Group, Department, Street Address, City, Country, Postal Code; Tel: +1 555-555-5555; Fax: +1 555-555-5556; E-mail:  \linkable{myemail@university.edu} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{spacing}{2}   % use double spacing for rest of manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sect:intro}  % \label{} allows reference to this section
This document shows the required format and appearance of a manuscript prepared for SPIE journals. Formatting guidelines must be carefully followed. Authors are advised to print this sample manuscript and use it as a reference while preparing their own paper, to ensure all guidelines are met.

%%-----------------------------------------------------------
\subsection{Use of This Document}

This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.  The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it. Authors may use it as a template to create their own manuscript. While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.

%%-----------------------------------------------------------
\subsection{English}

Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example. In addition, good English usage is essential. Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced. Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{http://spie.org/EnglishEditing}. SPIE authors will receive a 10\% discount off their services. A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission. Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.

%%-----------------------------------------------------------
\subsection{Page Setup and Fonts}

All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US letter paper, on which the margins should be 1.0 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in\ on the left and right.

The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}. If this font is not available, use a similar serif font. The manuscript should not contain headers or footers. Pages should be numbered.

%% Use of [h] in following command forces table to appear "here", instead of a top or bottom of page, which is generally preferred.
\begin{table}[h]
\caption{Fonts sizes and styles.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
\hline\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
\hline 
\end{tabular}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parts of Manuscript}

This section describes the normal structure of a manuscript and how each part should be handled. The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.

%%-----------------------------------------------------------
\subsection{Title and Author Information} 
\label{sect:title}
The article title appears left justified at the top of the first page. The title font is 16 pt., bold. The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized. Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.). The word “novel” should not appear in the title, as publication will imply novelty. Avoid the use of acronyms in the title, unless they are widely understood. Appendix A contains more about acronyms.

The list of authors immediately follows the title, 18 points below. The font is 12 pt., bold and the author names are left justified. The author affiliations and addresses follow the names, in 10-pt., normal font and left justified. For multiple affiliations, each affiliation should appear on a separate line. Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations. Corresponding author should be listed below the Keywords, following the line ``Address all correspondence to:"; include mailing address, telephone, fax, and E-mail address.

%%-----------------------------------------------------------
\subsection{Abstract} 
The abstract should be a concise summary of the paper. Because the abstract may be used in abstracting journals, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. It should not exceed 200 words. For further guidelines, please read the brief article titled ``How to Write an Abstract (PDF)," \\(\linkable{http://spie.org/Documents/Publications/How to Write an Abstract.pdf}) by Philip Koopman. (Courtesy of Philip Koopman, Carnegie Mellon University.) Note the underlined link must be written on a single line in order for the link to function. Thus, a break in the line, created with {\verb+\\+} is required before the link or the preceding text should be editted to gracefully place the link on a single line. This type of adjustment is best done at end of the manuscript-preparation process.

%%-----------------------------------------------------------
\subsection{Keywords} 
Up to eight keywords should be specified.

%%-----------------------------------------------------------
\subsection{Body of Paper} 
The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.

To provide transition elements in your paper, it is important to refer back (or forward) to specific sections. Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed..." or ``Section 2.1 contained a description..." If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out. When occurring in the middle of a sentence, these words are abbreviated Sect., Ref., Eq., and Fig.

At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).

%%-----------------------------------------------------------
\subsection{Footnotes} 
Use textual footnotes only when necessary to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should be avoided. If absolutely necessary, the footnote mark must come at the end of a sentence. To insert a footnote, use the {\verb|\footnote{}|} command.

%%-----------------------------------------------------------
\subsection{Appendices} 
SPIE journals do not accept supplementary materials. However, it is acceptable to include an Appendix when necessary,  details such as derivations of equations, proofs of theorems, and details of algorithms. Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.

%%-----------------------------------------------------------
\subsection{Acknowledgments} 
In the acknowledgments section, which appears just before the references, the authors may credit others for their guidance or help. Also, funding sources or sponsorship information may be stated. The acknowledgments section does not have a section number.

%%-----------------------------------------------------------
\subsection{References} 
The References section lists books, articles, and reports that are cited in the paper. This section does not have a section number. The references are numbered in the order in which they are cited. Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.  Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

The references are numbered in the order of their first citation. Citations to the references are made using superscripts, as demonstrated in the preceding paragraph. One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ..."  Two or more references should be separated by a comma with no space between them. Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.

%%---------------------------
\subsubsection{Reference linking and DOIs} 
A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet. The use of DOIs allows readers to easily access cited articles. Authors should include the DOI at the end of each reference in brackets, if a DOI is available. See examples at the end of this manuscript. A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}. The inclusion of DOIs will facilitate reference linking and is highly recommended.

In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note" in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}. The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.

%%-----------------------------------------------------------
\subsection{Biographies} 
A brief professional biography not to exceed 75 words may be provided for each author, if available. Biographies should be placed at the end of the paper, after the references. Personal information such as hobbies or birthplace/birthdate should not be included. Author photographs are not published.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Section Formatting} \label{sect:sections}

In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections. Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references. (Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.

Main section headings are in 12-pt., bold font, left-justified and in title case, where important words are capitalized.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style. The same goes for leading paragraphs of subsections and sub-subsections. Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation. There is no additional space between paragraphs. In LaTeX, paragraphs are separated by blank lines in the source file. Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

%%-----------------------------------------------------------
\subsection{Subsection Headings} 
All important words in a subsection (level 1) header are capitalized. Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end. The heading is left justified and its font is 12 pt., italic.

%%-----------
\subsubsection{Sub-subsection headings} 
The first word of a sub-subsection is capitalized. The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known). The heading is left justified and its font is 11 pt., italic.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Figures and Tables}

%%-----------------------------------------------------------
\subsection{Figures}

Figures are numbered in the order in which they are called out in the text. They should appear in the document in numerical order and as close as possible to their first reference in the text. It may be necessary to move figures or tables around to enhance readability. LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.

Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered. Figure captions are centered below the figure or graph. Figure captions start with the abbreviation ``Fig" in front of the figure number, followed by a period, and the text in 10-pt. font. See Fig.~\ref{fig:example} for an example.

%%  Use following command to specify that graphics file is in 
%%  a directory other than this LaTeX source file.
%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=5.5cm]{mcr3b.eps}
   \end{tabular}
   \end{center}
   \caption 
   { \label{fig:example} %>> use \label inside caption to get Fig. number with \ref{}
Example of a figure caption. } 
   \end{figure} 
%-------------
Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.  In no case, should the article's text be wrapped around a figure. Figure~\ref{fig:example2} shows two side-by-side images. When a figure contains more than one image, the author must submit them as a single image file. Further details about figure formatting can be found at \linkable{http://spie.org/x85020.xml
\#Components}.

%------------- 
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
     \\
     (a) \hspace{5.1cm} (b)
   \end{tabular}
   \end{center}
   \caption 
   { \label{fig:example2} %>> use \label inside caption to get Fig. number with \ref{}
Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
   \end{figure}

%-------------%%-----------------------------------------------------------
\subsection{Tables} 
Tables are numbered in the order in which they are referenced. They should appear in the document in numerical order and as close as possible to their first reference in the text. It is preferable to have tables appear at the top or bottom of the page, if possible. Table captions are handled identically to those for figures, except that they appear above the table. See Table~\ref{tab:fonts} for an example.
%%-----------------------------------------------------------

\subsection{Multimedia} 
Please refer to the multimedia guidelines at \linkable{http://spie.org/x85020.xml\#Multimedia} for specific submission guidelines and requirements. The following types of multimedia files are accepted: QuickTime Non-Streaming video (.qt or .mov), MPEG (.mpg or .mp4). The recommended maximum size for each multimedia file is 10-12 MB. Authors must insert a representative “still” image from the video file in the manuscript as a “figure.” This still image will be linked by the publisher to the actual video file, as will the caption label. Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures. Otherwise  The multimedia file type should be included in parentheses at the end of the figure caption, along with the file size. See Video \ref{vid:satellite} for an example.

%-------------
   \begin{video}
   \begin{center}
   {\includegraphics[height=5cm]{satellite.eps}}
   \\
   \end{center}
   \caption{\label{vid:satellite} Example of a multimedia still image (MPEG, 2.5 MB).}
   \end{video} 
%-------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix    %>>>> this command starts appendixes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Miscellaneous Formatting Details} \label{sect:misc}

At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.

%%-----------------------------------------------
\subsection{Formatting Equations} 
Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the field of view is
	\begin{equation}
	\label{eq:fov}
2 a = \frac{(b + 1)}{3c} \, ,
	\end{equation}
where $a$ is the ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma appears after the equation because the next line is a subordinate clause. If the equation ends the sentence, a period should follow the equation. The line following an equation should not be indented unless it is meant to start a new paragraph. Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..." Note that the word ``Equation" is spelled out if it begins a sentence, but is abbreviated as ``Eq." otherwise. Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq." and the following equation number..

%%-----------------------------------------------------------
\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.  The text of the theorem continues on the same line in normal, 10-pt. font, achieved in LaTeX using \verb|\footnotesize|.  For example,

\vspace{2ex}\noindent{\footnotesize{\bf Theorem 1.} For any unbiased estimator...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Some LaTeX Guidance} \label{sect:latex}

To work properly, the LaTeX style file {\ttfamily spieman.cls} used to create this document requires following LaTeX packages:
{\ttfamily times.sty}, {\ttfamily float.sty}, {\ttfamily ifthen.sty}, {\ttfamily setspace.sty}, \\{\ttfamily cite.sty} (version 4.01 or later), and {\ttfamily color.sty}. If you do not have them in your LaTeX environment, see your system manager, or download them from \linkable{http://www.ctan.org}.

The author is required to make sure his or her manuscript is properly formatted. LaTeX sometimes needs some help to avoid making gross formatting blunders. The source file for this document provides examples of how to cope with some of LaTeX's shortcomings.

%%-----------------------------------------------------------
\subsection{Margins and PostScript Fonts}

Manuscripts submitted for SPIE journals as Portable Document Format (PDF) files must be formatted for US-letter-size paper and have the correct margins. The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.

One may directly create a PDF file from the DVI file with the LaTeX utility {\ttfamily dvipdfm}, for example. No options are necessary. Appealing aspects of this utility are that Acrobat Distiller is not needed, and Type 1 PostScript fonts are automatically included in the resulting PDF file.  Furthermore, {\ttfamily dvipdfm} allows one to directly incorporate images in JPEG, PNG, and PDF formats, and not just EPS, which is normally used with LaTeX.

Alternatively, with an application such as Adobe Acrobat, PDF files can be created from PostScript (PS) files, which can be produced by DVIPS. In most cases, the following DVIPS options should be invoked.

An important DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file. This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.  The option ``{\ttfamily -P pdf}" makes DVIPS include these fonts in its output PS file.

LaTeX margins are related to the document's paper size. The paper size is set at two separate places in the process of creating a PS file. The first place is in {\ttfamily latex}. 
The second place is in the application DVIPS. DVIPS has its own default paper size, which can be overridden with the option ``{\ttfamily -t letter}" or ``{\ttfamily -t a4}".  
If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command.

The {\ttfamily times.sty} package produces a bug in the handling certain combinations of letters; for example, `fi' is interpretted as a British pound symbol. Use the option ``{\ttfamily -G0}" ( capital G and zero) to avoid this problem.

To summarize, the following DVIPS options are recommended when making the PS file: ``{\ttfamily -t letter -P pdf -G0}".

%%-----------------------------------------------------------
\subsection{Bold Math Symbols}

The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX. It also provides many useful capabilities for creating elaborate mathematical expressions. You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
\verb+\usepackage[]{amsmath}+ \\[1ex]
Then for bold math symbols, use \verb+\boldsymbol+; for example, 
\verb+$\boldsymbol{\pi}$+ 
yields a bold pi.  You can make it easier to use by defining a shorthand command:\\[1ex]
\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
and then using it like so \verb+$\bm{\pi}$+.

Not all math symbols are available in bold.  In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+. This command approximates a bold character with a superposition of several, slightly displaced unbold characters.

If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
Then, in the title, use something like:\\[1ex]
\verb+\title{Estimation of {$\boldsymbol\alpha$} by a Monte Carlo + \linebreak\verb+technique}+ \\[1ex]
Note that the command to create the alpha character is enclosed within braces to form a self-contained environment.

%%-----------------------------------------------------------
\subsection{Uppercase Letters and Special Symbols in BibTex and LaTeX}

BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case. LaTeX does the same thing for the article title. BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.

The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged within braces \verb!{}!. Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
\verb+ @article{Kaczmarz37,+ \\ 
\verb+ author = "S. Kaczmarz",+ \\ 
\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen + \linebreak\verb+linearer {G}leichungen",+ \\ 
\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
\verb+ volume = "A35",+ \\ 
\verb+ pages  = "355-357",+ \\	
\verb+ year   = "1937"	} + \\[1ex]
This example shows the treatment for both umlauts and uppercase letters.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments 
This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiejour}   %>>>> makes bibtex use spiejour.bst

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Biographies of authors %%%%%

\vspace{2ex}\noindent{\bf First Author} is an assistant professor at the University of Optical Engineering. He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.  He is the author of more than 50 journal papers and has written three book chapters. His current research interests include optical interconnects, holography, and optoelectronic systems. He is a member of SPIE.

\vspace{1ex}
\noindent Biographies and photographs of the other authors are not available.

\listoffigures
\listoftables

\end{spacing}
\end{document}

### 2014-12-10 latex-style-files-spie-manuscript/manuscript1.0.tex
Glory is fleeting, but obscurity is forever.
said Napoleon Bonaparte

--- 2014-12-10 latex-style-files-spie-manuscript/article.tex
@@
 
-%%\documentclass[12pt]{spieman}  %>>> 12pt font mandatory; use this for US letter paper 
-\documentclass[a4paper,12pt]{spieman}  %>>> use this instead for A4 paper
+\documentclass[12pt]{spieman}  %>>> 12pt font mandatory; use this for US letter paper 
+%%\documentclass[a4paper,12pt]{spieman}  %>>> use this instead for A4 paper
 %%\documentclass[nocompress,12pt]{spieman}  %>>> to avoid compression of citations
@@
 \usepackage{tocloft}
+\usepackage{units}
+\usepackage{nicefrac}
+\usepackage{color}
+\usepackage{epstopdf}
+\usepackage[globalcitecopy,labelstoglobalaux,sectionbib]{bibunits}
+\usepackage[thinspace,thinqspace,squaren]{SIunits}
+\usepackage{fancyhdr}
+\usepackage{url}
+\usepackage{wasysym}
+%\usepackage{alltt}
+%\renewcommand{\ttdefault}{txtt} 
+\usepackage{array}
+%\usepackage[version=3]{mhchem}
+%\usepackage[T1]{fontenc}
+%\usepackage{textcomp}
+%\usepackage{verbatim} 
+%\usepackage{mathpazo}
+%\usepackage{amsmath}
+%\usepackage{mathtools}
+\usepackage{amssymb}
+\usepackage{accents}
+\usepackage{url}
+\usepackage{amscd}
+\usepackage{epsfig}
+\usepackage{cite}
+\usepackage{subfig}
+\usepackage[globalcitecopy,labelstoglobalaux,sectionbib]{bibunits}
+%\usepackage[sectionbib]{bibunits}
+\usepackage{appendix}
+\usepackage{slashbox}
+%\usepackage{multirow}
+%\usepackage{caption}
 
-\title{Working title: the most amazzing SPIM and how we built it}
+\title{Working title: the most amaz-zing SPIM and how we built it}
 
@@
 \begin{abstract}
-200 words limit.
-It should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting and indexing databases, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period.
-The body of the manuscript should be double-spaced and fully justified.
+200 words limit. no numerical references presenting concisely the objectives, methodology used, results obtained, and their significance.
 \end{abstract}
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}
+\keywords{Light sheet microscopy, Big data, Optical clearing, Data management, whole brain imaging, rolling shutter, 7,8.}
 
@@
 \label{sect:intro}  % \label{} allows reference to this section
-This document shows the required format and appearance of a manuscript prepared for SPIE journals.
-Formatting guidelines must be carefully followed.
-Authors are advised to print this sample manuscript and use it as a reference while preparing their own paper, to ensure all guidelines are met.
+Here will be an introduction to whole brain imaging the challenges it is facing and how light sheet microscopy is addressing those challenges.
+Points to raise: briefly optical clearing, big data generation and management, image quality degradation necessitating rolling shutter, refocusing?, double sided illumination, maybe Bessel beam illumination, etc.
 
-%%-----------------------------------------------------------
-\subsection{Use of This Document}
+\section{Optical Setup}
+\subsection{Optical path}
+Here we describe our optical setup, the components we use etc
 
-This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.
-The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it.
-Authors may use it as a template to create their own manuscript.
-While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.
+\subsection{Alignment}
+and maybe also some details on who we aligned everything. we have our sample mirror with the hole in it, the shear plate, periscopes etc...
 
-%%-----------------------------------------------------------
-\subsection{English}
+\subsection{Sample chamber}
+the sample chamber is probably of particular interest, how was it designed and made, how do we protect the objectives, stop it from leaking, soft connections and hard connections.
 
-Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-In addition, good English usage is essential.
-Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced.
-Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{http://spie.org/EnglishEditing}.
-SPIE authors will receive a 10\% discount off their services.
-A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission.
-Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.
+\section{Software Management}
+Here we describe all things murmex, components and their communication/ interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
 
-%%-----------------------------------------------------------
-\subsection{Page Setup and Fonts}
+\section{Data Management}
+Here we describe our data pipeline: data production rate as function of frame rate and image size, stack size, tomo size, SSD space, transfer to NAS digital downsampling, and tiff compression, NAS to CINECA, 10 gigabit connection etc.
 
-All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm).
-Manuscripts must be formatted for US letter paper, on which the margins should be 1.0 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in\ on the left and right.
+\section{Data}
+some pretty images to prove that it all worked.
 
-The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}.
-If this font is not available, use a similar serif font.
-The manuscript should not contain headers or footers.
-Pages should be numbered.
+\section{Conclusion}
+summary
 
-%% Use of [h] in following command forces table to appear "here", instead of a top or bottom of page, which is generally preferred.
-\begin{table}[h]
-\caption{Fonts sizes and styles.} 
-\label{tab:fonts}
-\begin{center}       
-\begin{tabular}{|l|l|} %% this creates two columns
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
-\hline\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
-\hline 
-\end{tabular}
-\end{center}
-\end{table}
+\section{Outlook}
+where are we going next with this?
+
+%%-------------
+   %\begin{figure}
+   %\begin{center}
+   %\begin{tabular}{c}
+   %\includegraphics[height=5.5cm]{mcr3b.eps}
+   %\end{tabular}
+   %\end{center}
+   %\caption 
+   %{ \label{fig:example} %>> use \label inside caption to get Fig. number with \ref{}
+%Example of a figure caption. } 
+   %\end{figure} 
+%
+%%------------- 
+   %\begin{figure}
+   %\begin{center}
+   %\begin{tabular}{c}
+   %\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
+     %\\
+     %(a) \hspace{5.1cm} (b)
+   %\end{tabular}
+   %\end{center}
+   %\caption 
+   %{ \label{fig:example2} %>> use \label inside caption to get Fig. number with \ref{}
+%Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
+   %\end{figure}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parts of Manuscript}
-
-This section describes the normal structure of a manuscript and how each part should be handled.
-The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
-
-%%-----------------------------------------------------------
-\subsection{Title and Author Information} 
-\label{sect:title}
-The article title appears left justified at the top of the first page.
-The title font is 16 pt., bold.
-The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.
-Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.).
-The word “novel” should not appear in the title, as publication will imply novelty.
-Avoid the use of acronyms in the title, unless they are widely understood.
-Appendix A contains more about acronyms.
-
-The list of authors immediately follows the title, 18 points below.
-The font is 12 pt., bold and the author names are left justified.
-The author affiliations and addresses follow the names, in 10-pt., normal font and left justified.
-For multiple affiliations, each affiliation should appear on a separate line.
-Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations.
-Corresponding author should be listed below the Keywords, following the line ``Address all correspondence to:"; include mailing address, telephone, fax, and E-mail address.
-
-%%-----------------------------------------------------------
-\subsection{Abstract} 
-The abstract should be a concise summary of the paper.
-Because the abstract may be used in abstracting journals, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-It should not exceed 200 words.
-For further guidelines, please read the brief article titled ``How to Write an Abstract (PDF)," \\(\linkable{http://spie.org/Documents/Publications/How to Write an Abstract.pdf}) by Philip Koopman.
-(Courtesy of Philip Koopman, Carnegie Mellon University.) Note the underlined link must be written on a single line in order for the link to function.
-Thus, a break in the line, created with {\verb+\\+} is required before the link or the preceding text should be editted to gracefully place the link on a single line.
-This type of adjustment is best done at end of the manuscript-preparation process.
-
-%%-----------------------------------------------------------
-\subsection{Keywords} 
-Up to eight keywords should be specified.
-
-%%-----------------------------------------------------------
-\subsection{Body of Paper} 
-The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.
-
-To provide transition elements in your paper, it is important to refer back (or forward) to specific sections.
-Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed..." or ``Section 2.1 contained a description..." If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out.
-When occurring in the middle of a sentence, these words are abbreviated Sect., Ref., Eq., and Fig.
-
-At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).
-
-%%-----------------------------------------------------------
-\subsection{Footnotes} 
-Use textual footnotes only when necessary to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should be avoided.
-If absolutely necessary, the footnote mark must come at the end of a sentence.
-To insert a footnote, use the {\verb|\footnote{}|} command.
-
-%%-----------------------------------------------------------
-\subsection{Appendices} 
-SPIE journals do not accept supplementary materials.
-However, it is acceptable to include an Appendix when necessary,  details such as derivations of equations, proofs of theorems, and details of algorithms.
-Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.
-
-%%-----------------------------------------------------------
-\subsection{Acknowledgments} 
-In the acknowledgments section, which appears just before the references, the authors may credit others for their guidance or help.
-Also, funding sources or sponsorship information may be stated.
-The acknowledgments section does not have a section number.
-
-%%-----------------------------------------------------------
-\subsection{References} 
-The References section lists books, articles, and reports that are cited in the paper.
-This section does not have a section number.
-The references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this document.
-
-The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.
-Alternatively, the references may be directly formatted in the LaTeX source file.
-
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.
-References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
-
-The references are numbered in the order of their first citation.
-Citations to the references are made using superscripts, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ..."  Two or more references should be separated by a comma with no space between them.
-Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.
-
-%%---------------------------
-\subsubsection{Reference linking and DOIs} 
-A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet.
-The use of DOIs allows readers to easily access cited articles.
-Authors should include the DOI at the end of each reference in brackets, if a DOI is available.
-See examples at the end of this manuscript.
-A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}.
-The inclusion of DOIs will facilitate reference linking and is highly recommended.
-
-In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note" in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}.
-The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.
-
-%%-----------------------------------------------------------
-\subsection{Biographies} 
-A brief professional biography not to exceed 75 words may be provided for each author, if available.
-Biographies should be placed at the end of the paper, after the references.
-Personal information such as hobbies or birthplace/birthdate should not be included.
-Author photographs are not published.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Section Formatting} \label{sect:sections}
-
-In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
-Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references.
-(Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.
-
-Main section headings are in 12-pt., bold font, left-justified and in title case, where important words are capitalized.
-
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style.
-The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation.
-There is no additional space between paragraphs.
-In LaTeX, paragraphs are separated by blank lines in the source file.
-Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
-
-%%-----------------------------------------------------------
-\subsection{Subsection Headings} 
-All important words in a subsection (level 1) header are capitalized.
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end.
-The heading is left justified and its font is 12 pt., italic.
-
-%%-----------
-\subsubsection{Sub-subsection headings} 
-The first word of a sub-subsection is capitalized.
-The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known).
-The heading is left justified and its font is 11 pt., italic.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Figures and Tables}
-
-%%-----------------------------------------------------------
-\subsection{Figures}
-
-Figures are numbered in the order in which they are called out in the text.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It may be necessary to move figures or tables around to enhance readability.
-LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.
-
-Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered.
-Figure captions are centered below the figure or graph.
-Figure captions start with the abbreviation ``Fig" in front of the figure number, followed by a period, and the text in 10-pt.
-font.
-See Fig.~\ref{fig:example} for an example.
-
-%%  Use following command to specify that graphics file is in 
-%%  a directory other than this LaTeX source file.
-%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
-%-------------
-   \begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[height=5.5cm]{mcr3b.eps}
-   \end{tabular}
-   \end{center}
-   \caption 
-   { \label{fig:example} %>> use \label inside caption to get Fig. number with \ref{}
-Example of a figure caption. } 
-   \end{figure} 
-%-------------
-Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.
-In no case, should the article's text be wrapped around a figure.
-Figure~\ref{fig:example2} shows two side-by-side images.
-When a figure contains more than one image, the author must submit them as a single image file.
-Further details about figure formatting can be found at \linkable{http://spie.org/x85020.xml
-\#Components}.
-
-%------------- 
-   \begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
-     \\
-     (a) \hspace{5.1cm} (b)
-   \end{tabular}
-   \end{center}
-   \caption 
-   { \label{fig:example2} %>> use \label inside caption to get Fig. number with \ref{}
-Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
-   \end{figure}
-
-%-------------%%-----------------------------------------------------------
-\subsection{Tables} 
-Tables are numbered in the order in which they are referenced.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It is preferable to have tables appear at the top or bottom of the page, if possible.
-Table captions are handled identically to those for figures, except that they appear above the table.
-See Table~\ref{tab:fonts} for an example.
-%%-----------------------------------------------------------
-
-\subsection{Multimedia} 
-Please refer to the multimedia guidelines at \linkable{http://spie.org/x85020.xml\#Multimedia} for specific submission guidelines and requirements.
-The following types of multimedia files are accepted: QuickTime Non-Streaming video (.qt or .mov), MPEG (.mpg or .mp4).
-The recommended maximum size for each multimedia file is 10-12 MB.
-Authors must insert a representative “still” image from the video file in the manuscript as a “figure.” This still image will be linked by the publisher to the actual video file, as will the caption label.
-Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.
-Otherwise  The multimedia file type should be included in parentheses at the end of the figure caption, along with the file size.
-See Video \ref{vid:satellite} for an example.
-
-%-------------
-   \begin{video}
-   \begin{center}
-   {\includegraphics[height=5cm]{satellite.eps}}
-   \\
-   \end{center}
-   \caption{\label{vid:satellite} Example of a multimedia still image (MPEG, 2.5 MB).}
-   \end{video} 
-%-------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix    %>>>> this command starts appendixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Miscellaneous Formatting Details} \label{sect:misc}
-
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.
-
-%%-----------------------------------------------
-\subsection{Formatting Equations} 
-Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.
-Important equations appear on their own line.
-Such equations are centered.
-For example, ``The expression for the field of view is
-	\begin{equation}
-	\label{eq:fov}
-2 a = \frac{(b + 1)}{3c} \, ,
-	\end{equation}
-where $a$ is the ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.
-
-Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma appears after the equation because the next line is a subordinate clause.
-If the equation ends the sentence, a period should follow the equation.
-The line following an equation should not be indented unless it is meant to start a new paragraph.
-Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.
-
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..." Note that the word ``Equation" is spelled out if it begins a sentence, but is abbreviated as ``Eq." otherwise.
-Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq." and the following equation number..
-
-%%-----------------------------------------------------------
-\subsection{Formatting Theorems}
-
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.
-The text of the theorem continues on the same line in normal, 10-pt.
-font, achieved in LaTeX using \verb|\footnotesize|.
-For example,
-
-\vspace{2ex}\noindent{\footnotesize{\bf Theorem 1.} For any unbiased estimator...}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Some LaTeX Guidance} \label{sect:latex}
-
-To work properly, the LaTeX style file {\ttfamily spieman.cls} used to create this document requires following LaTeX packages:
-{\ttfamily times.sty}, {\ttfamily float.sty}, {\ttfamily ifthen.sty}, {\ttfamily setspace.sty}, \\{\ttfamily cite.sty} (version 4.01 or later), and {\ttfamily color.sty}.
-If you do not have them in your LaTeX environment, see your system manager, or download them from \linkable{http://www.ctan.org}.
-
-The author is required to make sure his or her manuscript is properly formatted.
-LaTeX sometimes needs some help to avoid making gross formatting blunders.
-The source file for this document provides examples of how to cope with some of LaTeX's shortcomings.
-
-%%-----------------------------------------------------------
-\subsection{Margins and PostScript Fonts}
-
-Manuscripts submitted for SPIE journals as Portable Document Format (PDF) files must be formatted for US-letter-size paper and have the correct margins.
-The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.
-
-One may directly create a PDF file from the DVI file with the LaTeX utility {\ttfamily dvipdfm}, for example.
-No options are necessary.
-Appealing aspects of this utility are that Acrobat Distiller is not needed, and Type 1 PostScript fonts are automatically included in the resulting PDF file.
-Furthermore, {\ttfamily dvipdfm} allows one to directly incorporate images in JPEG, PNG, and PDF formats, and not just EPS, which is normally used with LaTeX.
-
-Alternatively, with an application such as Adobe Acrobat, PDF files can be created from PostScript (PS) files, which can be produced by DVIPS.
-In most cases, the following DVIPS options should be invoked.
-
-An important DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file.
-This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.
-The option ``{\ttfamily -P pdf}" makes DVIPS include these fonts in its output PS file.
-
-LaTeX margins are related to the document's paper size. The paper size is set at two separate places in the process of creating a PS file. The first place is in {\ttfamily latex}. 
-The second place is in the application DVIPS. DVIPS has its own default paper size, which can be overridden with the option ``{\ttfamily -t letter}" or ``{\ttfamily -t a4}".  
-If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command.
-
-The {\ttfamily times.sty} package produces a bug in the handling certain combinations of letters; for example, `fi' is interpretted as a British pound symbol.
-Use the option ``{\ttfamily -G0}" ( capital G and zero) to avoid this problem.
-
-To summarize, the following DVIPS options are recommended when making the PS file: ``{\ttfamily -t letter -P pdf -G0}".
-
-%%-----------------------------------------------------------
-\subsection{Bold Math Symbols}
-
-The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX.
-It also provides many useful capabilities for creating elaborate mathematical expressions.
-You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
-\verb+\usepackage[]{amsmath}+ \\[1ex]
-Then for bold math symbols, use \verb+\boldsymbol+; for example, 
-\verb+$\boldsymbol{\pi}$+ 
-yields a bold pi.  You can make it easier to use by defining a shorthand command:\\[1ex]
-\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
-and then using it like so \verb+$\bm{\pi}$+.
-
-Not all math symbols are available in bold.
-In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+.
-This command approximates a bold character with a superposition of several, slightly displaced unbold characters.
-
-If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
-Then, in the title, use something like:\\[1ex]
-\verb+\title{Estimation of {$\boldsymbol\alpha$} by a Monte Carlo + \linebreak\verb+technique}+ \\[1ex]
-Note that the command to create the alpha character is enclosed within braces to form a self-contained environment.
-
-%%-----------------------------------------------------------
-\subsection{Uppercase Letters and Special Symbols in BibTex and LaTeX}
-
-BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case.
-LaTeX does the same thing for the article title.
-BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.
-
-The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged within braces \verb!{}!.
-Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
-\verb+ @article{Kaczmarz37,+ \\ 
-\verb+ author = "S. Kaczmarz",+ \\ 
-\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen + \linebreak\verb+linearer {G}leichungen",+ \\ 
-\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
-\verb+ volume = "A35",+ \\ 
-\verb+ pages  = "355-357",+ \\	
-\verb+ year   = "1937"	} + \\[1ex]
-This example shows the treatment for both umlauts and uppercase letters.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \acknowledgments 
-This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
+Human Brain Project tutta la vita.
 
@@
 
-\bibliography{report}   %>>>> bibliography data in report.bib
+%\bibliography{report2}   %>>>> bibliography data in report.bib
 \bibliographystyle{spiejour}   %>>>> makes bibtex use spiejour.bst
+\begin{thebibliography}{0}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Biographies of authors %%%%%
+\bibitem{Silvestri2012} Silvestri, L., Bria, A., Sacconi, L., Iannello, G. \& Pavone, F. S., XY. 	\emph{Opt Express} \textbf{20}, 20582-20598 (2012).
 
-\vspace{2ex}\noindent{\bf First Author} is an assistant professor at the University of Optical Engineering.
-He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.
-He is the author of more than 50 journal papers and has written three book chapters.
-His current research interests include optical interconnects, holography, and optoelectronic systems.
-He is a member of SPIE.
-
-\vspace{1ex}
-\noindent Biographies and photographs of the other authors are not available.
+\end{thebibliography}
 

### 2014-12-10 latex-style-files-spie-manuscript/manuscript1.0.tex
First commit: contains folder (latex) in which all images and documents to be loaded into the manuscript need to be placed. Latex file is called manuscript1.0 increment as needed. Also contains example papers published in the target journal and example publications of similar content.

@@
 %  ifthen.sty, cite.sty, color.sty, setspace.sty
-%
-%  Special instructions are included in this file after the
-%  symbol %>>>>
-%  Numerous commands are commented out, but included to show how
-%  to effect various options, for example, to print page numbers, etc.
-%  This LaTeX source file is composed for LaTeX2e.
 
@@
 %  for example, [dvips], but that may be inappropriate for some LaTeX installations.
-%%\usepackage{amsmath}  %>>> for AMS math formatting, 
-%  including bold Greek symbols
+
 \usepackage[]{graphicx}
@@
 %\usepackage{mathpazo}
-%\usepackage{amsmath}
+%\usepackage{amsmath} %>>> for AMS math formatting including bold Greek symbols
 %\usepackage{mathtools}
@@
 
-\title{Working title: the most amaz-zing SPIM and how we built it}
+\title{Working title: the most amaz-zing SPIM and how we built it. Authors currently alphabetical.}
 
-%>>>> The author is responsible for formatting the 
-%  author list and their affiliations.  Use \\ to force linebreaks.
-%  The correspondence between each author and his/her address
-%  can be indicated with a superscript, 
-%  which is easily obtained with \supscr{}.
-%>>>> After the abstract, the author must include
-%  a list of keywords and contact information for the corresponding author.
-
-\author{First Author,\supscr{a} Second Author,\supscr{a} Third Author,\supscr{b} Fourth Author\supscr{a,b}}
+\author{Irene Costantini,\supscr{a} Giulio Iannello,\supscr{d} M.
+Caroline M\"{u}llenbroich,\supscr{a} Leonardo Onofri,\supscr{d} Francesco S.
+Pavone,\supscr{a,b,c} Leonardo Sacconi,\supscr{b,a} Ludovico Silvestri, \supscr{a} Marcel Van t'Hoff\supscr{x}}
 
@@
 \supscrsm{b}National Institute of Optics, National Research Council, Italy\\
-\supscrsm{c}Department of Physics and Astronomy, University of Florence, Via Giovanni Sansone, 1, Sesto Fiorentino (Firenze), Italy, 50019}
+\supscrsm{c}Department of Physics and Astronomy, University of Florence, Via Giovanni Sansone, 1, Sesto Fiorentino (Firenze), Italy, 50019\\
+\supscrsm{d}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
+\supscrsm{x}Distrio, Murmex}
 
@@
 Here will be an introduction to whole brain imaging the challenges it is facing and how light sheet microscopy is addressing those challenges.
-Points to raise: briefly optical clearing, big data generation and management, image quality degradation necessitating rolling shutter, refocusing?, double sided illumination, maybe Bessel beam illumination, etc.
+Points to raise: briefly optical clearing, big data generation and management, image quality degradation necessitating rolling shutter, refocusing?, The next parts will be in clear sections so that we can divide them better between us if necessary.
+Can be merged later on if we wish so.
 
-\section{Optical Setup}
+Basic principles of light sheet microscopy: light efficiency/reduced phototoxicity, speed, true optical sectioning, resolution etc.
+
+\section{Optical clearing}
+CLARITY and TDE stuff, get contribution/input from Irene.
+
+\section{Optomechanics}
 	\subsection{Optical path}
-Here we describe our optical setup, the components we use etc
+Here we describe our optical setup, the components we use etc. 
+		\subsubsection{illumination}
+		lasers, AOTF, Pockels, Bessel, double sided, digitally scanned, objectives
+		\subsubsection{detection}
+		objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
+		\subsubsection{Sample mounting and rotation}
+		the sample chamber is probably of particular interest, how was it designed and made, how do we protect the objectives, stop it from leaking, soft connections and hard connections.
+how do we rotate and move the sample within the chamber.
+in the end, this is where the magic happens....
 
 	\subsection{Alignment}
-and maybe also some details on who we aligned everything. we have our sample mirror with the hole in it, the shear plate, periscopes etc...
-
-\subsection{Sample chamber}
-the sample chamber is probably of particular interest, how was it designed and made, how do we protect the objectives, stop it from leaking, soft connections and hard connections.
+and maybe also some details on how we aligned everything. we have our sample mirror with the hole in it, the shear plate, periscopes etc...
 
 \section{Software Management}
-Here we describe all things murmex, components and their communication/ interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
+Here we describe all things software control and communication, components and their interaction.
+how is the rolling shutter timed with galvos, triggers and clocks etc.
+Get in touch early with Marcel to ask him and write/contribute to this paragraph.
 
 \section{Data Management}
-Here we describe our data pipeline: data production rate as function of frame rate and image size, stack size, tomo size, SSD space, transfer to NAS digital downsampling, and tiff compression, NAS to CINECA, 10 gigabit connection etc.
+	\subsection{Pipeline}
+	Here we describe our data pipeline: data production rate as function of frame rate and image size, stack size, tomo size, SSD space, transfer to NAS digital downsampling, and tiff compression, Leo's python script, NAS to CINECA, 10 gigabit connection etc.
+
+	\subsection{stitching and visualisation}
+	Terastitcher and Teraviewer
+
+	\subsection{example for postprocessing: Automated cell counting}
+	See Reference\cite{Frasconi2014} for details.
 
@@
 
-\bibitem{Silvestri2012} Silvestri, L., Bria, A., Sacconi, L., Iannello, G. \& Pavone, F. S., XY. 	\emph{Opt Express} \textbf{20}, 20582-20598 (2012).
+\bibitem{Silvestri2012} Silvestri, L., Bria, A., Sacconi, L., Iannello, G. \& Pavone, F. S. 	\emph{Opt Express} \textbf{20}, 20582-20598 (2012).
+
+\bibitem{Frasconi2014} Frasconi, P., Silvestri, L., Soda, P., Cortini, R., L., Pavone, F. S., \& Iannello, G. 	\emph{Bioinformatics} \textbf{30}, i587-i593 (2014).
 

### 2015-01-13 latex-style-files-spie-manuscript/manuscript1.0.tex
commit for sharing with Ludo

--- 2014-12-10 latex-style-files-spie-manuscript/manuscript1.0.tex
@@
 \usepackage{accents}
+%\usepackage{hyperref}
 \usepackage{url}
@@
 \usepackage{slashbox}
-%\usepackage{multirow}
+\usepackage{multirow}
+\usepackage{pbox}
 %\usepackage{caption}
+\usepackage{pdflscape}
+\usepackage{nicefrac}
+\usepackage{rotating}
+\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue,
+		pagebackref,
+		hyperindex,%linktocpage,
+		bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=0,
+		pdfstartview=FitV,
+		pdfstartpage=1]
+	{hyperref} % makes pdf look nice with hyperlinks
 
-\title{Working title: the most amaz-zing SPIM and how we built it}
+\title{Working title: the most amaz-zing SPIM and how we built it.}
 
-%>>>> The author is responsible for formatting the 
-%  author list and their affiliations.  Use \\ to force linebreaks.
-%  The correspondence between each author and his/her address
-%  can be indicated with a superscript, 
-%  which is easily obtained with \supscr{}.
-%>>>> After the abstract, the author must include
-%  a list of keywords and contact information for the corresponding author.
+\author{M.
+Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel Van t'Hoff\supscr{f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
+Pavone,\supscr{a,b,c,d}  }
 
-\author{First Author,\supscr{a} Second Author,\supscr{a} Third Author,\supscr{b} Fourth Author\supscr{a,b}}
-
-\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy, University of Florence, Via Nello Carrara,1, Sesto Fiorentino (Firenze), Italy, 50019\\
-\supscrsm{b}National Institute of Optics, National Research Council, Italy\\
-\supscrsm{c}Department of Physics and Astronomy, University of Florence, Via Giovanni Sansone, 1, Sesto Fiorentino (Firenze), Italy, 50019}
+\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
+\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
+\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
+\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
+\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
+\supscrsm{f}Distrio, Murmex}
 
@@
 
-\begin{spacing}{2}   % use double spacing for rest of manuscript
+%\begin{spacing}{2}   % use double spacing for rest of manuscript
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction}%funnel shape
 \label{sect:intro}  % \label{} allows reference to this section
-Here will be an introduction to whole brain imaging the challenges it is facing and how light sheet microscopy is addressing those challenges.
-Points to raise: briefly optical clearing, big data generation and management, image quality degradation necessitating rolling shutter, refocusing?, double sided illumination, maybe Bessel beam illumination, etc.
 
-\section{Optical Setup}
-\subsection{Optical path}
-Here we describe our optical setup, the components we use etc
+The highly ambitious project of mapping and understanding each and every neuronal connection in the whole brain has been moved from the realm of wishful longing to feasible reality by the recent advent of light sheet fluorescent microscopy (LSFM).
+With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition.
+In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
+This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap (Figure\ref{fig:Panel1},A).
+Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise.
+Consequently LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths; however, it requires the sample to be transparent.
+
+Several challenges remain to be overcome, however, to allow fast and, most of all systematic, production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
+Those challenges include fast, cheap and reproducible sample preparation, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces.
+The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
+On the other hand, the imaging of large, intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent.
+This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.
+
+Here we will review a state-of-the-art LSFM, as it is implemented in our lab, which can be used to acquire 3D data sets of clarified mouse brains.
+The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples.
+After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days.
+In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task which in previous publication has too often been summarised in a single sentence.
+A systematic approach to handle, store and analyse the data is also given.
+We further explain about the data volume we produce how it can be reduced and handled.
+We finish with some nice data and an outlook.
+The final sentence of the introduction needs to be amazing.
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{Panel1.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:Panel1} Schematic of light sheet microscopy.
+(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
+The clarified, fluorescently-labelled brain (B) is mounted on a Teflon cylinder inside the watertight chamber (D) and can be translated and rotated freely with piezo motors (D).
+The sample is glued onto a cover slip which is slid into a custom made adapter mount that is inserted into the Teflon cylinder (E).}
+   \end{figure}
+
+\section{Optical clearing and sample mounting}
+Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
+Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices.
+Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque.
+In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed.
+These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
+
+A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
+A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
+Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap.
+Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies.
+With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.
+
+To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation.
+The question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quarz cuvettes have been reported (cite), however these approaches are limited to much smaller sample volumes.
+
+We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},C) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
+A motorized x-, y-, z-, $\theta$-stage (M-122.2DD and M-116.DG, Physik Instrumente) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
+The clarified brains are fixed with super glue to a coverslip which is slid into a custom made adapter and tightened with a plastic-capped screw.
+The adaptor is then inserted into the Teflon cylinder (Figure\ref{fig:Panel1},E) with the coverslip being positioned on the far side of the detection objective.
+Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.
+The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
+Stable mounting is a key concern as a whole brain tomography can require image acquisition in excess of 3 days.
+We found that the effect of gravity, tissue shrinking/expansion and evaporation of PBS over such time spans are negligible, however, after that point the super glue is starting to dissolve.
+
+	\section{Optical path}
+
+	\subsection{Illumination}
+
+		\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{Panel2.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:excitation} (A) Topview of the excitation path.
+The galvo scanners are mounted above periscopes.
+LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter, ABCD: flip mirrors.
+Inset: detection.
+(B) Oblique view of the microscope.
+A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut out for the translation stages.
+A second breadboard is used for the camera.}
+   \end{figure}
+
+The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A).
+The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components) and have each an output power of 50mW.
+The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series).
+An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines.
+The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity.
+Due to the nonlinear response of the AOTF we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a linear look-up table through interpolation.
+The zero order light is blocked by an iris.
+An electro-optical laser modulator acts like a wave plate with electrically controlled retardation and rapidly rotates (hundreds ns/ms?) the input polarisation of the excitation light by $90\degree$.
+The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system.
+First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
+A digital line is used to electronically control the frequency of the polarisation shift.
+After the laser modulator the excitation beam is further expanded by a factor of 2 (f100, f200) with two achromatic doublets.
+From here on three different light paths can be chosen through flip mirrors.
+One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam.
+The other two options create Gaussian beams of different beam diameter.
+This diameter variation translates to different fields of view later on in the detection path.
+The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two excitation arms which are built to be identical.
+The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo).
+The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.
+The light sheet is generated digitally by scanning the excitation beam with a sawtooth signal applied to the galvo.
+This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
+The scan mirror surface is reimaged with a telescope (f50, f100) onto the back aperture a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
+The two excitation objectives are designed for air immersion.
+A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the glue/mounting of the lens elements which is compromised by the organic solvent.
+The sample chamber is tightly bolted  to the optical breadboard while soft connections through silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages.
+All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
+In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber.
+
+		\subsection{Detection}
+		%objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
+
+		Fluorescence is collected on a axis perpendicular to the excitation with an objective that was specifically designed for immersion in clearing solutions of various refractive indices.
+The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP).
+To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
+HERE WE'LL NEED SOME CHARACTERISATION DATA.
+We use a tube lens of 200mm to create an image on a sCMOS camera (Orca Flash4.0, Hamamatsu).
+A fluorescent filter is used to block out any excitation light.
+The camera chip of over 4 megapixels is read out in one sweep from top to bottom in the so-called light sheet mode in which only a subset of horizontal lines is exposed and consequently read out and any time.
+This sweeping line exposure creates a virtual confocal slit.
+Confocality is achieved by synchronising a single line which generates the light sheet with the exposure of a few lines on the CMOS chip.
+
+For image acquisition the sample is slowly translated at a fixed speed along the detection axis through the light sheet.
+Images are recorded at a frame rate of 44Hz in different planes along the optical axis of the detection lens (here z) to acquire a stack.
+After successful stack acquisition the sample is moved to an adjacent vertical position (here y) to acquire the next image stack.
+Once the entire vertical slice composed of z stacks is acquired the sample is moved to an incremented x position.
+In this way the entire cubic volume is imaged.
 
 	\subsection{Alignment}
-and maybe also some details on who we aligned everything. we have our sample mirror with the hole in it, the shear plate, periscopes etc...
 
-\subsection{Sample chamber}
-the sample chamber is probably of particular interest, how was it designed and made, how do we protect the objectives, stop it from leaking, soft connections and hard connections.
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{Panel3.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope.
+AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system.
+(B) The alignment mirror can be rotated to precisely reflect at $45\degree$.
+(C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm.
+(D) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.}
+   \end{figure}
+
+For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
+The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's depth of field.
+Telecentricity, that is the imaging with two lenses which are the sum of their focal lengths apart, has to be strictly observed in all three arms (Figure\ref{fig:alignment},A), which means the galvo scanners need to be precisely placed in telecentric planes of the excitation objectives while in the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
+Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as pair with recursive dependence.
+
+Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be.
+The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber.
+Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
+With this ``sample mirror" three different position can now be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole, and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage.
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{Panel4.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam in converted into a spherical wavefront.
+Right: inverted light path where a focal spot in the back aperture creates a collimated output.
+(B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.}
+   \end{figure}
+
+The excitation objectives are fixed on mounts which allow three dimensional translation plus pitch and yaw adjustment (LP-1A, Newport).
+In a first step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives.
+We found it useful to use two mirrors in each periscope, one vertically mounted and one mounted at $45\degree$ for vertical deflection of the incoming beam.
+In this way full beam steering can be achieved to realign the periscope before hitting the galvo scanner.
+After this initial alignment the first excitation objective was then placed into the beam path and brought to focus onto the sample mirror, which was adjusted to reflect the light back into the same objective.
+Using a shear plate and a polarising beam splitter cube the back reflected light was qualitatively checked for collimation to ensure the sample mirror was correctly placed in the focal plane of the objective (Figure\ref{fig:alignment2},B).
+The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C).
+This time collimation was checked with the light going through both objectives and so their confocal placement was insured.
+The microscope was then aligned recursively by starting at the confocal point between the objectives and placing successively lens after lens in the up-stream direction.
+Finally, the sample mirror was position in reflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
 
 \section{Software Management}
-Here we describe all things murmex, components and their communication/ interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
+
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{connectivity.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:connectivity} Connectivity scheme} 
+   \end{figure}
+
+%Here we describe all things software control and communication, components and their interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
+
+%Based on a modular scheme (OOP) using Murmex development kit
+%Separate building blocks control different components of the microscope
+%Hierarchical structure coordinates complex tasks
+%Communication takes place through RabbitMQ server (open source message-oriented middleware) using the LabbitMQ library
+
+The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
+Another aspect of software design is avoiding redundancy in writing software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
+Writing well structured scientific software in a group of researchers is an often recurring challenge.
+The final code should be the common effort of all contributors each with their own know-how and practical expertise.
+We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods.
+
+The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their contribution to the software within a  standardized programming scheme by employing object oriented programming methodology.
+Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middleware facilitating message shipment and receival.
+These layers of abstraction are mostly hidden for the developers.
+
+RabbitMQ
+The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
+The message-based communication allows for buffered, asynchronous and reliable message communication between several software components.
+Messages are routed by the broker to the specific software component by its ID.
+In order to access the functionality of RabbitMQ, the application programming interface (API) \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ} was used, which uses .NET calls for sending and receiving messages to and from the RabbitMQ broker.
+Messages can be sent to a single recipient by its ID or sent to all available components.
+
+Murmex
+The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer).
+A finite state machine resembles the Strategy pattern [Design Patterns: Elements of Reusable Object-Oriented Software, E.
+Gamma, R.
+Helm, R.
+Johnson, J.
+Vlissides, 1994], which lets the software of one component proceed from one particular state to another based on message it receives from itself or other components (for example to execute Initialise, Start, Proceed, Stop, Terminate).
+In each state it executes the code for that state only, but flexible execution patterns are possible.
+It thus allows for predictable behaviour, without knowing the exact code.
+Murmex has twelve pre-defined common states (e.g.
+Initialise, Start, Stop, Terminate) and a generic state for implementing custom states.
+A software component that represents one, yet large, task, often uses only those previously four mentioned states.
+Examples for such a software component are the implementation a laser, translation stage and a camera.
 
 \section{Data Management}
-Here we describe our data pipeline: data production rate as function of frame rate and image size, stack size, tomo size, SSD space, transfer to NAS digital downsampling, and tiff compression, NAS to CINECA, 10 gigabit connection etc.
+	\subsection{Pipeline}
+
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{DataFlow.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:DataFlow} Scheme of the data flow.
+(A) Data streaming on the microscope.
+The data is written through the CameraLink connection onto the SSD.
+From there the data can be transferred via a 10Gb connection to the NAS or to the supercomputing centre CINECA in Bologna.
+SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
+(B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
+   \end{figure}
+
+%\begin{landscape}
+\begin{table}%[t!]
+	\centering
+		\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
+		\begin{tabular}{lrl}
+		frame rate																	& 44			& Hz	\\
+		size of 1 frame															& 8				& MB	\\
+		frames per stack														& 3900		& 		\\
+		size of original stack											& 30.4		& GB	\\
+		size of converted stack											& 3				& GB	\\
+		stack acquisition time											& 88.6		& s		\\
+		stack conversion time												& 140			& s		\\
+		time ratio conversion/ acquisition					& 1.6			& 		\\
+		data production rate												& +1.2		&	TB/h\\
+		data conversion rate												& -0.7		&	TB/h\\
+		net rate																		& +0.5		&	TB/h\\
+		SSD RAID																		& 10.9		& TB	\\
+		max acquisition time to fill up SSDs				& 21			& h		\\
+		max tomo size to fill up SSDs								& 25.4		& TB	\\
+		\end{tabular}
+\end{table}
+%\end{landscape}
+The unprecedented amount of data routinely produced by light sheet microscopy presents challenges to the traditional way we interact with our data.
+Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires a professional approach to centralised network architecture.
+The following paragraphs give an idea of the considerations one has to give to the big data volume problem.
+The camera used in our light sheet microscope has a dedicated work station with a CameraLink card and 10.9TB of SSD space in RAID 0 configuration.
+This finite storage capacity is further expanded by a network-attached storage (NAS) of 32.4TB (Figure\ref{fig:DataFlow}).
+The SSDs and the NAS are connected via a 10Gb bandwidth connection using a 10Gb switch and a 10Gb optical fibre connects our lab to the supercomputing centre CINECA in Bologna.
+Mention PICO system/storage analysis capacity there?
+Mention graphical processing unit and cores/processors/RAM of work station?
+
+With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
+Based on a frame rate of 44Hz each stack takes approximately 1.5 minutes to acquire and the SSD RAID fills up with a data writing rate of 1.2TB/h.
+If no further measures are taken the SSD RAID of 10.9TB would be filled up in just 9h.
+A custom compression script written in Python serves the triple purpose of translating the images from the proprietary Hamamatsu file format to 3D tif, to transfer the data from the SSD RAID to a network attached storage (NAS) and to reduce the raw data size by first, digitally downsampling the image resolution and second, applying a lossless compression to the tif images.
+This leads to a overall reduction of data size by a factor of ten, each stack now taking up only 3GB of disc space, albeit at a much slower conversion rate (-0.7TB/h) than the rate at which data is written to the SSD thus representing the most serious bottleneck to our data production pipeline.
+The SSD RAID fills up at a rate of 0.5TB/h which means the total acquisition time is limited to less than 24h and a total tomo size of just over 25TB.
+After this time acquisition has to be halted until the slower conversion process has caught up and freed the SSD RAID before data acquisition can start again.
+A whole mouse brain tomography would take 3 days of uninterrupted measuring yet with the necessary breaks for data transfer this time is easily doubled to tripled.
+
+	\subsection{Stitching and visualisation}
+
+Given the limited field of view of the microscope, the acquisition of macroscopic specimens required many parallel image stacks to cover all the volume.
+Thus, in order to achieve a 3D image of the whole specimen from raw data, the Terastitcher\cite{Bria2012} has been recently proposed, i.e.
+a stitching tool capable to deal with teravoxel-sized images.
+However, the Terastitcher does not support input data acquired through the serial sectioning procedure, which leads to a specimen partitioned in different layers.
+Furthermore, only single channel images can be processed.
+For these reasons, we extended the Terastitcher functionalities introducing the two following additional features: i) stitching of a specimen partitioned in a number of overlapping layers for the hippocampus reconstruction and, ii) coping with images containing more than one channel for the human brain tomography.
+With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depicts in Fig.1 the adopted strategy.
+First of all, the various input layers, each of which is composed of several parallel overlapping stacks, are separately stitched by using the existing Terastitcher tool.
+After this preliminary step,  leveraging the layer coordinates provided by the instrument, we import the processed layers as a new volume where each layer has a partial overlap with adjacent layers.
+Furthermore, each layer is organized in a non-overlapping tiled format, enabling the application of a multi MIP-NCC approach\cite{Bria2012}, which computes the displacement  between two adjacent layers along all of the three directions (Fig.
+1).
+When a displacement computation for each pair of adjacent layers has been computed, the overlapping regions are merged through a blending procedure which smooths the transition between layers, resembling once more the procedure used by Terastitcher for combining adjacent stacks.
+Finally, we note that due to the repositioning of each layer, the volume containing the reconstructed specimen might contain empty regions, which are thereby filled with black voxels.
+Turning our attention to the second additional feature, that is handling multi-channel images, the Terastitcher has been extended so that the MIP-NCC algorithm used for displacement computation can work on an image, which can be either
+the fusion of the input channels or one of the input channels.
+This permits to privilege the channel with more information content over the other channels as well as discard noisy channels.
+Note that the reconstructed 3D image can be produced with the same channel composition of raw data.
+
+	\subsection{Example for postprocessing: Automated cell counting}
+	See Reference\cite{Frasconi2014} for details.
 
 \section{Data}
-some pretty images to prove that it all worked.
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[height=16cm]{LSMdata.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:LSMdata} Whole mouse brain tomography.
+Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective).
+(A) 3D rendering of a parvalbumin-dTomato brain.
+(B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm.
+(C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C.
+Scale bar = 100 µm.}
+   \end{figure}
 
@@
 summary
+Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a combination of unprecedented spatio-temporal scale.
+The impact of this unique measurement technique will continue to revolutionise the field of whole brain connectomics due to its ability to record millions of images over the course of days or even weeks.
+The data produced in this fashion easily amounts several TB per data set and needs to be stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods.
+The latter need to be robust, standarised and fully automated processes yet allow for flexible, exploratory and tailored analysis.
 
 \section{Outlook}
-where are we going next with this?
+where are we going next with this? ask Leo Onofri and Giulio to contribute to this, issues data mangament, aberration correction
+mapping of complementary data sets obtained in the same system, eg structural connectivity, morphology and gene expression.
 
-%%-------------
-   %\begin{figure}
-   %\begin{center}
-   %\begin{tabular}{c}
-   %\includegraphics[height=5.5cm]{mcr3b.eps}
+\begin{landscape}
+\begin{table}[t!]
+	\centering
+		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
+		\begin{tabular}{llll}
+		Component												&	Manufacturer															& Part\# 								& Specifications 																													\\\hline
+		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 50mW, s-polarised																					 \\
+																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																					 \\
+																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised																		 \\
+																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised																		 \\
+																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised															 \\
+		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\
+		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V										 \\
+		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth							 \\
+		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																				 \\		
+		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)																	 \\
+																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)																			 \\
+		\multirow{3}{*}[0.6em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																										 \\
+																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s						\\
+																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ 		\\
+		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\
+		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\
+		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
+		\end{tabular}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+\begin{table}[t!]
+	\centering
+		\caption[Resolution]{Imaging properties and derived quantities.
+The thickness of the light sheet is approximately of the same size as the depth of field of the high NA detection lens.\label{tab:resolution}}
+		\begin{tabular}{lrlrl}
+		\multicolumn{5}{l}{Detection}\\\hline\hline
+		wavelength																	&	$\lambda$				&																																					& 0.5			& $\mu m$	\\
+		refractive index														&	n								&																																					& 1.45		& 				\\
+		numerical aperture 													&	$\text{NA}_d$		&																																					& 1				& 				\\
+		angular aperture 														& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
+		magnification 															& M								&																																					& 25			&					\\
+		tube lens 																	& $f_{\text{TL}}$	&																																					& 180			&	$mm$		\\
+		effective focal length objective						& EFL							& $=\nicefrac{f_{\text{TL}}}{M}$																					& 7.2			& $mm$		\\
+		diameter back focal plane										& BFP							& $= 2\text{EFL}\text{NA}_d$																							& 14.4		& $mm$		\\
+		field number																& FN							&																																					& 18			& $mm$		\\
+		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.72		& $mm$		\\
+		depth of field															& $\Delta$				& $=\nicefrac{\lambda*n}{(\text{NA}_d)^2}+ \nicefrac{n*e}{M \text{NA}_d}$	& 1.10 		& $\mu m$	\\ 
+		Airy radius lat.														& $r_A$						& $=\nicefrac{0.61 \lambda}{\text{NA}_d}$																	& 0.31		& $\mu m$	\\\\
+		\multicolumn{5}{l}{Excitation}\\\hline\hline
+		numerical aperture 													&	$\text{NA}_e$		&																																					& 0.3			& 				\\
+		magnification,	nominal											& m								&																																					& 10			&					\\
+		tube lens 																	& $f_{\text{tl}}$	&																																					& 100			&	$mm$		\\
+		effective focal length, objective						& efl							& $=\nicefrac{f_{\text{tl}}}{m}$																					& 20			& $mm$		\\
+		magnification, effective										& $m_e$						&	$=\nicefrac{f_{\text{tl}}}{\text{efl}}$																	& 5				&					\\
+		refractive index														&	$\eta$					&																																					& 1				& 				\\
+		beam radius																	& $\omega$				&																																					& 4.5			& $mm$		\\
+		%Airy radius lat.														& $r_a$						& $=\nicefrac{0.61 \lambda}{\text{NA}_e}$																	& 1.02		& $\mu m$	\\
+		min light sheet waist												& $\omega_0$			& $=\nicefrac{\lambda \text{efl}}{\pi \omega}$														& 1.41		& $\mu m$	\\
+		confocal parameter													& b								& $=\nicefrac{2 \pi \omega_0^2}{\lambda}$																	& 25.15		& $\mu m$	\\\\
+		\multicolumn{5}{l}{Camera}\\\hline\hline
+		cell size																		& e								&																																					& 6.5			&	$\mu m$	\\
+		effective area 															& $r^2$						&																																					& $13.3^2$	&	$\text{mm}^2$	\\
+		\end{tabular}
+\end{table}
+\end{landscape}
+
+		%\begin{landscape}
+%\begin{table}[t!]
+	%\centering
+		%\caption[Optical clearing]{Overview of tools and chemicals necessary for optical clearing.\label{tab:clearing}}
+		%\begin{tabular}{lllll}
+		%Component												&	Manufacturer															& Part 						& Specs 					& Specs\\\hline
+		%degasing chamber								& 																					&  	& 								& \\
+		%clearing chamber								& 3D printed custom design									&  	& 								& \\
+		%voltage supply									& 																					&  	& 								& \\
+		%soap circulation thingy					& 																					&  	& 								& \\
+		%shakey incubator								& 																					&  	& 								& \\
+		%all those chemicals							& 																					&  	& 								& \\
 		%\end{tabular}
-   %\end{center}
-   %\caption 
-   %{ \label{fig:example} %>> use \label inside caption to get Fig. number with \ref{}
-%Example of a figure caption. } 
-   %\end{figure} 
-%
+%\end{table}
+%\end{landscape}
+
 %%------------- 
@@
 Human Brain Project tutta la vita. 
+GARR gave us a beautiful 10gb fiber to cineca
+CINECA for hosting us on pico
 
@@
 
-\bibitem{Silvestri2012} Silvestri, L., Bria, A., Sacconi, L., Iannello, G. \& Pavone, F. S., XY. 	\emph{Opt Express} \textbf{20}, 20582-20598 (2012).
+\bibitem{Huisken2009} J. Huisken and D. Y. Stainier, ``Selective plane illumination microscopy techniques in developmental biology," \emph{Development} \textbf{136}(), 1963–1975 (2009).
+
+\bibitem{Chung2013} Chung, K., Wallace, J., Kim, S.
+Y., Kalyanasundaram, S., Andalman, A.
+S., Davidson, T.
+J.
+\& Deisseroth, K.
+Structural and molecular interrogation of intact biological systems.
+\emph{Nature} \textbf{497}, 332–33 (2013).
+
+\bibitem{Tomer2014} Tomer, R., Ye, L., Hsueh, B. \& Deisseroth, K. Advanced CLARITY for rapid and high-resolution imaging of intact tissues. \emph{nature protocols} \textbf{9}, 1682-1697 (2014).
+
+\bibitem{Silvestri2012} L. Silvestri, A. Bria, L. Sacconi, G. Iannello,  and F. S. Pavone,  ``" \emph{Opt Express} \textbf{20}(), 20582-20598 (2012).
+
+\bibitem{Frasconi2014} P. Frasconi, L. Silvestri, P. Soda, R. L. Cortini, F. S. Pavone and G. Iannello, ``" \emph{Bioinformatics} \textbf{30}(), i587-i593 (2014).
+
+\bibitem{Bria2012} A. Bria and G. Iannello,  ``TeraStitcher-A tool for fast automatic 3D-stitching of teravoxel-sized microscopy images,"  \emph{BMC bioinformatics} \textbf{13}(), 316 (2012).
 
@@
 \listoffigures
+%pannel1: optical pathway, drawing images from chamber, sample mirror photos
+%pannel2: software scheme
+%panel3: hardware connection scheme
+%panel4: data pipeline, graph data amount/time
+%panel5: experiment pipeline
+%panel6: images, tomos
+
 \listoftables
 
-\end{spacing}
+%\end{spacing}
 \end{document}

### 2015-01-13 latex-style-files-spie-manuscript/manuscript1.0.tex
- new y axis scale on mouse brain size graph to include ludos new calculations - marcel's text crudely inserted and needs extensive review

@@
 HERE WE'LL NEED SOME CHARACTERISATION DATA.
+An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.
 We use a tube lens of 200mm to create an image on a sCMOS camera (Orca Flash4.0, Hamamatsu).
@@
 The final code should be the common effort of all contributors each with their own know-how and practical expertise.
-We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods.
-
-The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their contribution to the software within a  standardized programming scheme by employing object oriented programming methodology.
-Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middleware facilitating message shipment and receival.
+Contemporary experimental research often relies on the acquisition and real-time processing of various data streams.
+In a given experiment, data may be acquired from multiple, even spatially separated sources, while individual processing steps may be computationally intensive and need to be distributed over several computers to be performed on-line.
+We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods, using the Murmex library.
+The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their respective contributions to the software within a standardized programming scheme by employing object oriented programming methodology (OOP).
+Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middle ware facilitating message shipment and receival.
 These layers of abstraction are mostly hidden for the developers.
 
-RabbitMQ
+\subsection{Object oriented programming}
+In OOP the developer creates classes, which are data structures that contain private data and methods that perform actions on the data.
+LabVIEW supports classes since 2006, but got to its mature form with LabVIEW 2009.
+When you create a subclass (child) from the toplevel class (parent), you automatically inherit its methods and data.
+Public methods can be called by the child, while private methods are only accessible by the owning class.
+A method implemented by the parent, which has the Dynamic Dispatch enabled and is public, can be replaced or augmented by the child.
+The parent can force the child to call its method or allow to ignore its code.
+A call to such a dynamic and public method is chained, it thus calls first the child method, which perform the action before or after calling the parent.
+The parent calls again its parent before or after executing its code and thus create a complete call chain for a single method.
+Next to the methods, the classes have private class data, which can only be accessed by the owning class.
+In order to give access to its data, a method needs to have methods accessing the data.
+The instance created at runtime from a class is called the object.
+Many objects can be made from a class, like many pies can be made from a pie recipe.
+Next, each object runs independently and contains its own data.
+
+\subsection{RabbitMQ}
 The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
@@
 
-Murmex
+\subsection{Murmex}
 The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer).
@@
 A software component that represents one, yet large, task, often uses only those previously four mentioned states.
-Examples for such a software component are the implementation a laser, translation stage and a camera.
+Examples for such a software component are the implementation of a laser, a translation stage and a camera.
+Such a component would implement in the Initialise method the initialisation of the communication port to the device, start activity in the Start method, stop activity in the Stop method and close the communication and free up memory in the Terminate.
+While each component is an autonomous program, variables on which each component might depend, have to be shared among the components.
+The Update method is used for this purpose, which allows components to update itself with new parameters and automatically forward these parameters to down- or upstream components by using a mapping script $(e.g.
+datastorage.total_movie_size=xres*yres*number_of_frames, where datastorage is the ID of the recipient, total_movie_size is the name of the parameter to be updated and xres, yres and number_of_frames are the names of parameters of the sender)$.
+Typically, a Murmex component streams data only to components listed as observers in its configuration file.
+Using this concept, components can be configured to form arbitrarily complex signal processing pipelines or networks.
+Once a component has been considered to be stable by the developer, an executable can be built.
+An important component named ServiceManager (also based on Murmex) can communicate to other ServiceManagers over the network or internet and can start remotely executables.
+This allows the user to start up a sophisticated configuration with multiple components as executable on different computers, but steered from one computer.
 
@@
 \section{Data}
+
 	\begin{figure}
@@
    \end{figure}
+
+	Everybody take a look at Figure\ref{fig:LSMdata} because it is the best we have.
 

### 2015-01-15 latex-style-files-spie-manuscript/manuscript1.0.tex
-deleted OOP paragraph -rewritten software into
-last commit before splitting between ludo and caroline

@@
 
+\section{Optical characterisation}
+
 \section{Software Management}
@@
 The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
-Another aspect of software design is avoiding redundancy in writing software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
-Writing well structured scientific software in a group of researchers is an often recurring challenge.
-The final code should be the common effort of all contributors each with their own know-how and practical expertise.
-Contemporary experimental research often relies on the acquisition and real-time processing of various data streams.
-In a given experiment, data may be acquired from multiple, even spatially separated sources, while individual processing steps may be computationally intensive and need to be distributed over several computers to be performed on-line.
-We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods, using the Murmex library.
-The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their respective contributions to the software within a standardized programming scheme by employing object oriented programming methodology (OOP).
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
+Our experimental research is based on the acquisition and real-time processing of various data streams.
+In a given experiment, data may be acquired from multiple, spatially separated sources, and individual processing steps can be computationally intensive and may need to be distributed over several computers to be performed at run-time.
+For those reasons we chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
+
+Another important aspect of software design is avoiding redundancy when scaling up the software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
+Writing well structured, scalable and easily maintainable scientific software in a group of researchers is an often recurring challenge.
+Object oriented programming is a programming paradigm whose main aspects are encapsulation, inheritance and polymorphism and a useful tool to address these challenges.
+
+Encapsulation refers to the concept that the entirety of software needed to say operate a microscope is broken up into self-contained modules.
+Those modules are user-defined data types and referred to as ``classes" where one instance of a class is called an ``object".
+For example a class could be the basic code to operate an  abstract laser while 5 instances of this class would be the necessary adjustments to operate 5 real world lasers from different manufacturers.
+This modular programming style keeps large amounts of software routines separate and less prone to conflict with each other.
+
+Classes are arranged in hierarchical structures and inheritance, the act of passing on knowledge from a ``parent" to a ``child" within a class, reduces the amount of programming required when increasingly more complex functions have to be added to the system.
+For example when specialised behaviour is added to the bottom of the hierarchy, only code regarding this very specific task has to be added while every other aspect is inherited from above.
+For example, if the code for a motor stage has already been implemented, a rotation stage can be interpreted as the child of a translation stage where the travel range is infinite.
+This increases code re-usability and saves time.
+
+In this way, the microscope software is decomposed into the communication and interaction of different objects through methods, bits of code, which act on each object's private data.
+
+The Murmex software development kit is based on the OOP paradigm and helps users to collaborate on software development by letting them independently create their respective contributions to the software in the form of new objects or methods within a standardized programming scheme.
+
+\subsection{RabbitMQ}
 Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middle ware facilitating message shipment and receival.
 These layers of abstraction are mostly hidden for the developers.
-
-\subsection{Object oriented programming}
-In OOP the developer creates classes, which are data structures that contain private data and methods that perform actions on the data.
-LabVIEW supports classes since 2006, but got to its mature form with LabVIEW 2009.
-When you create a subclass (child) from the toplevel class (parent), you automatically inherit its methods and data.
-Public methods can be called by the child, while private methods are only accessible by the owning class.
-A method implemented by the parent, which has the Dynamic Dispatch enabled and is public, can be replaced or augmented by the child.
-The parent can force the child to call its method or allow to ignore its code.
-A call to such a dynamic and public method is chained, it thus calls first the child method, which perform the action before or after calling the parent.
-The parent calls again its parent before or after executing its code and thus create a complete call chain for a single method.
-Next to the methods, the classes have private class data, which can only be accessed by the owning class.
-In order to give access to its data, a method needs to have methods accessing the data.
-The instance created at runtime from a class is called the object.
-Many objects can be made from a class, like many pies can be made from a pie recipe.
-Next, each object runs independently and contains its own data.
-
-\subsection{RabbitMQ}
 The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.

### 2015-01-15 latex-style-files-spie-manuscript/manuscript1.0.tex
- modification to PanelSample - citations - expansion on mounting

--- 2015-01-13 latex-style-files-spie-manuscript/manuscript1.0.tex
@@
-%  article.tex (Version 1.00, released 1 October 2013)
-%  LaTeX source file to demonstrate formatting for manuscripts 
-%  to be submitted to SPIE journals
-%  based on the class file spieman.cls, which requires 
-%  the following standard packages:  times.sty, float.sty, 
-%  ifthen.sty, cite.sty, color.sty, setspace.sty
-
 %  The following commands have been added in the SPIE class 
@@
 %  The bibliography style file is called spiejour.bst
-%  This article.tex file needs the following image files:
-%  mcr3b.eps
-%  fig2.eps
-%  satellite.eps
 
@@
 %% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%  The following command loads a graphics package to include images 
-%  in the document. It may be necessary to specify a DVI driver option,
-%  for example, [dvips], but that may be inappropriate for some LaTeX installations.
 
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light sheet microscopy, Big data, Optical clearing, Data management, whole brain imaging, rolling shutter, 7,8.}
+\keywords{Light sheet microscopy, big data, whole brain mounting, data management, whole brain imaging, rolling shutter, 7,8.}
 
@@
 \section{Introduction}%funnel shape
-\label{sect:intro}  % \label{} allows reference to this section
+\label{sect:intro}
 
@@
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
-This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap (Figure\ref{fig:Panel1},A).
+This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap (Figure\ref{fig:Panel0},A).
 Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise.
@@
 
-Here we will review a state-of-the-art LSFM, as it is implemented in our lab, which can be used to acquire 3D data sets of clarified mouse brains.
+Here we will describe a state-of-the-art LSFM, as it is implemented in our lab, which can be used to acquire 3D data sets of clarified mouse brains.
 The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples.
 After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days.
-In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task which in previous publication has too often been summarised in a single sentence.
+In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task whichhas too often been summarised in a single sentence.
 A systematic approach to handle, store and analyse the data is also given.
@@
 The final sentence of the introduction needs to be amazing.
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{PanelSampel.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.
+Excitation and detection occur on independent perpendicular axes.
+(B) Mounting of a claried brain.
+The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.}
+   \end{figure}
 
@@
 \section{Optical clearing and sample mounting}
-Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
+%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
 Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices.
@@
 These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
-
-A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
+%
+%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
 A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
@@
 To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation.
-The question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quarz cuvettes have been reported (cite), however these approaches are limited to much smaller sample volumes.
+While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
+The problem of sample mounting in light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample (Figure\ref{fig:Panel1},A).
+Most commonly the vertical direction is chosen.
+Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.
 
 We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},C) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
-A motorized x-, y-, z-, $\theta$-stage (M-122.2DD and M-116.DG, Physik Instrumente) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
+A motorized x-, y-, z-, $\theta$-stage (three M-122.2DD and one M-116.DG, Physik Instrumente) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
 The clarified brains are fixed with super glue to a coverslip which is slid into a custom made adapter and tightened with a plastic-capped screw.
@@
 The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
-Stable mounting is a key concern as a whole brain tomography can require image acquisition in excess of 3 days.
-We found that the effect of gravity, tissue shrinking/expansion and evaporation of PBS over such time spans are negligible, however, after that point the super glue is starting to dissolve.
 
@@
 The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A).
-The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components) and have each an output power of 50mW.
+The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components).
 The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series).
@@
 The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity.
-Due to the nonlinear response of the AOTF we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a linear look-up table through interpolation.
+Due to the nonlinear response of the AOTF we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output.
 The zero order light is blocked by an iris.
-An electro-optical laser modulator acts like a wave plate with electrically controlled retardation and rapidly rotates (hundreds ns/ms?) the input polarisation of the excitation light by $90\degree$.
+An electro-optical laser modulator acts like a wave plate with electrically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
 The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system.
@@
 After the laser modulator the excitation beam is further expanded by a factor of 2 (f100, f200) with two achromatic doublets.
+
 From here on three different light paths can be chosen through flip mirrors.
@@
 This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
+
 The scan mirror surface is reimaged with a telescope (f50, f100) onto the back aperture a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
 The two excitation objectives are designed for air immersion.
-A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the glue/mounting of the lens elements which is compromised by the organic solvent.
+A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent.
 The sample chamber is tightly bolted  to the optical breadboard while soft connections through silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages.
@@
 		%objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
+		%exposure time of single line affects how many are exposed at same time, confocality by synchronisation- not exactly
 
@@
 
-For image acquisition the sample is slowly translated at a fixed speed along the detection axis through the light sheet.
+%For image acquisition the sample is slowly translated at a fixed speed along the detection axis through the light sheet.
 Images are recorded at a frame rate of 44Hz in different planes along the optical axis of the detection lens (here z) to acquire a stack.
@@
 After this initial alignment the first excitation objective was then placed into the beam path and brought to focus onto the sample mirror, which was adjusted to reflect the light back into the same objective.
-Using a shear plate and a polarising beam splitter cube the back reflected light was qualitatively checked for collimation to ensure the sample mirror was correctly placed in the focal plane of the objective (Figure\ref{fig:alignment2},B).
+Using a shear plate and a beam splitter cube the back reflected light was qualitatively checked for collimation to ensure the sample mirror was correctly placed in the focal plane of the objective (Figure\ref{fig:alignment2},B).
 The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C).
 This time collimation was checked with the light going through both objectives and so their confocal placement was insured.
-The microscope was then aligned recursively by starting at the confocal point between the objectives and placing successively lens after lens in the up-stream direction.
+The microscope was then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source.
 Finally, the sample mirror was position in reflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
 
-\section{Software Management}
+\section{Optical characterisation}
 
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{connectivity.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:connectivity} Connectivity scheme} 
-   \end{figure}
-
-%Here we describe all things software control and communication, components and their interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
-
-%Based on a modular scheme (OOP) using Murmex development kit
-%Separate building blocks control different components of the microscope
-%Hierarchical structure coordinates complex tasks
-%Communication takes place through RabbitMQ server (open source message-oriented middleware) using the LabbitMQ library
-
-The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
-Another aspect of software design is avoiding redundancy in writing software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
-Writing well structured scientific software in a group of researchers is an often recurring challenge.
-The final code should be the common effort of all contributors each with their own know-how and practical expertise.
-We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods.
-
-The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their contribution to the software within a  standardized programming scheme by employing object oriented programming methodology.
-Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middleware facilitating message shipment and receival.
+%\section{Software Management}
+%
+	%\begin{figure}
+   %\begin{center}
+   %\begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{connectivity.eps}
+   %\end{tabular}
+   %\end{center}
+   %\caption{\label{fig:connectivity} Connectivity scheme} 
+   %\end{figure}
+%
+%%Here we describe all things software control and communication, components and their interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
+%
+%
+%%Based on a modular scheme (OOP) using Murmex development kit
+%%Separate building blocks control different components of the microscope
+%%Hierarchical structure coordinates complex tasks
+%%Communication takes place through RabbitMQ server (open source message-oriented middleware) using the LabbitMQ library
+%
+%The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
+Our experimental research is based on the acquisition and real-time processing of various data streams.
+In a given experiment, data may be acquired from multiple, spatially separated sources, and individual processing steps can be computationally intensive and may need to be distributed over several computers to be performed at run-time.
+For those reasons we chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
+%
+%Another important aspect of software design is avoiding redundancy when scaling up the software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
+Writing well structured, scalable and easily maintainable scientific software in a group of researchers is an often recurring challenge.
+Object oriented programming is a programming paradigm whose main aspects are encapsulation, inheritance and polymorphism and a useful tool to address these challenges.
+%
+%Encapsulation refers to the concept that the entirety of software needed to say operate a microscope is broken up into self-contained modules.
+Those modules are user-defined data types and referred to as ``classes" where one instance of a class is called an ``object".
+For example a class could be the basic code to operate an  abstract laser while 5 instances of this class would be the necessary adjustments to operate 5 real world lasers from different manufacturers.
+This modular programming style keeps large amounts of software routines separate and less prone to conflict with each other.
+%
+%Classes are arranged in hierarchical structures and inheritance, the act of passing on knowledge from a ``parent" to a ``child" within a class, reduces the amount of programming required when increasingly more complex functions have to be added to the system.
+For example when specialised behaviour is added to the bottom of the hierarchy, only code regarding this very specific task has to be added while every other aspect is inherited from above.
+For example, if the code for a motor stage has already been implemented, a rotation stage can be interpreted as the child of a translation stage where the travel range is infinite.
+This increases code re-usability and saves time.
+%
+%In this way, the microscope software is decomposed into the communication and interaction of different objects through methods, bits of code, which act on each object's private data.
+%
+%The Murmex software development kit is based on the OOP paradigm and helps users to collaborate on software development by letting them independently create their respective contributions to the software in the form of new objects or methods within a standardized programming scheme.
+%
+%\subsection{RabbitMQ}
+%Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middle ware facilitating message shipment and receival.
 These layers of abstraction are mostly hidden for the developers.
-
-RabbitMQ
-The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
+%The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
 The message-based communication allows for buffered, asynchronous and reliable message communication between several software components.
@@
 Messages can be sent to a single recipient by its ID or sent to all available components.
-
-Murmex
-The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer).
+%
+%\subsection{Murmex}
+%The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer).
 A finite state machine resembles the Strategy pattern [Design Patterns: Elements of Reusable Object-Oriented Software, E.
@@
 A software component that represents one, yet large, task, often uses only those previously four mentioned states.
-Examples for such a software component are the implementation a laser, translation stage and a camera.
-
-\section{Data Management}
-	\subsection{Pipeline}
-
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{DataFlow.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:DataFlow} Scheme of the data flow.
+Examples for such a software component are the implementation of a laser, a translation stage and a camera.
+Such a component would implement in the Initialise method the initialisation of the communication port to the device, start activity in the Start method, stop activity in the Stop method and close the communication and free up memory in the Terminate.
+%While each component is an autonomous program, variables on which each component might depend, have to be shared among the components.
+The Update method is used for this purpose, which allows components to update itself with new parameters and automatically forward these parameters to down- or upstream components by using a mapping script $(e.g.
+datastorage.total_movie_size=xres*yres*number_of_frames, where datastorage is the ID of the recipient, total_movie_size is the name of the parameter to be updated and xres, yres and number_of_frames are the names of parameters of the sender)$.
+%Typically, a Murmex component streams data only to components listed as observers in its configuration file.
+Using this concept, components can be configured to form arbitrarily complex signal processing pipelines or networks.
+Once a component has been considered to be stable by the developer, an executable can be built.
+An important component named ServiceManager (also based on Murmex) can communicate to other ServiceManagers over the network or internet and can start remotely executables.
+This allows the user to start up a sophisticated configuration with multiple components as executable on different computers, but steered from one computer.
+%
+%
+%
+%
+%\section{Data Management}
+	%\subsection{Pipeline}
+	%
+	%\begin{figure}
+   %\begin{center}
+   %\begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{DataFlow.eps}
+   %\end{tabular}
+   %\end{center}
+   %\caption{\label{fig:DataFlow} Scheme of the data flow.
 (A) Data streaming on the microscope.
@@
 (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
-   \end{figure}
-
-%\begin{landscape}
-\begin{table}%[t!]
-	\centering
-		\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
-		\begin{tabular}{lrl}
-		frame rate																	& 44			& Hz	\\
-		size of 1 frame															& 8				& MB	\\
-		frames per stack														& 3900		& 		\\
-		size of original stack											& 30.4		& GB	\\
-		size of converted stack											& 3				& GB	\\
-		stack acquisition time											& 88.6		& s		\\
-		stack conversion time												& 140			& s		\\
-		time ratio conversion/ acquisition					& 1.6			& 		\\
-		data production rate												& +1.2		&	TB/h\\
-		data conversion rate												& -0.7		&	TB/h\\
-		net rate																		& +0.5		&	TB/h\\
-		SSD RAID																		& 10.9		& TB	\\
-		max acquisition time to fill up SSDs				& 21			& h		\\
-		max tomo size to fill up SSDs								& 25.4		& TB	\\
-		\end{tabular}
-\end{table}
-%\end{landscape}
-The unprecedented amount of data routinely produced by light sheet microscopy presents challenges to the traditional way we interact with our data.
+   %\end{figure}
+	%
+%%\begin{landscape}
+%\begin{table}%[t!]
+	%\centering
+		%\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
+		%\begin{tabular}{lrl}
+		%frame rate																	& 44			& Hz	\\
+		%size of 1 frame															& 8				& MB	\\
+		%frames per stack														& 3900		& 		\\
+		%size of original stack											& 30.4		& GB	\\
+		%size of converted stack											& 3				& GB	\\
+		%stack acquisition time											& 88.6		& s		\\
+		%stack conversion time												& 140			& s		\\
+		%time ratio conversion/ acquisition					& 1.6			& 		\\
+		%data production rate												& +1.2		&	TB/h\\
+		%data conversion rate												& -0.7		&	TB/h\\
+		%net rate																		& +0.5		&	TB/h\\
+		%SSD RAID																		& 10.9		& TB	\\
+		%max acquisition time to fill up SSDs				& 21			& h		\\
+		%max tomo size to fill up SSDs								& 25.4		& TB	\\
+		%\end{tabular}
+%\end{table}
+%%\end{landscape}
+%The unprecedented amount of data routinely produced by light sheet microscopy presents challenges to the traditional way we interact with our data.
 Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires a professional approach to centralised network architecture.
@@
 Mention graphical processing unit and cores/processors/RAM of work station?
-
-With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
+	%
+%With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
 Based on a frame rate of 44Hz each stack takes approximately 1.5 minutes to acquire and the SSD RAID fills up with a data writing rate of 1.2TB/h.
@@
 A whole mouse brain tomography would take 3 days of uninterrupted measuring yet with the necessary breaks for data transfer this time is easily doubled to tripled.
-
-	\subsection{Stitching and visualisation}
-
-Given the limited field of view of the microscope, the acquisition of macroscopic specimens required many parallel image stacks to cover all the volume.
+%
+	%\subsection{Stitching and visualisation}
+	%
+%Given the limited field of view of the microscope, the acquisition of macroscopic specimens required many parallel image stacks to cover all the volume.
 Thus, in order to achieve a 3D image of the whole specimen from raw data, the Terastitcher\cite{Bria2012} has been recently proposed, i.e.
@@
 For these reasons, we extended the Terastitcher functionalities introducing the two following additional features: i) stitching of a specimen partitioned in a number of overlapping layers for the hippocampus reconstruction and, ii) coping with images containing more than one channel for the human brain tomography.
-With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depicts in Fig.1 the adopted strategy.
+%With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depicts in Fig.1 the adopted strategy.
 First of all, the various input layers, each of which is composed of several parallel overlapping stacks, are separately stitched by using the existing Terastitcher tool.
@@
 Finally, we note that due to the repositioning of each layer, the volume containing the reconstructed specimen might contain empty regions, which are thereby filled with black voxels.
-Turning our attention to the second additional feature, that is handling multi-channel images, the Terastitcher has been extended so that the MIP-NCC algorithm used for displacement computation can work on an image, which can be either
-the fusion of the input channels or one of the input channels.
+%Turning our attention to the second additional feature, that is handling multi-channel images, the Terastitcher has been extended so that the MIP-NCC algorithm used for displacement computation can work on an image, which can be either
+%the fusion of the input channels or one of the input channels.
 This permits to privilege the channel with more information content over the other channels as well as discard noisy channels.
 Note that the reconstructed 3D image can be produced with the same channel composition of raw data.
+%
+%
+	%\subsection{Example for postprocessing: Automated cell counting}
+	%See Reference\cite{Frasconi2014} for details.
+%
+%
+\section{Data}
 
-	\subsection{Example for postprocessing: Automated cell counting}
-	See Reference\cite{Frasconi2014} for details.
-
-\section{Data}
 	\begin{figure}
@@
 		Component												&	Manufacturer															& Part\# 								& Specifications 																													\\\hline
-		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 50mW, s-polarised																					 \\
+		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																					 \\
 																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																					 \\
@@
 
-\bibitem{Huisken2009} J. Huisken and D. Y. Stainier, ``Selective plane illumination microscopy techniques in developmental biology," \emph{Development} \textbf{136}(), 1963–1975 (2009).
+\bibitem{Huisken2009} J. Huisken and D. Y. Stainier, ``Selective plane illumination microscopy techniques in developmental biology," \emph{Development} \textbf{136}(12), 1963–1975 (2009).
 
-\bibitem{Chung2013} Chung, K., Wallace, J., Kim, S.
-Y., Kalyanasundaram, S., Andalman, A.
-S., Davidson, T.
+\bibitem{Chung2013} K.
+Chung, J.
+Wallace, S.
+Y.
+Kim, S.
+Kalyanasundaram, A.
+S.
+Andalman, T.
 J.
-\& Deisseroth, K.
-Structural and molecular interrogation of intact biological systems.
-\emph{Nature} \textbf{497}, 332–33 (2013).
+Davidson and K.
+Deisseroth, ``Structural and molecular interrogation of intact biological systems," \emph{Nature} \textbf{497}(7449), 332–33 (2013).
 
-\bibitem{Tomer2014} Tomer, R., Ye, L., Hsueh, B. \& Deisseroth, K. Advanced CLARITY for rapid and high-resolution imaging of intact tissues. \emph{nature protocols} \textbf{9}, 1682-1697 (2014).
+\bibitem{Tomer2014} R. Tomer, L. Ye, B. Hsueh and K. Deisseroth, ``Advanced CLARITY for rapid and high-resolution imaging of intact tissues," \emph{nature protocols} \textbf{9}(7), 1682-1697 (2014).
 
-\bibitem{Silvestri2012} L. Silvestri, A. Bria, L. Sacconi, G. Iannello,  and F. S. Pavone,  ``" \emph{Opt Express} \textbf{20}(), 20582-20598 (2012).
+\bibitem{Kaufmann2012} A.
+Kaufmann, M.
+Mickoleit, M.
+Weber and J.
+Huisken, ``Multilayer mounting enables long-term imaging of zebrafish development in a light sheet microscope," \emph{Development} \textbf{139}(17), 3242-3247 (2012).
+
+\bibitem{Pitrone2013} P.
+Pitrone, J.
+Schindelin, L.
+Stuyvenberg, S.
+Preibisch, M.
+Weber, K.
+W.
+Eliceiri, J.
+Huisken and P.
+Tomancak, ``OpenSPIM-an open access platform for light sheet microscopy," \emph{arXiv} reprint arXiv:1302.1987, 3242-3247 (2013).
+
+\bibitem{Olarte2012} O.
+E.
+Olarte, J.
+Licea-Rodriguez, J.
+A.
+Palero, E.
+J.
+Gualda, D.
+Artigas, J.
+Mayer and P.
+Loza-Alvarez, ``Image formation by linear and nonlinear digital scanned light-sheet fluorescence microscopy with Gaussian and Bessel beam profiles," \emph{Biomedical optics express} \textbf{3}(7), 1492-1505 (2012).
+
+\bibitem{Silvestri2012} L.
+Silvestri, A.
+Bria, L.
+Sacconi, G.
+Iannello,  and F.
+S.
+Pavone,  ``Confocal light sheet microscopy: micron-scale neuroanatomy of the entire mouse brain," \emph{Opt Express} \textbf{20}(18), 20582-20598 (2012).
 
@@
 
-\bibitem{Bria2012} A. Bria and G. Iannello,  ``TeraStitcher-A tool for fast automatic 3D-stitching of teravoxel-sized microscopy images,"  \emph{BMC bioinformatics} \textbf{13}(), 316 (2012).
+\bibitem{Bria2012} A. Bria and G. Iannello,  ``TeraStitcher-A tool for fast automatic 3D-stitching of teravoxel-sized microscopy images,"  \emph{BMC bioinformatics} \textbf{13}(1), 316 (2012).
 

### 2015-01-20 latex-style-files-spie-manuscript/manuscript1.1_Ludo.tex
modified manuscript called manuscript1.1_Ludo.tex

--- 2015-01-15 latex-style-files-spie-manuscript/manuscript1.0.tex
@@
 
-\section{Software Management}
+\section{Microscope management software}
 
@@
 
-The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
-Our experimental research is based on the acquisition and real-time processing of various data streams.
-In a given experiment, data may be acquired from multiple, spatially separated sources, and individual processing steps can be computationally intensive and may need to be distributed over several computers to be performed at run-time.
-For those reasons we chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
+\subsection{General design principles}
 
-Another important aspect of software design is avoiding redundancy when scaling up the software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
-Writing well structured, scalable and easily maintainable scientific software in a group of researchers is an often recurring challenge.
-Object oriented programming is a programming paradigm whose main aspects are encapsulation, inheritance and polymorphism and a useful tool to address these challenges.
+The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated together and operated through a custom-made software.
+Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing proper synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging.
+The overall architecture of the software and its practical implementation were chosen to satisfy several principles:
 
-Encapsulation refers to the concept that the entirety of software needed to say operate a microscope is broken up into self-contained modules.
-Those modules are user-defined data types and referred to as ``classes" where one instance of a class is called an ``object".
-For example a class could be the basic code to operate an  abstract laser while 5 instances of this class would be the necessary adjustments to operate 5 real world lasers from different manufacturers.
-This modular programming style keeps large amounts of software routines separate and less prone to conflict with each other.
+\begin{itemize}
+\item{\emph{User-friendliness}.
+The light sheet microscope here presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by researchers with no expertise in optics and/or software development.}
+\item{\emph{Working in a distributed environment}.
+The apparatus should deal with many independent hardware components, and with several data streams (see below).
+Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
+\item{\emph{Robustness and ease of maintenance}.
+Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
+Furthermore, developers must be able to fix existing code or to develop new one without having to change the whole software.}
+\item{\emph{Reusability and scalability}.
+When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch is pure loss of time.
+Writing well structured, scalable and easily maintainable scientific software can help avoiding redundancy and boosting up productivity.}
+\end{itemize}
 
-Classes are arranged in hierarchical structures and inheritance, the act of passing on knowledge from a ``parent" to a ``child" within a class, reduces the amount of programming required when increasingly more complex functions have to be added to the system.
-For example when specialised behaviour is added to the bottom of the hierarchy, only code regarding this very specific task has to be added while every other aspect is inherited from above.
-For example, if the code for a motor stage has already been implemented, a rotation stage can be interpreted as the child of a translation stage where the travel range is infinite.
-This increases code re-usability and saves time.
+Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
+An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
+This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
+Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
+The graphical user interface (GUI) provides intuitive control of the apparatus as well as deep personalization.
+In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
+Both GUIs and code are developed according to the LabVIEW Style Guide \cite{}.
 
-In this way, the microscope software is decomposed into the communication and interaction of different objects through methods, bits of code, which act on each object's private data.
+\subsection{Murmex}
+To let the software operate efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used.
+This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardized programming scheme.
 
-The Murmex software development kit is based on the OOP paradigm and helps users to collaborate on software development by letting them independently create their respective contributions to the software in the form of new objects or methods within a standardized programming scheme.
-
-\subsection{RabbitMQ}
-Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middle ware facilitating message shipment and receival.
+Basically, Murmex creates distributed finite state machines.
+These are design patterns in which one component proceed from one particular state to another based on the message it receives either from itself or from other components.
+For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middleware facilitating message shipment and receival.
 These layers of abstraction are mostly hidden for the developers.
@@
 Messages are routed by the broker to the specific software component by its ID.
-In order to access the functionality of RabbitMQ, the application programming interface (API) \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ} was used, which uses .NET calls for sending and receiving messages to and from the RabbitMQ broker.
-Messages can be sent to a single recipient by its ID or sent to all available components.
+The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
 
-\subsection{Murmex}
-The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer).
-A finite state machine resembles the Strategy pattern [Design Patterns: Elements of Reusable Object-Oriented Software, E.
-Gamma, R.
-Helm, R.
-Johnson, J.
-Vlissides, 1994], which lets the software of one component proceed from one particular state to another based on message it receives from itself or other components (for example to execute Initialise, Start, Proceed, Stop, Terminate).
-In each state it executes the code for that state only, but flexible execution patterns are possible.
-It thus allows for predictable behaviour, without knowing the exact code.
-Murmex has twelve pre-defined common states (e.g.
-Initialise, Start, Stop, Terminate) and a generic state for implementing custom states.
-A software component that represents one, yet large, task, often uses only those previously four mentioned states.
-Examples for such a software component are the implementation of a laser, a translation stage and a camera.
-Such a component would implement in the Initialise method the initialisation of the communication port to the device, start activity in the Start method, stop activity in the Stop method and close the communication and free up memory in the Terminate.
-While each component is an autonomous program, variables on which each component might depend, have to be shared among the components.
-The Update method is used for this purpose, which allows components to update itself with new parameters and automatically forward these parameters to down- or upstream components by using a mapping script $(e.g.
-datastorage.total_movie_size=xres*yres*number_of_frames, where datastorage is the ID of the recipient, total_movie_size is the name of the parameter to be updated and xres, yres and number_of_frames are the names of parameters of the sender)$.
-Typically, a Murmex component streams data only to components listed as observers in its configuration file.
-Using this concept, components can be configured to form arbitrarily complex signal processing pipelines or networks.
-Once a component has been considered to be stable by the developer, an executable can be built.
-An important component named ServiceManager (also based on Murmex) can communicate to other ServiceManagers over the network or internet and can start remotely executables.
-This allows the user to start up a sophisticated configuration with multiple components as executable on different computers, but steered from one computer.
+Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states.
+Usually, just a few of this states are actually used in standard application.
+An example of a standard implementation of the Murmex state machines for a scanning system is shown in Fig.
+BLABLA.
+Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file.
+Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet.
+A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely.
+This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.
+
+\subsection{System timing and software organization}
+
+A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig.
+BLABLA, respectively.
+One personal computer (Dell XXXXX) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Dell YYYYY) to handle and manage the enormous streams of data produced (see next section).
+Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI XXXX, National Instruments, Austin, USA).
+
+Synchronization of the camera rolling shutter to the scanning of the light sheet is achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
+In particular, the HSYNC signal from the camera is used, providing a true-type-logic (TTL) pulse everytime the rolling shutter steps from one line to the next one.
+This trigger signal is used as a clock by the DAQ board, so that the line producing the light sheet moves step by step with the rolling shutter.
+The same HSYNC signal is used to trigger the DAQ digital signal sent to the electro-optic laser modulator.
+In this case, since at each position of the scanning line the modulator should go trough at least two states (vertical polarization and horizontal polarization), HSYNC is used as a trigger while the clock used is the (much faster) internal clock of the DAQ board.
+
+Each hardware component (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component.
+Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just send analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Beyond hardware-related software, two additional Murmex components (named Stack and Tomo) orchestrate the operation of the entire system.
+
+The stack component is used to acquire single image stacks along the $z$ direction, and to this aim send specific messages to coordinate the Camera and the Stages components.
+Stacks are collected by moving continuously the sample along $z$ while keeping the camera acquiring in free run.
+The translation speed is such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
+The stack component also specify the name of the file where data are saved.
+
+The tomo component is used to image the entire sample by collecting many adjacent, parallel, partially-overlapping stacks.
+To this aim it exchanges messages with the Stack and the Stages components.
+The user can specify the volume to be imaged either by inserting the maximum $x$, $y$ and $z$ coordinates of a parallelepiped, or by providing a text file with the list of stacks to be collected ($x$ and $y$ coordinates, starting and ending $z$s).
+The Tomo component also inform the experimenter about the state of the acquisition by sending an email when it's finished or if any trouble is experienced.
+
+All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
+Beacuse of its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
 
 \section{Data Management}
-	\subsection{Pipeline}
+
+The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
+Since the clearing procedure with CLARITY produces a linear expansion of about $1.2\times$ \cite{Costantini}, the volume of a clarified mouse brain can be estimated as $\simeq 0.9$ $\text{cm}^3$, while that of a parallelepiped encompassing the sample is expanded to $\simeq 1.6$ $\text{cm}^3$.
+Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.26\times0.26\times2$ $\mu\text{m}^3$.
+This means that a cleared mouse brain will be represented with about 6 TeraVoxels, while a parallelepiped encompassing the brain will result in 10.8 TeraVoxels.
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 12 TB for the whole brain "alone" and 21.6 TB for the parallelepiped (see Table XXXX).
+
+This unprecedented amount of data challenges to the traditional way we interact with our data.
+Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
+
+\subsection{Data handling and storage}
+
+The camera used in our light sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the datastream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
+Although this is already a large and expensive system for the current SSD technology, it is way smaller than the size of the raw datasets produced in each tomography.
+We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable.
+The NAS operates in a safer data modality (RAID 5) with 32 TB of useful disk space.
+The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main italian supercomputing center).
+
+The camera used in our light sheet microscope has a dedicated work station with a CameraLink card and 10.9TB of SSD space in RAID 0 configuration.
+This finite storage capacity is further expanded by a network-attached storage (NAS) of 32.4TB (Figure\ref{fig:DataFlow}).
+The SSDs and the NAS are connected via a 10Gb bandwidth connection using a 10Gb switch and a 10Gb optical fibre connects our lab to the supercomputing centre CINECA in Bologna.
+Mention PICO system/storage analysis capacity there?
+Mention graphical processing unit and cores/processors/RAM of work station?
+
+With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
+Based on a frame rate of 44Hz each stack takes approximately 1.5 minutes to acquire and the SSD RAID fills up with a data writing rate of 1.2TB/h.
+If no further measures are taken the SSD RAID of 10.9TB would be filled up in just 9h.
+A custom compression script written in Python serves the triple purpose of translating the images from the proprietary Hamamatsu file format to 3D tif, to transfer the data from the SSD RAID to a network attached storage (NAS) and to reduce the raw data size by first, digitally downsampling the image resolution and second, applying a lossless compression to the tif images.
+This leads to a overall reduction of data size by a factor of ten, each stack now taking up only 3GB of disc space, albeit at a much slower conversion rate (-0.7TB/h) than the rate at which data is written to the SSD thus representing the most serious bottleneck to our data production pipeline.
+The SSD RAID fills up at a rate of 0.5TB/h which means the total acquisition time is limited to less than 24h and a total tomo size of just over 25TB.
+After this time acquisition has to be halted until the slower conversion process has caught up and freed the SSD RAID before data acquisition can start again.
+A whole mouse brain tomography would take 3 days of uninterrupted measuring yet with the necessary breaks for data transfer this time is easily doubled to tripled.
 
@@
 %\end{landscape}
-The unprecedented amount of data routinely produced by light sheet microscopy presents challenges to the traditional way we interact with our data.
-Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires a professional approach to centralised network architecture.
-The following paragraphs give an idea of the considerations one has to give to the big data volume problem.
-The camera used in our light sheet microscope has a dedicated work station with a CameraLink card and 10.9TB of SSD space in RAID 0 configuration.
-This finite storage capacity is further expanded by a network-attached storage (NAS) of 32.4TB (Figure\ref{fig:DataFlow}).
-The SSDs and the NAS are connected via a 10Gb bandwidth connection using a 10Gb switch and a 10Gb optical fibre connects our lab to the supercomputing centre CINECA in Bologna.
-Mention PICO system/storage analysis capacity there?
-Mention graphical processing unit and cores/processors/RAM of work station?
-
-With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
-Based on a frame rate of 44Hz each stack takes approximately 1.5 minutes to acquire and the SSD RAID fills up with a data writing rate of 1.2TB/h.
-If no further measures are taken the SSD RAID of 10.9TB would be filled up in just 9h.
-A custom compression script written in Python serves the triple purpose of translating the images from the proprietary Hamamatsu file format to 3D tif, to transfer the data from the SSD RAID to a network attached storage (NAS) and to reduce the raw data size by first, digitally downsampling the image resolution and second, applying a lossless compression to the tif images.
-This leads to a overall reduction of data size by a factor of ten, each stack now taking up only 3GB of disc space, albeit at a much slower conversion rate (-0.7TB/h) than the rate at which data is written to the SSD thus representing the most serious bottleneck to our data production pipeline.
-The SSD RAID fills up at a rate of 0.5TB/h which means the total acquisition time is limited to less than 24h and a total tomo size of just over 25TB.
-After this time acquisition has to be halted until the slower conversion process has caught up and freed the SSD RAID before data acquisition can start again.
-A whole mouse brain tomography would take 3 days of uninterrupted measuring yet with the necessary breaks for data transfer this time is easily doubled to tripled.
 
@@
 
+\bibitem{castagna1997object} G. Castagna, \emph{``Object-Oriented Programming A Unified Foundation,"} Birkh{\"a}user, Boston (1997).
+
+\bibitem{Costantini} I.
+Costantini, J.-P.
+Ghobril, A.
+P.
+Di Giovanna, A.
+L.
+Allegra Mascaro, L.
+Silvestri, M.
+C.
+Muellenbroich, L.
+Onofri, V.
+Conti, F.
+Vanzi, L.
+Sacconi, R.
+Guerrini, H.
+Markram, G.
+Iannello, and F.
+S.
+Pavone, \emph{submitted}.
+
+\bibitem{Kovacevic2005} N.
+Kovacevic, J.
+T.
+Henderson, E.
+Chan, N.
+Lifshitz, J.
+Bishop, A.
+C.
+Evans, R.
+M.
+Henkelman, and X.
+J.
+Chen, "A Three-dimensional MRI Atlas of the Mouse Brain with Estimates of the Average and Variability", \emph{Cereb.
+Cortex} \textbf{15}(5), 639-45 (2005).
+
 \end{thebibliography}

### 2015-01-20 latex-style-files-spie-manuscript/manuscript1.0.tex

@@
 
-Here we will describe a state-of-the-art LSFM, as it is implemented in our lab, which can be used to acquire 3D data sets of clarified mouse brains.
+Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains.
 The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples.
@@
    \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.
-Excitation and detection occur on independent perpendicular axes.
-(B) Mounting of a claried brain.
+Excitation (blue) and fluorescence detection (green) occur on independent, perpendicular axes.
+(B) Mounting of a clarified, fluorescently labelled brain.
 The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.}
@@
 
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel1.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:Panel1} Schematic of light sheet microscopy.
-(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
-The clarified, fluorescently-labelled brain (B) is mounted on a Teflon cylinder inside the watertight chamber (D) and can be translated and rotated freely with piezo motors (D).
-The sample is glued onto a cover slip which is slid into a custom made adapter mount that is inserted into the Teflon cylinder (E).}
-   \end{figure}
-
-\section{Optical clearing and sample mounting}
+\section{Sample mounting}
 %Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
@@
 
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{NuPanel1.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:Panel1} Schematic of light sheet microscopy.
+(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
+The custom-made sample chamber is assembled with silicone bellows and seal rings.
+The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber (C) and can be translated and rotated freely with piezo motors (D).}
+   \end{figure}
+
 To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation.
 While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
-The problem of sample mounting in light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample (Figure\ref{fig:Panel1},A).
+The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample.
 Most commonly the vertical direction is chosen.
@@
 
-We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},C) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
-A motorized x-, y-, z-, $\theta$-stage (three M-122.2DD and one M-116.DG, Physik Instrumente) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
-The clarified brains are fixed with super glue to a coverslip which is slid into a custom made adapter and tightened with a plastic-capped screw.
-The adaptor is then inserted into the Teflon cylinder (Figure\ref{fig:Panel1},E) with the coverslip being positioned on the far side of the detection objective.
+To acquire whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B).
+The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip.
+The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw.
+The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective.
 Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.
+
+We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
+The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:Panel1},B).
+All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
+In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:Panel1},C).
 The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
+A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
 
@@
 The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity.
-Due to the nonlinear response of the AOTF we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output.
+Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output.
 The zero order light is blocked by an iris.
-An electro-optical laser modulator acts like a wave plate with electrically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
+An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
 The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system.
 First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
-A digital line is used to electronically control the frequency of the polarisation shift.
-After the laser modulator the excitation beam is further expanded by a factor of 2 (f100, f200) with two achromatic doublets.
+A digital line is used to electronically control the frequency with which the polarisation is changed.
+After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).
 
@@
 This diameter variation translates to different fields of view later on in the detection path.
-The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two excitation arms which are built to be identical.
+The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms.
 The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo).
 The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.
-The light sheet is generated digitally by scanning the excitation beam with a sawtooth signal applied to the galvo.
-This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
 
-The scan mirror surface is reimaged with a telescope (f50, f100) onto the back aperture a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
-The two excitation objectives are designed for air immersion.
+The scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
+The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber.
 A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent.
-The sample chamber is tightly bolted  to the optical breadboard while soft connections through silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages.
-All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
-In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber.
+The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective.
+%This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
 
@@
 
-		Fluorescence is collected on a axis perpendicular to the excitation with an objective that was specifically designed for immersion in clearing solutions of various refractive indices.
+Fluorescence detection in light sheet microscopy is analogous to conventional wide-field microscopy.
+Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
 The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP).
 To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
-HERE WE'LL NEED SOME CHARACTERISATION DATA.
+A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a camera chip of over 4 megapixels.
+In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
+In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor.
+With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms.
+Setting the line exposure time to 3ms results in approx.
+300 lines being simultaneously exposed.
+This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $80\micro m$ in the sample space.
+With those values the camera acquires images at a frame rate of 44Hz.
+Synchronisation of the rolling shutter with the scanned illumination beam results in confocal line detection\cite{Baumgart2012}.
+
+\section{Optical characterisation}
 An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.
-We use a tube lens of 200mm to create an image on a sCMOS camera (Orca Flash4.0, Hamamatsu).
-A fluorescent filter is used to block out any excitation light.
-The camera chip of over 4 megapixels is read out in one sweep from top to bottom in the so-called light sheet mode in which only a subset of horizontal lines is exposed and consequently read out and any time.
-This sweeping line exposure creates a virtual confocal slit.
-Confocality is achieved by synchronising a single line which generates the light sheet with the exposure of a few lines on the CMOS chip.
 
-%For image acquisition the sample is slowly translated at a fixed speed along the detection axis through the light sheet.
-Images are recorded at a frame rate of 44Hz in different planes along the optical axis of the detection lens (here z) to acquire a stack.
-After successful stack acquisition the sample is moved to an adjacent vertical position (here y) to acquire the next image stack.
-Once the entire vertical slice composed of z stacks is acquired the sample is moved to an incremented x position.
-In this way the entire cubic volume is imaged.
+	\subsection{Contrast}
+	\subsection{Signal-to-noise ratio}
+	\subsection{Optical sectioning}
 
-	\subsection{Alignment}
+\section{Alignment}
 
@@
    \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope.
-AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system.
-(B) The alignment mirror can be rotated to precisely reflect at $45\degree$.
+AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises.
+(B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.
 (C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm.
-(D) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.}
+(D) The alignment mirror can be rotated to precisely reflect by $90\degree$.}
    \end{figure}
@@
 For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
-The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's depth of field.
-Telecentricity, that is the imaging with two lenses which are the sum of their focal lengths apart, has to be strictly observed in all three arms (Figure\ref{fig:alignment},A), which means the galvo scanners need to be precisely placed in telecentric planes of the excitation objectives while in the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
-Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as pair with recursive dependence.
+The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane.
+Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Figure\ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives.
+In the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
+Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as a pair with recursive dependence.
 
 Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be.
-The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber.
+The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Figure\ref{fig:alignment},B).
 Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
-With this ``sample mirror" three different position can now be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole, and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage.
+With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Figure\ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Figure\ref{fig:alignment},D).
 
@@
    \end{center}
-   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam in converted into a spherical wavefront.
-Right: inverted light path where a focal spot in the back aperture creates a collimated output.
+   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront.
+Right: inverted light path, a focal spot in the back aperture creates a collimated output.
 (B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.}
@@
 The excitation objectives are fixed on mounts which allow three dimensional translation plus pitch and yaw adjustment (LP-1A, Newport).
-In a first step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives.
+In a first alignment step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives.
 We found it useful to use two mirrors in each periscope, one vertically mounted and one mounted at $45\degree$ for vertical deflection of the incoming beam.
 In this way full beam steering can be achieved to realign the periscope before hitting the galvo scanner.
-After this initial alignment the first excitation objective was then placed into the beam path and brought to focus onto the sample mirror, which was adjusted to reflect the light back into the same objective.
-Using a shear plate and a beam splitter cube the back reflected light was qualitatively checked for collimation to ensure the sample mirror was correctly placed in the focal plane of the objective (Figure\ref{fig:alignment2},B).
+After this initial alignment the sample mirror was placed with its reflective surface in the centre of the central cut-out of the breadboard.
+The first excitation objective was placed into the beam path and brought to focus onto the sample mirror which was adjusted to reflect the light back into the same objective through the irises.
+Using a shear plate and a beam splitter cube the back reflected light was qualitatively adjusted for collimation using translation along the excitation axis of the objective mount (Figure\ref{fig:alignment2},B).
 The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C).
 This time collimation was checked with the light going through both objectives and so their confocal placement was insured.
-The microscope was then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source.
-Finally, the sample mirror was position in reflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
-
-\section{Optical characterisation}
+Both excitation arms were then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source, alternating between the two modalities illustrated in Figure\ref{fig:alignment2},A.
+Finally, the sample mirror was positioned in deflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
 
@@
 																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
-																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised															 \\
-		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\
-		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V										 \\
-		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth							 \\
-		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																				 \\		
+																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
+		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
+		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V						\\\hline
+		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth			\\\hline
+		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																\\\hline		
 		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)													\\
-																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)																			 \\
-		\multirow{3}{*}[0.6em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																										 \\
+																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)															\\\hline
+		\multirow{3}{*}[1.2em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																						\\
 																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s		\\
-																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ 		\\
-		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\
-		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\
+																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
+		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
+		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
 		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
@@
 		effective area 															& $r^2$						&																																					& $13.3^2$	&	$\text{mm}^2$	\\
+		line read out time													& t								&																																					& 9.7			&	$\mu s$	\\
+		line exposure time													& l								&																																					& 3				&	ms			\\
+		slit width, camera space										& $d_c$						& $=\nicefrac{l}{t} $																											& 2				&	mm	\\
+		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 80			&	$\mu m$	\\
+		frame rate																	& $\nu$						&	$=\nicefrac{1}{2048 t + l}$																							& 43.6		& Hz\\
 		\end{tabular}
@@
 \acknowledgments
+workshop boys cause they are amazing.
 Human Brain Project tutta la vita. 
@@
 
+\bibitem{Keller2008a} P.
+J.
+Keller and E.
+H.
+K.
+Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light sheet fluorescence microscopy," \emph{urr.
+Opin.
+Neurobiol.} \textbf{18}(6), 624–632 (2008).
+
+\bibitem{Keller2008b} P.
+J.
+Keller, A.
+D.
+Schmidt, J.
+Wittbrodt, and E.
+H.
+K.
+Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
+
+\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light sheet microscopy with confocal slit detection," \emph{Optics express} \textbf{20}(19), 21805-21814 (2012).
+
 \bibitem{Silvestri2012} L.

### 2015-01-20 latex-style-files-spie-manuscript/manuscript1.0.tex
commit before merge with ludo

@@
 After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days.
-In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task whichhas too often been summarised in a single sentence.
-A systematic approach to handle, store and analyse the data is also given.
+In addition to a full description of the optical setup, the control hardware and software, we further present a practical guide for the alignment of a LSFM, a non-trivial task that requires careful consideration.
+A systematic approach to handle, store and analyse the data is explained in detail.
 We further explain about the data volume we produce how it can be reduced and handled.
-We finish with some nice data and an outlook.
+The imaging capabilities are demonstrated by 3D reconstructions of biological specimens.
 The final sentence of the introduction needs to be amazing.
@@
 
-\section{Sample mounting}
+\section{Sample mounting and motion}
 %Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
@@
 The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
+To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed.
 A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
+Illumination and detection axes are horizontal and the sampler rotation occurs around the vertical axis.
 
 	\section{Optical path}
-
-	\subsection{Illumination}
 
@@
 
+\subsection{Laser unit}		
 The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A).
@@
 
+\subsection{Illumination unit}		
 From here on three different light paths can be chosen through flip mirrors.
@@
 
-Fluorescence detection in light sheet microscopy is analogous to conventional wide-field microscopy.
+In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector.
 Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
@@
 To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
-A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a camera chip of over 4 megapixels.
+A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels.
 In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
@@
 With those values the camera acquires images at a frame rate of 44Hz.
-Synchronisation of the rolling shutter with the scanned illumination beam results in confocal line detection\cite{Baumgart2012}.
+
+The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave.
+The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012}.
+For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.
+Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast.
+The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.
 
@@
 	\subsection{Contrast}
+
 	\subsection{Signal-to-noise ratio}
+
 	\subsection{Optical sectioning}
@@
 		\begin{tabular}{llll}
-		Component												&	Manufacturer															& Part\# 								& Specifications 																											\\\hline
+		Component												&	Manufacturer															& Part\# 								& Specifications 																											\\\hline\hline
 		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\

### 2015-02-04 latex-style-files-spie-manuscript/manuscript_merged.tex
first commit after Leo - no light sheet comic - change of order: light path first, sample stuff dopo - combined panel for chamber and sample mounting - alignment at bottom in supplementary information

--- 2015-01-20 latex-style-files-spie-manuscript/manuscript1.0.tex
@@
 
-\title{Working title: the most amaz-zing SPIM and how we built it.}
+\title{Robust data management for high through-put light sheet microscopy of whole mouse brains}
 
 \author{M.
-Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel Van t'Hoff\supscr{f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
+Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel Van t'Hoff,\supscr{f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
 Pavone,\supscr{a,b,c,d}  }
@@
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
-This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap (Figure\ref{fig:Panel0},A).
+This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap.
 Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise.
@@
 
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{PanelSampel.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.
-Excitation (blue) and fluorescence detection (green) occur on independent, perpendicular axes.
+%\begin{figure}
+   %\begin{center}
+   %\begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{PanelSampel.eps}
+   %\end{tabular}
+   %\end{center}
+   %\caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.
+The sample is illuminated with a planar light sheet (blue) perpendicular to fluorescence detection (green).
 (B) Mounting of a clarified, fluorescently labelled brain.
 The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.}
-   \end{figure}
-
-\section{Sample mounting and motion}
-%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
-Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices.
-Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque.
-In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed.
-These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
-%
-%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
-A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
-Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap.
-Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies.
-With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.
-
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{NuPanel1.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:Panel1} Schematic of light sheet microscopy.
-(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
-The custom-made sample chamber is assembled with silicone bellows and seal rings.
-The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber (C) and can be translated and rotated freely with piezo motors (D).}
-   \end{figure}
-
-To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation.
-While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
-The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample.
-Most commonly the vertical direction is chosen.
-Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.
-
-To acquire whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B).
-The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip.
-The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw.
-The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective.
-Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.
-
-We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
-The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:Panel1},B).
-All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
-In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:Panel1},C).
-The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
-To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed.
-A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).
-Illumination and detection axes are horizontal and the sampler rotation occurs around the vertical axis.
+   %\end{figure}
 
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel2.eps}
+   \includegraphics[width=\textwidth]{frame1.eps}
    \end{tabular}
@@
 The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective.
-%This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
+This generates incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
+Additionally each line is specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.
 
-\subsection{Detection}
-		%objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
-		%exposure time of single line affects how many are exposed at same time, confocality by synchronisation- not exactly
+\subsection{Detection unit}
 
@@
 In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
+The cell size of the OrcaFlash is $p^2= 6.5\micro m$ x $6.5\micro m$ over an active area of 13.3mm.
+With a 200mm tube lens the field of view in the sample is $480\micro m$.
+
 In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor.
-With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms.
-Setting the line exposure time to 3ms results in approx.
-300 lines being simultaneously exposed.
-This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $80\micro m$ in the sample space.
-With those values the camera acquires images at a frame rate of 44Hz.
+With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t=9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms.
+Setting the line exposure time to $l=3ms$ results in approx.
+$k=\nicefrac{l}{t}\approx300$  lines being simultaneously exposed at any time.
+This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $d_s=\nicefrac{k p}{M_{\text{eff}}}= 0.72m$ in the sample space.
+With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(2048t+l)} \approx 44Hz$.
 
@@
 The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.
+
+\section{Sample mounting and motion}
+%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
+Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices.
+Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque.
+In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed.
+These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
+%
+%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
+A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
+Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap.
+Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies.
+With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{frame2.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:frame2} Schematic of light sheet microscopy.
+(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
+(B) The custom-made sample chamber is assembled with silicone bellows and seal rings.
+The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber (C) and can be translated and rotated freely with piezo motors (D).
+(E) Mounting of a clarified, fluorescently labelled brain.
+The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.}
+   \end{figure}
+
+To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation.
+While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
+The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample.
+Most commonly the vertical direction is chosen.
+Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.
+
+For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},D).
+The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip.
+The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw.
+The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective.
+Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.
+
+We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
+The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B).
+All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
+In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C).
+The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
+To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed.
+A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D).
+Illumination and detection axes are horizontal and the sampler rotation occurs around the vertical axis.
 
@@
 
-\section{Alignment}
+\section{Microscope management software}
 
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel3.eps}
+   \includegraphics[width=\textwidth]{connectivity.eps}
    \end{tabular}
    \end{center}
-   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope.
-AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises.
-(B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.
-(C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm.
-(D) The alignment mirror can be rotated to precisely reflect by $90\degree$.}
+   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively.
+The software architecture scheme clarifies the hierachic structure of the Murmex components.
+AO analog output, DO digital output, DI digital input.}
    \end{figure}
 
-For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
-The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane.
-Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Figure\ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives.
-In the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
-Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as a pair with recursive dependence.
+\subsection{General design principles}
 
-Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be.
-The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Figure\ref{fig:alignment},B).
-Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
-With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Figure\ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Figure\ref{fig:alignment},D).
+The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated together and operated through a custom-made software.
+Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing proper synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging.
+The overall architecture of the software and its practical implementation were chosen to satisfy several principles:
+
+\begin{itemize}
+\item{\emph{User-friendliness}.
+The light sheet microscope here presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by researchers with no expertise in optics and/or software development.}
+\item{\emph{Working in a distributed environment}.
+The apparatus should deal with many independent hardware components, and with several data streams (see below).
+Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
+\item{\emph{Robustness and ease of maintenance}.
+Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
+Furthermore, developers must be able to fix existing code or to develop new one without having to change the whole software.}
+\item{\emph{Reusability and scalability}.
+When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch is pure loss of time.
+Writing well structured, scalable and easily maintainable scientific software can help avoiding redundancy and boosting up productivity.}
+\end{itemize}
+
+Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
+An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
+This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
+Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
+The graphical user interface (GUI) provides intuitive control of the apparatus as well as deep personalization.
+In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
+Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
+
+\subsection{Murmex}
 
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel4.eps}
+   \includegraphics[width=\textwidth]{murmex.eps}
    \end{tabular}
    \end{center}
-   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront.
-Right: inverted light path, a focal spot in the back aperture creates a collimated output.
-(B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.}
+   \caption{\label{fig:murmex} This graph needs a caption.} 
    \end{figure}
 
-The excitation objectives are fixed on mounts which allow three dimensional translation plus pitch and yaw adjustment (LP-1A, Newport).
-In a first alignment step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives.
-We found it useful to use two mirrors in each periscope, one vertically mounted and one mounted at $45\degree$ for vertical deflection of the incoming beam.
-In this way full beam steering can be achieved to realign the periscope before hitting the galvo scanner.
-After this initial alignment the sample mirror was placed with its reflective surface in the centre of the central cut-out of the breadboard.
-The first excitation objective was placed into the beam path and brought to focus onto the sample mirror which was adjusted to reflect the light back into the same objective through the irises.
-Using a shear plate and a beam splitter cube the back reflected light was qualitatively adjusted for collimation using translation along the excitation axis of the objective mount (Figure\ref{fig:alignment2},B).
-The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C).
-This time collimation was checked with the light going through both objectives and so their confocal placement was insured.
-Both excitation arms were then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source, alternating between the two modalities illustrated in Figure\ref{fig:alignment2},A.
-Finally, the sample mirror was positioned in deflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
+To let the software operate efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used.
+This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardized programming scheme.
 
-%\section{Software Management}
-%
-	%\begin{figure}
-   %\begin{center}
-   %\begin{tabular}{c}
-   %\includegraphics[width=\textwidth]{connectivity.eps}
-   %\end{tabular}
-   %\end{center}
-   %\caption{\label{fig:connectivity} Connectivity scheme} 
-   %\end{figure}
-%
-%%Here we describe all things software control and communication, components and their interaction. how is the rolling shutter timed with galvos, triggers and clocks etc.
-%
-%
-%%Based on a modular scheme (OOP) using Murmex development kit
-%%Separate building blocks control different components of the microscope
-%%Hierarchical structure coordinates complex tasks
-%%Communication takes place through RabbitMQ server (open source message-oriented middleware) using the LabbitMQ library
-%
-%The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers.
-Our experimental research is based on the acquisition and real-time processing of various data streams.
-In a given experiment, data may be acquired from multiple, spatially separated sources, and individual processing steps can be computationally intensive and may need to be distributed over several computers to be performed at run-time.
-For those reasons we chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
-%
-%Another important aspect of software design is avoiding redundancy when scaling up the software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory.
-Writing well structured, scalable and easily maintainable scientific software in a group of researchers is an often recurring challenge.
-Object oriented programming is a programming paradigm whose main aspects are encapsulation, inheritance and polymorphism and a useful tool to address these challenges.
-%
-%Encapsulation refers to the concept that the entirety of software needed to say operate a microscope is broken up into self-contained modules.
-Those modules are user-defined data types and referred to as ``classes" where one instance of a class is called an ``object".
-For example a class could be the basic code to operate an  abstract laser while 5 instances of this class would be the necessary adjustments to operate 5 real world lasers from different manufacturers.
-This modular programming style keeps large amounts of software routines separate and less prone to conflict with each other.
-%
-%Classes are arranged in hierarchical structures and inheritance, the act of passing on knowledge from a ``parent" to a ``child" within a class, reduces the amount of programming required when increasingly more complex functions have to be added to the system.
-For example when specialised behaviour is added to the bottom of the hierarchy, only code regarding this very specific task has to be added while every other aspect is inherited from above.
-For example, if the code for a motor stage has already been implemented, a rotation stage can be interpreted as the child of a translation stage where the travel range is infinite.
-This increases code re-usability and saves time.
-%
-%In this way, the microscope software is decomposed into the communication and interaction of different objects through methods, bits of code, which act on each object's private data.
-%
-%The Murmex software development kit is based on the OOP paradigm and helps users to collaborate on software development by letting them independently create their respective contributions to the software in the form of new objects or methods within a standardized programming scheme.
-%
-%\subsection{RabbitMQ}
-%Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middle ware facilitating message shipment and receival.
+Basically, Murmex creates distributed finite state machines.
+These are design patterns in which one component proceed from one particular state to another based on the message it receives either from itself or from other components.
+For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middleware facilitating message shipment and receival.
 These layers of abstraction are mostly hidden for the developers.
-%The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
+The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
 The message-based communication allows for buffered, asynchronous and reliable message communication between several software components.
 Messages are routed by the broker to the specific software component by its ID.
-In order to access the functionality of RabbitMQ, the application programming interface (API) \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ} was used, which uses .NET calls for sending and receiving messages to and from the RabbitMQ broker.
-Messages can be sent to a single recipient by its ID or sent to all available components.
-%
-%\subsection{Murmex}
-%The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer).
-A finite state machine resembles the Strategy pattern [Design Patterns: Elements of Reusable Object-Oriented Software, E.
-Gamma, R.
-Helm, R.
-Johnson, J.
-Vlissides, 1994], which lets the software of one component proceed from one particular state to another based on message it receives from itself or other components (for example to execute Initialise, Start, Proceed, Stop, Terminate).
-In each state it executes the code for that state only, but flexible execution patterns are possible.
-It thus allows for predictable behaviour, without knowing the exact code.
-Murmex has twelve pre-defined common states (e.g.
-Initialise, Start, Stop, Terminate) and a generic state for implementing custom states.
-A software component that represents one, yet large, task, often uses only those previously four mentioned states.
-Examples for such a software component are the implementation of a laser, a translation stage and a camera.
-Such a component would implement in the Initialise method the initialisation of the communication port to the device, start activity in the Start method, stop activity in the Stop method and close the communication and free up memory in the Terminate.
-%While each component is an autonomous program, variables on which each component might depend, have to be shared among the components.
-The Update method is used for this purpose, which allows components to update itself with new parameters and automatically forward these parameters to down- or upstream components by using a mapping script $(e.g.
-datastorage.total_movie_size=xres*yres*number_of_frames, where datastorage is the ID of the recipient, total_movie_size is the name of the parameter to be updated and xres, yres and number_of_frames are the names of parameters of the sender)$.
-%Typically, a Murmex component streams data only to components listed as observers in its configuration file.
-Using this concept, components can be configured to form arbitrarily complex signal processing pipelines or networks.
-Once a component has been considered to be stable by the developer, an executable can be built.
-An important component named ServiceManager (also based on Murmex) can communicate to other ServiceManagers over the network or internet and can start remotely executables.
-This allows the user to start up a sophisticated configuration with multiple components as executable on different computers, but steered from one computer.
-%
-%
-%
-%
-%\section{Data Management}
-	%\subsection{Pipeline}
-	%
-	%\begin{figure}
-   %\begin{center}
-   %\begin{tabular}{c}
-   %\includegraphics[width=\textwidth]{DataFlow.eps}
-   %\end{tabular}
-   %\end{center}
-   %\caption{\label{fig:DataFlow} Scheme of the data flow.
+The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
+
+Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states.
+Usually, just a few of this states are actually used in standard application.
+An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig.
+BLABLA.
+Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file.
+Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet.
+A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely.
+This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.
+
+\subsection{System timing and software organization}
+
+A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig.
+BLABLA, respectively.
+One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section).
+Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).
+
+Synchronization of the camera rolling shutter to the scanning of the light sheet is achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
+In particular, the HSYNC signal from the camera is used, providing a true-type-logic (TTL) pulse everytime the rolling shutter steps from one line to the next one.
+This trigger signal is used as a clock by the DAQ board, so that the line producing the light sheet moves step by step with the rolling shutter.
+The same HSYNC signal is used to trigger the DAQ digital signal sent to the electro-optic laser modulator.
+In this case, since at each position of the scanning line the modulator should go trough at least two states (vertical polarization and horizontal polarization), HSYNC is used as a trigger while the clock used is the (much faster) internal clock of the DAQ board.
+
+Each hardware component (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component.
+Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just send analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Beyond hardware-related software, two additional Murmex components (named Stack and Tomo) orchestrate the operation of the entire system.
+
+The stack component is used to acquire single image stacks along the $z$ direction, and to this aim send specific messages to coordinate the Camera and the Stages components.
+Stacks are collected by moving continuously the sample along $z$ while keeping the camera acquiring in free run.
+The translation speed is such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
+The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack.
+The name of this file and the path to it is specified by the Stack component.
+
+The tomo component is used to image the entire sample by collecting many adjacent, parallel, partially-overlapping stacks.
+To this aim it exchanges messages with the Stack and the Stages components.
+The user can specify the volume to be imaged either by inserting the maximum $x$, $y$ and $z$ coordinates of a parallelepiped, or by providing a text file with the list of stacks to be collected ($x$ and $y$ coordinates, starting and ending $z$s).
+The Tomo component also inform the experimenter about the state of the acquisition by sending an email when it's finished or if any trouble is experienced.
+
+All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
+Beacuse of its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
+
+\section{Data Management}
+
+The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
+Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$.
+This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels.
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table XXXX).
+However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching.
+This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.
+
+This unprecedented amount of data challenges to the traditional way we interact with our data.
+Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
+
+\subsection{Data handling and storage}
+
+The camera used in our light sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the datastream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
+Although this is already a large and expensive system for the current SSD technology, it is way smaller than the size of the raw datasets produced in each tomography.
+We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable.
+The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space.
+The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main italian supercomputing center).
+The data flow scheme is summarized in Figure \ref{fig:DataFlow}.
+
+While transferring the data from the SSD to the NAS, we also perform a file conversion from the proprietary Hamamatsu format to a more manageable one.
+We chose the TIFF format among the others because it permits to store 3D image with lossless compression in a single file.
+Furthermore, it is a flexible and platform-independent format supported by numerous image processing applications.
+We thus developed a conversion module that leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library.
+The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
+Since the output of the Hamamatsu camera may exceed tens of Gbytes, the image in proprietary format is read slice by slice to minimize memory requirements.
+The module has also an option to downsample the image on save the input image at full or reduced resolution, in order to adapt to storage availability.
+Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling as usual.
+This kind of downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude.
+Thus the parallelepid volume cointaining the whole mouse brain can be represented using about 2-3 TB of disk space.
+
+Although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
+The Camera component flushes data on the SSD with a rate $R_{data}$ dependent on frame rate $R_{frame}$ and on the image size:
+\begin{equation}
+R_{data} [\text{Bytes}] = 2\times R_{frame} \times \#_{pixels}\,,
+\end{equation}
+where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{volume} = 0.5 R_{data} \times \text{Voxel size}$.
+
+With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
+The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h.
+Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB.
+This is well above the disk space needed to image the parallelepieped volume encompassing a whole mouse brain.
+Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
+
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{DataFlow.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:DataFlow} Scheme of the data flow.
 (A) Data streaming on the microscope.
-The data is written through the CameraLink connection onto the SSD.
-From there the data can be transferred via a 10Gb connection to the NAS or to the supercomputing centre CINECA in Bologna.
 SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
 (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
-   %\end{figure}
-	%
-%%\begin{landscape}
-%\begin{table}%[t!]
-	%\centering
-		%\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
-		%\begin{tabular}{lrl}
-		%frame rate																	& 44			& Hz	\\
-		%size of 1 frame															& 8				& MB	\\
-		%frames per stack														& 3900		& 		\\
-		%size of original stack											& 30.4		& GB	\\
-		%size of converted stack											& 3				& GB	\\
-		%stack acquisition time											& 88.6		& s		\\
-		%stack conversion time												& 140			& s		\\
-		%time ratio conversion/ acquisition					& 1.6			& 		\\
-		%data production rate												& +1.2		&	TB/h\\
-		%data conversion rate												& -0.7		&	TB/h\\
-		%net rate																		& +0.5		&	TB/h\\
-		%SSD RAID																		& 10.9		& TB	\\
-		%max acquisition time to fill up SSDs				& 21			& h		\\
-		%max tomo size to fill up SSDs								& 25.4		& TB	\\
-		%\end{tabular}
-%\end{table}
-%%\end{landscape}
-%The unprecedented amount of data routinely produced by light sheet microscopy presents challenges to the traditional way we interact with our data.
-Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires a professional approach to centralised network architecture.
-The following paragraphs give an idea of the considerations one has to give to the big data volume problem.
-The camera used in our light sheet microscope has a dedicated work station with a CameraLink card and 10.9TB of SSD space in RAID 0 configuration.
-This finite storage capacity is further expanded by a network-attached storage (NAS) of 32.4TB (Figure\ref{fig:DataFlow}).
-The SSDs and the NAS are connected via a 10Gb bandwidth connection using a 10Gb switch and a 10Gb optical fibre connects our lab to the supercomputing centre CINECA in Bologna.
-Mention PICO system/storage analysis capacity there?
-Mention graphical processing unit and cores/processors/RAM of work station?
-	%
-%With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
-Based on a frame rate of 44Hz each stack takes approximately 1.5 minutes to acquire and the SSD RAID fills up with a data writing rate of 1.2TB/h.
-If no further measures are taken the SSD RAID of 10.9TB would be filled up in just 9h.
-A custom compression script written in Python serves the triple purpose of translating the images from the proprietary Hamamatsu file format to 3D tif, to transfer the data from the SSD RAID to a network attached storage (NAS) and to reduce the raw data size by first, digitally downsampling the image resolution and second, applying a lossless compression to the tif images.
-This leads to a overall reduction of data size by a factor of ten, each stack now taking up only 3GB of disc space, albeit at a much slower conversion rate (-0.7TB/h) than the rate at which data is written to the SSD thus representing the most serious bottleneck to our data production pipeline.
-The SSD RAID fills up at a rate of 0.5TB/h which means the total acquisition time is limited to less than 24h and a total tomo size of just over 25TB.
-After this time acquisition has to be halted until the slower conversion process has caught up and freed the SSD RAID before data acquisition can start again.
-A whole mouse brain tomography would take 3 days of uninterrupted measuring yet with the necessary breaks for data transfer this time is easily doubled to tripled.
-%
-	%\subsection{Stitching and visualisation}
-	%
-%Given the limited field of view of the microscope, the acquisition of macroscopic specimens required many parallel image stacks to cover all the volume.
+   \end{figure}
+
+\begin{table}%[t!]
+	\centering
+		\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
+		\begin{tabular}{lrl}
+		frame rate																	& 44			& Hz	\\
+		size of 1 frame															& 8				& MB	\\
+		frames per stack														& 3900		& 		\\
+		size of original stack											& 30.4		& GB	\\
+		size of converted stack											& 3				& GB	\\
+		stack acquisition time											& 88.6		& s		\\
+		stack conversion time												& 140			& s		\\
+		time ratio conversion/ acquisition					& 1.6			& 		\\
+		data production rate												& +1.2		&	TB/h\\
+		data conversion rate												& -0.7		&	TB/h\\
+		net rate																		& +0.5		&	TB/h\\
+		SSD RAID																		& 10.9		& TB	\\
+		max acquisition time to fill up SSDs				& 21			& h		\\
+		max tomo size to fill up SSDs								& 25.4		& TB	\\
+		\end{tabular}
+\end{table}
+
+\subsection{Stitching and visualisation}
+
+Given the limited field of view of the microscope, the acquisition of macroscopic specimens required many parallel image stacks to cover all the volume.
 Thus, in order to achieve a 3D image of the whole specimen from raw data, the Terastitcher\cite{Bria2012} has been recently proposed, i.e.
@@
 For these reasons, we extended the Terastitcher functionalities introducing the two following additional features: i) stitching of a specimen partitioned in a number of overlapping layers for the hippocampus reconstruction and, ii) coping with images containing more than one channel for the human brain tomography.
-%With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depicts in Fig.1 the adopted strategy.
+With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depicts in Fig.1 the adopted strategy.
 First of all, the various input layers, each of which is composed of several parallel overlapping stacks, are separately stitched by using the existing Terastitcher tool.
@@
 Finally, we note that due to the repositioning of each layer, the volume containing the reconstructed specimen might contain empty regions, which are thereby filled with black voxels.
-%Turning our attention to the second additional feature, that is handling multi-channel images, the Terastitcher has been extended so that the MIP-NCC algorithm used for displacement computation can work on an image, which can be either
-%the fusion of the input channels or one of the input channels.
+Turning our attention to the second additional feature, that is handling multi-channel images, the Terastitcher has been extended so that the MIP-NCC algorithm used for displacement computation can work on an image, which can be either
+the fusion of the input channels or one of the input channels.
 This permits to privilege the channel with more information content over the other channels as well as discard noisy channels.
 Note that the reconstructed 3D image can be produced with the same channel composition of raw data.
-%
-%
-	%\subsection{Example for postprocessing: Automated cell counting}
-	%See Reference\cite{Frasconi2014} for details.
-%
-%
+
 \section{Data}
@@
 		numerical aperture 													&	$\text{NA}_d$		&																																					& 1				& 				\\
-		angular aperture 														& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
-		magnification 															& M								&																																					& 25			&					\\
-		tube lens 																	& $f_{\text{TL}}$	&																																					& 180			&	$mm$		\\
+		%angular aperture 													& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
+		magnification 															& $M_{\text{eff}}$&	$= \nicefrac{f_{\text{TL}}}{\text{EFL}}$																& 27.8		&					\\
+		tube lens 																	& $f_{\text{TL}}$	&																																					& 200			&	$mm$		\\
 		effective focal length objective						& EFL							& $=\nicefrac{f_{\text{TL}}}{M}$																					& 7.2			& $mm$		\\
-		diameter back focal plane										& BFP							& $= 2\text{EFL}\text{NA}_d$																							& 14.4		& $mm$		\\
+		diameter back focal plane										& BFP							& $= 2\cdot \text{EFL} \cdot \text{NA}_d$																	& 14.4		& $mm$		\\
 		field number																& FN							&																																					& 18			& $mm$		\\
-		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.72		& $mm$		\\
-		depth of field															& $\Delta$				& $=\nicefrac{\lambda*n}{(\text{NA}_d)^2}+ \nicefrac{n*e}{M \text{NA}_d}$	& 1.10 		& $\mu m$	\\ 
+		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.65		& $mm$		\\
+		depth of field															& $\Delta$				& $=\nicefrac{\lambda \cdot n}{(\text{NA}_d)^2}+ \nicefrac{n \cdot e}{M \cdot \text{NA}_d}$	& 1.06 		& $\mu m$	\\ 
 		Airy radius lat.														& $r_A$						& $=\nicefrac{0.61 \lambda}{\text{NA}_d}$																	& 0.31		& $\mu m$	\\\\
@@
 		line exposure time													& l								&																																					& 3				&	ms			\\
-		slit width, camera space										& $d_c$						& $=\nicefrac{l}{t} $																											& 2				&	mm	\\
-		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 80			&	$\mu m$	\\
-		frame rate																	& $\nu$						&	$=\nicefrac{1}{2048 t + l}$																							& 43.6		& Hz\\
+		slit width, camera space										& $d_c$						& $=\nicefrac{l \cdot e}{t} $																							& 2				&	mm	\\
+		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 0.72		&	mm	\\
+		frame rate																	& $\nu$						&	$=\nicefrac{1}{(2048 \cdot t + l})$																			& 43.6		& Hz\\
 		\end{tabular}
@@
 \end{landscape}
-
-		%\begin{landscape}
-%\begin{table}[t!]
-	%\centering
-		%\caption[Optical clearing]{Overview of tools and chemicals necessary for optical clearing.\label{tab:clearing}}
-		%\begin{tabular}{lllll}
-		%Component												&	Manufacturer															& Part 						& Specs 					& Specs\\\hline
-		%degasing chamber								& 																					&  	& 								& \\
-		%clearing chamber								& 3D printed custom design									&  	& 								& \\
-		%voltage supply									& 																					&  	& 								& \\
-		%soap circulation thingy					& 																					&  	& 								& \\
-		%shakey incubator								& 																					&  	& 								& \\
-		%all those chemicals							& 																					&  	& 								& \\
-		%\end{tabular}
-%\end{table}
-%\end{landscape}
-
-%%------------- 
-   %\begin{figure}
-   %\begin{center}
-   %\begin{tabular}{c}
-   %\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
-     %\\
-     %(a) \hspace{5.1cm} (b)
-   %\end{tabular}
-   %\end{center}
-   %\caption 
-   %{ \label{fig:example2} %>> use \label inside caption to get Fig. number with \ref{}
-%Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
-   %\end{figure}
 
@@
 
+\bibitem{castagna1997object} G. Castagna, \emph{``Object-Oriented Programming A Unified Foundation,"} Birkh{\"a}user, Boston (1997).
+
+\bibitem{Costantini} I.
+Costantini, J.-P.
+Ghobril, A.
+P.
+Di Giovanna, A.
+L.
+Allegra Mascaro, L.
+Silvestri, M.
+C.
+Muellenbroich, L.
+Onofri, V.
+Conti, F.
+Vanzi, L.
+Sacconi, R.
+Guerrini, H.
+Markram, G.
+Iannello, and F.
+S.
+Pavone, \emph{submitted}.
+
+\bibitem{Kovacevic2005} N.
+Kovacevic, J.
+T.
+Henderson, E.
+Chan, N.
+Lifshitz, J.
+Bishop, A.
+C.
+Evans, R.
+M.
+Henkelman, and X.
+J.
+Chen, "A Three-dimensional MRI Atlas of the Mouse Brain with Estimates of the Average and Variability", \emph{Cereb.
+Cortex} \textbf{15}(5), 639-45 (2005).
+
+\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
+
 \end{thebibliography}
@@
 
+\section{Supplementary information}
+
+\subsection{Alignment}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{Panel3.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope.
+AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises.
+(B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.
+(C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm.
+(D) The alignment mirror can be rotated to precisely reflect by $90\degree$.}
+   \end{figure}
+
+For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
+The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane.
+Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Figure\ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives.
+In the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
+Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as a pair with recursive dependence.
+
+Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be.
+The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Figure\ref{fig:alignment},B).
+Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
+With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Figure\ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Figure\ref{fig:alignment},D).
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{Panel4.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront.
+Right: inverted light path, a focal spot in the back aperture creates a collimated output.
+(B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.}
+   \end{figure}
+
+The excitation objectives are fixed on mounts which allow three dimensional translation plus pitch and yaw adjustment (LP-1A, Newport).
+In a first alignment step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives.
+We found it useful to use two mirrors in each periscope, one vertically mounted and one mounted at $45\degree$ for vertical deflection of the incoming beam.
+In this way full beam steering can be achieved to realign the periscope before hitting the galvo scanner.
+After this initial alignment the sample mirror was placed with its reflective surface in the centre of the central cut-out of the breadboard.
+The first excitation objective was placed into the beam path and brought to focus onto the sample mirror which was adjusted to reflect the light back into the same objective through the irises.
+Using a shear plate and a beam splitter cube the back reflected light was qualitatively adjusted for collimation using translation along the excitation axis of the objective mount (Figure\ref{fig:alignment2},B).
+The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C).
+This time collimation was checked with the light going through both objectives and so their confocal placement was insured.
+Both excitation arms were then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source, alternating between the two modalities illustrated in Figure\ref{fig:alignment2},A.
+Finally, the sample mirror was positioned in deflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
+
 %\end{spacing}

### 2015-02-05 latex-style-files-spie-manuscript/manuscript_merged.tex
new origin graph of microscope characterisation marcels name is corrected

@@
 \author{M.
-Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel Van t'Hoff,\supscr{f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
+Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b,f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
 Pavone,\supscr{a,b,c,d}  }
@@
 \supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
-\supscrsm{f}Distrio, Murmex}
+\supscrsm{f}Distrio, Amsterdam, The Netherlands}
 
@@
 
-	\subsection{Contrast}
-
-	\subsection{Signal-to-noise ratio}
-
-	\subsection{Optical sectioning}
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{origin.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:origin} Optical characterisation.
+(A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian.
+(B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged.
+(C) The signal to noise ratio.}
+   \end{figure}
 

### 2015-02-11 latex-style-files-spie-manuscript/manuscript_Leo.tex
- merged with Ludo, new file name now Leo (something) - cosmetic changes to Ludo's parts - added Ludo's amazing new graph - think formulas in new tables were wrong (swapped exp time and shutter pace) - changed chip dimension to r because l is used for lines in confocal slit - changed number vertical pixels to number horizontal lines in table to match text - added abstract - adapted end of intro to new abstract - I like the new title - updated new line exposure time and consequently derived values - general spell and consistency checks - optical characterisation in next update - conclusion stil

--- 2015-02-05 latex-style-files-spie-manuscript/manuscript_merged.tex
@@
 
-\title{Robust data management for high through-put light sheet microscopy of whole mouse brains}
+\title{Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains}
 
@@
 \begin{abstract}
-200 words limit. no numerical references presenting concisely the objectives, methodology used, results obtained, and their significance.
+The comprehensive mapping and quantification of neuronal connections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution.
+We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact, clarified, whole-mount mouse brains.
+Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software.
+The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.
+It can easily be adapted and integrated to other microscope systems and has been made freely available to the light sheet community.
+The unprecedented amount of data routinely generated by light sheet microscopy further requires novel strategies for data handling and storage.
+To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets.
+The meso-scale neuroanatomy imaged at micron-scale resolution allows characterization and quantification of neuronal connections in unsectioned mouse brains.
 \end{abstract}
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light sheet microscopy, big data, whole brain mounting, data management, whole brain imaging, rolling shutter, 7,8.}
+\keywords{Light sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging.}
 
@@
 Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise.
-Consequently LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths; however, it requires the sample to be transparent.
+Hence LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths.
 
-Several challenges remain to be overcome, however, to allow fast and, most of all systematic, production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
-Those challenges include fast, cheap and reproducible sample preparation, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces.
+Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
+Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces.
 The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
@@
 The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples.
-After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days.
-In addition to a full description of the optical setup, the control hardware and software, we further present a practical guide for the alignment of a LSFM, a non-trivial task that requires careful consideration.
-A systematic approach to handle, store and analyse the data is explained in detail.
-We further explain about the data volume we produce how it can be reduced and handled.
-The imaging capabilities are demonstrated by 3D reconstructions of biological specimens.
-The final sentence of the introduction needs to be amazing.
+After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days.
+In addition, a full description of the the control hardware and software is presented.
+The microscope software coordinates each and every microscope component and ensures critical timing and synchronisation between those components.
+The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light sheet community.
+We further give a systematic and robust approach to handle, store and analyse light sheet microscopy data of tens of terabytes.
+To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.
 
@@
 The galvo scanners are mounted above periscopes.
-LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter, ABCD: flip mirrors.
-Inset: detection.
+LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter.
+Inset: detection path.
 (B) Oblique view of the microscope.
-A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut out for the translation stages.
+A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages.
 A second breadboard is used for the camera.}
@@
 The zero order light is blocked by an iris.
-An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
-The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system.
+An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
+The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
 First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
-A digital line is used to electronically control the frequency with which the polarisation is changed.
+A digital line is used to switch to zero the output of the pre-amplifier, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
 After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).
@@
 \subsection{Illumination unit}		
-From here on three different light paths can be chosen through flip mirrors.
-One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam.
-The other two options create Gaussian beams of different beam diameter.
-This diameter variation translates to different fields of view later on in the detection path.
-The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms.
-The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo).
-The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.
+The light impinges onto a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms.
+The beam diameter is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo).
+Both galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.
 
-The scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
+Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
+The galvos are on planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
 The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber.
 A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent.
+A guide to align objectives to a common focus can be found in the supplementary information.
 The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective.
-This generates incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
-Additionally each line is specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.
+This generates incoherent illumination resulting in fewer artefacts.
+%cite{StelzerNatMeth2014}.
+Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.
 
@@
 
-In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector.
+In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector.
 Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
-The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP).
+The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm).
 To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
@@
 In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
-The cell size of the OrcaFlash is $p^2= 6.5\micro m$ x $6.5\micro m$ over an active area of 13.3mm.
-With a 200mm tube lens the field of view in the sample is $480\micro m$.
+The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$.
+With a 200mm tube lens the field of view in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).
 
-In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor.
-With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t=9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms.
-Setting the line exposure time to $l=3ms$ results in approx.
-$k=\nicefrac{l}{t}\approx300$  lines being simultaneously exposed at any time.
-This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $d_s=\nicefrac{k p}{M_{\text{eff}}}= 0.72m$ in the sample space.
-With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(2048t+l)} \approx 44Hz$.
+In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor.
+With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms.
+Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in approx.
+$l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
+This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of
+
+\begin{equation}
+s_{\text{object}}=\frac{l p}{M_{\text{eff}}}= 7.2 \micro m 
+\end{equation}
+
+in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective.
+With the given values of line exposure and line read out time, the camera acquires images at a frame rate of
+
+\begin{equation}
+\nu = \frac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz. 
+\end{equation}
 
 The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave.
-The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012}.
-For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.
+The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also paragraph \ref{sec:timing} on synchronisation).
 Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast.
-The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.
+The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.
 
@@
    \end{center}
-   \caption{\label{fig:frame2} Schematic of light sheet microscopy.
+   \caption{\label{fig:frame2} Schematic of sample mounting and motion.
 (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
 (B) The custom-made sample chamber is assembled with silicone bellows and seal rings.
-The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber (C) and can be translated and rotated freely with piezo motors (D).
+The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D).
 (E) Mounting of a clarified, fluorescently labelled brain.
@@
    \end{figure}
+
+We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
+The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B).
+All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
+In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C).
+The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
+To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed.
+A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D).
+Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.
 
@@
 
-For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},D).
+For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},E).
 The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip.
@@
 
-We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
-The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B).
-All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
-In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C).
-The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
-To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed.
-A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D).
-Illumination and detection axes are horizontal and the sampler rotation occurs around the vertical axis.
+\section{Optical characterisation}
 
-\section{Optical characterisation}
-An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.
+The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space.
+In particular, the radial (i.e.
+perpendicular to the detection axis) and axial (i.e.
+parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction.
+In a light sheet microscope, axial and radial resolutions are determined by the numerical aperture (NA) of the illumination and detection optics, respectively.
+The radial PSF is a standard Airy function, whose FWHM is given by:
+
+\begin{equation}
+\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
+\end{equation}
+
+$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
+
+The axial resolution is given by the thickness of the light sheet.
+If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
+The $1/e^2$ radius of the beam waist is given by:
+\begin{equation}
+w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
+\end{equation}
+where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index).
+Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
+The axial FWHM is then given by:
+\begin{equation}
+\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
+\end{equation}
+
+The thickness of the light sheet is not constant throughout the field of view due to the limited depth of focus of the Gaussian beam.
+This latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius is not bigger than $\sqrt{2} w_0$:
+\begin{equation}
+b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
+\end{equation}
+
+The need to have an almost uniform resolution in the camera field of view (FOV) imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq ???$, resulting in $b \simeq ???$ and $\text{FWHM}_{\text{axial}} \simeq?????$.
+
+An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}.
+The reader is referred to this table as a quick guide to tailor the apparatus to their specific needs.
+
+AND HERE THE AMMAZING OURS DATAS
 
@@
 
+For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.
+
 \section{Microscope management software}
-
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{connectivity.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively.
-The software architecture scheme clarifies the hierachic structure of the Murmex components.
-AO analog output, DO digital output, DI digital input.}
-   \end{figure}
 
@@
 
-The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated together and operated through a custom-made software.
-Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing proper synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging.
+The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software.
+Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging.
 The overall architecture of the software and its practical implementation were chosen to satisfy several principles:
@@
 \item{\emph{User-friendliness}.
-The light sheet microscope here presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by researchers with no expertise in optics and/or software development.}
+The light sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
 \item{\emph{Working in a distributed environment}.
@@
 Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
-Furthermore, developers must be able to fix existing code or to develop new one without having to change the whole software.}
+Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
 \item{\emph{Reusability and scalability}.
-When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch is pure loss of time.
-Writing well structured, scalable and easily maintainable scientific software can help avoiding redundancy and boosting up productivity.}
+When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time.
+Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
 \end{itemize}
@@
 Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
-The graphical user interface (GUI) provides intuitive control of the apparatus as well as deep personalization.
-In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
+The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation.
+In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
 Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
@@
    \end{center}
-   \caption{\label{fig:murmex} This graph needs a caption.} 
+   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
    \end{figure}
@@
 Basically, Murmex creates distributed finite state machines.
-These are design patterns in which one component proceed from one particular state to another based on the message it receives either from itself or from other components.
+These are design patterns in which one component proceeds from one particular state to another based on the message it receives either from itself or from other components.
 For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middleware facilitating message shipment and receival.
@@
 Usually, just a few of this states are actually used in standard application.
-An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig.
-BLABLA.
-Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file.
-Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet.
-A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely.
-This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.
+An example of a standard implementation of the Murmex state machine for the camera is shown in Fig.
+\ref{fig:murmex}.
+Each Murmex component streams information about its current status to its 'observers' which are other components specified in its configuration file.
+Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on any number of computers connected through a local connection or the Internet.
+A special component, named ServiceManager (also based on Murmex), which must be running on each computer, allows to start executables remotely in user-defined compositions of components.
+This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but operated from one computer.
 
 \subsection{System timing and software organization}
+\label{sec:timing}
 
-A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig.
-BLABLA, respectively.
-One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section).
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{connectivity.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:connectivity} Schematic view of the hardware architecture of the microscope. Different kind of physical connections are depicted with different colours.} 
+   \end{figure}
+
+A schematic overview of the hardware architecture of our light sheet microscope is shown in Fig.
+\ref{fig:connectivity}.
+One personal computer (Precision T5600, Dell, Round Rock, USA, see also Table \ref{tab:optomechanics}) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section).
 Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).
@@
 Synchronization of the camera rolling shutter to the scanning of the light sheet is achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
-In particular, the HSYNC signal from the camera is used, providing a true-type-logic (TTL) pulse everytime the rolling shutter steps from one line to the next one.
+In particular, the HSYNC signal from the camera is used, providing a true-type-logic (TTL) pulse every time the rolling shutter steps from one line to the next one.
 This trigger signal is used as a clock by the DAQ board, so that the line producing the light sheet moves step by step with the rolling shutter.
@@
 Each hardware component (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component.
-Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just send analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
 Beyond hardware-related software, two additional Murmex components (named Stack and Tomo) orchestrate the operation of the entire system.
 
-The stack component is used to acquire single image stacks along the $z$ direction, and to this aim send specific messages to coordinate the Camera and the Stages components.
+The Stack component is used to acquire single image stacks along the detection axis, here the $z$ direction, and to this aim sends specific messages to coordinate the Camera and the Stages components.
 Stacks are collected by moving continuously the sample along $z$ while keeping the camera acquiring in free run.
-The translation speed is such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
+The translation speed is calculated such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
 The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack.
-The name of this file and the path to it is specified by the Stack component.
+Note that the Camera component must write data to disk in perfect time, otherwise the nominal $z$ position is of each frame is no more coincident with the real $z$ position of the plane imaged.
+For this reason, we set the process executing the Camera code to be of highest priority.
+The Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
+The Stack component also specify the name and the path of the \emph{.cxd} file.
 
-The tomo component is used to image the entire sample by collecting many adjacent, parallel, partially-overlapping stacks.
+The Tomo component is used to image the entire sample by collecting many adjacent, parallel, partially-overlapping stacks.
 To this aim it exchanges messages with the Stack and the Stages components.
-The user can specify the volume to be imaged either by inserting the maximum $x$, $y$ and $z$ coordinates of a parallelepiped, or by providing a text file with the list of stacks to be collected ($x$ and $y$ coordinates, starting and ending $z$s).
-The Tomo component also inform the experimenter about the state of the acquisition by sending an email when it's finished or if any trouble is experienced.
+The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped, or by providing a text file with the list of stacks to be collected ($x$ and $y$ coordinates, starting and ending $z$s).
+The Tomo component also informs the experimenter about the state of the acquisition by sending an email when acquisition is finished or if any trouble is experienced.
 
 All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
-Beacuse of its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
+Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
 
@@
 
-The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
-Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$.
+The volume of a mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
+Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size amounts to $0.234\times0.234\times2$ $\micro\text{m}^3$.
 This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels.
-Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table XXXX).
-However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching.
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table \ref{tab:dataproduction}).
+However, image stacks are acquired with a 10\% of linear superposition, which is later used for image stitching.
 This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.
 
-This unprecedented amount of data challenges to the traditional way we interact with our data.
+This unprecedented amount of data challenges the traditional way we interact with our data.
 Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
@@
 
-The camera used in our light sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the datastream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
-Although this is already a large and expensive system for the current SSD technology, it is way smaller than the size of the raw datasets produced in each tomography.
+The camera used in our light sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
+Although this is already a large and expensive system for the current SSD technology, it is much smaller than the size of the raw datasets produced in each tomography.
 We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable.
 The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space.
-The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main italian supercomputing center).
+The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre).
 The data flow scheme is summarized in Figure \ref{fig:DataFlow}.
@@
 The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
-Since the output of the Hamamatsu camera may exceed tens of Gbytes, the image in proprietary format is read slice by slice to minimize memory requirements.
-The module has also an option to downsample the image on save the input image at full or reduced resolution, in order to adapt to storage availability.
-Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling as usual.
+Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format is read slice by slice to minimize memory requirements.
+The module has also an option to downsample the image or save the input image at full or reduced resolution, in order to adapt to storage availability.
+Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling unaltered.
 This kind of downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude.
-Thus the parallelepid volume cointaining the whole mouse brain can be represented using about 2-3 TB of disk space.
+Thus the parallelepiped volume containing the whole mouse brain can be represented using about 2-3 TB of disk space.
 
-Although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
-The Camera component flushes data on the SSD with a rate $R_{data}$ dependent on frame rate $R_{frame}$ and on the image size:
+The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition.
+Thus, although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
+The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size:
 \begin{equation}
-R_{data} [\text{Bytes}] = 2\times R_{frame} \times \#_{pixels}\,,
+R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}\,,
 \end{equation}
-where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{volume} = 0.5 R_{data} \times \text{Voxel size}$.
+where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.
 
-With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
-The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h.
+With a standard image size of $2048\times 2048$ pixels, and $R_{\text{frame}}=44$ Hz, data are produced at a rate $R_{\text{data}}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2\times 10^7$ $\micro\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
+The conversion module can empty the SSD with an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h.
 Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB.
-This is well above the disk space needed to image the parallelepieped volume encompassing a whole mouse brain.
+This is well above the disk space needed to image the parallelepiped volume encompassing a whole mouse brain.
 Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
@@
 SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
+Different colours (red, yellow and green) indicate the time-sensitivity (higher to lower) of each data movement.
 (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
@@
 	\centering
-		\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
+		\caption[Data production]{Data production rates for typical camera operation.\label{tab:dataproduction}}
 		\begin{tabular}{lrl}
-		frame rate																	& 44			& Hz	\\
-		size of 1 frame															& 8				& MB	\\
-		frames per stack														& 3900		& 		\\
-		size of original stack											& 30.4		& GB	\\
-		size of converted stack											& 3				& GB	\\
-		stack acquisition time											& 88.6		& s		\\
-		stack conversion time												& 140			& s		\\
-		time ratio conversion/ acquisition					& 1.6			& 		\\
-		data production rate												& +1.2		&	TB/h\\
-		data conversion rate												& -0.7		&	TB/h\\
-		net rate																		& +0.5		&	TB/h\\
-		SSD RAID																		& 10.9		& TB	\\
-		max acquisition time to fill up SSDs				& 21			& h		\\
-		max tomo size to fill up SSDs								& 25.4		& TB	\\
+		\\
+		Voxel size																								& $0.234 \times 0.234 \times 2$	& $\micro\text{m}^3$ 	\\
+		Frame rate																								& 44														& Hz								\\
+		Frame size																								& $2048 \times 2048$ 						& pixels						\\
+		Frame disk size																						& 8									 						& MB								\\
+		Data production rate																			& 1.2								 						& TB/h 							\\
+		Data conversion rate																			& 0.7								 						& TB/h 							\\
+		Net SSD filling rate																			& 0.5								 						& TB/h 							\\
+		SSD RAID size																							& 10.9							 						& TB								\\
+		Max acquisition time to fill up SSDs											& 21.8							 						& h									\\
+		Max raw data size that can be acquired continuously				& 25.4							 						& TB								\\
+		Max volume that can be imaged 														& 1.24							 						& $\text{cm}^3$ 		\\
+		(considering 10\% superposition between adjacent stacks)	&										 						&										\\
 		\end{tabular}
@@
 
-\section{Outlook}
-where are we going next with this? ask Leo Onofri and Giulio to contribute to this, issues data mangament, aberration correction
-mapping of complementary data sets obtained in the same system, eg structural connectivity, morphology and gene expression.
-
 \begin{landscape}
@@
 		Component														&	Manufacturer																& Part\# 						& Specifications 														\\\hline\hline
-		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\
-																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																	\\
-																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised														\\
-																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
-																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
-		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
+		\multirow{5}{*}[2.5em]{Lasers} 			& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden}		& MLD								& 405nm,  80mW, s-polarised											\\
+																				&																							& MLD								& 445nm, 50mW, s-polarised											\\
+																				&   																					& Calypso						& 491nm, 50mW, s-polarised											\\
+																				&																							& Fandango					& 515nm, 50mW, s-polarised											\\
+																				&																							& Jive							& 561nm, 50mW, s-polarised											\\\hline
+		AOTF																& AA Opto-Electronic, France									&AOTFnC-400.650-TN 	&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
 		Laser modulator 										& Qioptiq	GmbH, Germany												& LM 0202 VIS ADP		& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V			\\\hline
@@
 		Galvo scanner 											& Cambridge Technology, USA										& 6220H 						& small angle step response $200\mu s$								\\\hline		
-		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)													\\
+		\multirow{2}{*}[0.6em]{Objectives}	&	Nikon; Japan																& Plan Fluor EPI 		& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)						\\
 																				& Olympus, Japan															& LMPLFLN20X 				& 20x0.4NA, WD 12mm, EFL 9mm (detection)							\\\hline
@@
 																				&																							& M-116 						& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
-		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
+		Camera 															& Hamamatsu, Japan														& Orca Flash4.0 	V2.0	& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
 		DAQ board														& National Instruments, USA										& NI PCIe-6353			& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
-		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
+		Workstation 1												& Dell, USA																		& T7500							&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, OS Windows 7 64 bit}\\
+		Workstation 2												& Dell, USA																		& T5600							&  \pbox[t]{10.5cm}{8GB RAM, Intel Xeon Processor E5-2620 @ 2 GHz, OS Windows 7 64 bit}\\
 		\end{tabular}
@@
 
-\begin{landscape}
 \begin{table}[t!]
 	\centering
-		\caption[Resolution]{Imaging properties and derived quantities.
-The thickness of the light sheet is approximately of the same size as the depth of field of the high NA detection lens.\label{tab:resolution}}
-		\begin{tabular}{lrlrl}
-		\multicolumn{5}{l}{Detection}\\\hline\hline  
-		wavelength																	&	$\lambda$				&																																					& 0.5			& $\mu m$	\\
-		refractive index														&	n								&																																					& 1.45		& 				\\
-		numerical aperture 													&	$\text{NA}_d$		&																																					& 1				& 				\\
-		%angular aperture 													& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
-		magnification 															& $M_{\text{eff}}$&	$= \nicefrac{f_{\text{TL}}}{\text{EFL}}$																& 27.8		&					\\
-		tube lens 																	& $f_{\text{TL}}$	&																																					& 200			&	$mm$		\\
-		effective focal length objective						& EFL							& $=\nicefrac{f_{\text{TL}}}{M}$																					& 7.2			& $mm$		\\
-		diameter back focal plane										& BFP							& $= 2\cdot \text{EFL} \cdot \text{NA}_d$																	& 14.4		& $mm$		\\
-		field number																& FN							&																																					& 18			& $mm$		\\
-		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.65		& $mm$		\\
-		depth of field															& $\Delta$				& $=\nicefrac{\lambda \cdot n}{(\text{NA}_d)^2}+ \nicefrac{n \cdot e}{M \cdot \text{NA}_d}$	& 1.06 		& $\mu m$	\\ 
-		Airy radius lat.														& $r_A$						& $=\nicefrac{0.61 \lambda}{\text{NA}_d}$																	& 0.31		& $\mu m$	\\\\
-		\multicolumn{5}{l}{Excitation}\\\hline\hline
-		numerical aperture 													&	$\text{NA}_e$		&																																					& 0.3			& 				\\
-		magnification,	nominal											& m								&																																					& 10			&					\\
-		tube lens 																	& $f_{\text{tl}}$	&																																					& 100			&	$mm$		\\
-		effective focal length, objective						& efl							& $=\nicefrac{f_{\text{tl}}}{m}$																					& 20			& $mm$		\\
-		magnification, effective										& $m_e$						&	$=\nicefrac{f_{\text{tl}}}{\text{efl}}$																	& 5				&					\\
-		refractive index														&	$\eta$					&																																					& 1				& 				\\
-		beam radius																	& $\omega$				&																																					& 4.5			& $mm$		\\
-		%Airy radius lat.														& $r_a$						& $=\nicefrac{0.61 \lambda}{\text{NA}_e}$																	& 1.02		& $\mu m$	\\
-		min light sheet waist												& $\omega_0$			& $=\nicefrac{\lambda \text{efl}}{\pi \omega}$														& 1.41		& $\mu m$	\\
-		confocal parameter													& b								& $=\nicefrac{2 \pi \omega_0^2}{\lambda}$																	& 25.15		& $\mu m$	\\\\
-		\multicolumn{5}{l}{Camera}\\\hline\hline
-		cell size																		& e								&																																					& 6.5			&	$\mu m$	\\
-		effective area 															& $r^2$						&																																					& $13.3^2$	&	$\text{mm}^2$	\\
-		line read out time													& t								&																																					& 9.7			&	$\mu s$	\\
-		line exposure time													& l								&																																					& 3				&	ms			\\
-		slit width, camera space										& $d_c$						& $=\nicefrac{l \cdot e}{t} $																							& 2				&	mm	\\
-		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 0.72		&	mm	\\
-		frame rate																	& $\nu$						&	$=\nicefrac{1}{(2048 \cdot t + l})$																			& 43.6		& Hz\\
+		\caption[Main formulas]{Overview of the main formulas related to light sheet microscopy.
+In the table, $f_{\text{TL}}^{\text{design}}$ is the focal length of the tube lens for which the objective has been designed (200 mm for Leica and Nikon, 180 mm for Olympus and 165 mm for Zeiss), $f_{\text{TL}}^{\text{real}}$ the focal length of the tube lens actually employed, $\text{M}$ the nominal magnification of the objective, $n$ the refractive index of the immersion medium, $\lambda_0$ the wavelength in vacuum, $\lambda$ the wavelength in the medium, $w$ the $1/e^2$ radius of the Gaussian beam at the objective back focal plane, FN the field number of the objective, $p$ the physical pixel size, $r_{\text{chip}}$ the size of the camera chip, $t_{\text{shutter}}$ the pace of the rolling shutter (i.e.
+the time between exposure start in subsequent lines), $ t_{\text{exp}}$ the line exposure time.
+The subscripts $_i$ and $_d$ refers to illumination and detection, respectively.
+\label{tab:resolution}}
+		\begin{tabular}{lrcl}
+		\\
+		\multicolumn{4}{l}{General formulas for microscope objectives}\\\hline\hline 
+		Nominal focal length							& $f$ 													& $=$		& $f_{\text{TL}}^{\text{design}}/\text{M}$				\\	
+		Effective focal length						& $f^{\text{eff}}$							& $=$		& $nf$													\\
+		Effective magnification						& $\text{M}^{\text{eff}}$				& $=$		& $f_{\text{TL}}^{\text{real}}/f^{\text{eff}}$			\\\\
+		\multicolumn{4}{l}{Excitation (Gaussian)}\\\hline\hline	
+		Beam waist												&$w_0$													& $=$ 	& $ \lambda f_{\text{i}}^{\text{eff}} / \pi w$				\\
+		Axial resolution									&$\text{FWHM}_{\text{axial}}$		& $=$   & $1.177 w_0 $											\\
+		Confocal parameter								& b															& $=$   & $2 \pi \omega_0^2 / \lambda$							\\
+																			&  															& $=$   & $2 \lambda {(f_{\text{i}}^{\text{eff}})}^2 / \pi w^2 $	\\\\
+		\multicolumn{4}{l}{Detection}\\\hline\hline  
+		Radial resolution									&$\text{FWHM}_{\text{radial}}$	& $=$		& $0.5 \lambda_0 / \text{NA}_{d}$						\\
+		Objective field size							& S															& $=$		& $\text{FN}/{\text{M}}$								\\\\
+		\multicolumn{4}{l}{Camera}\\\hline\hline  
+		Pixel size object space						& $ p_{\text{object}}$					& $=$		& $p/  \text{M}^{\text{eff}}$							\\
+		Camera FOV object space						&$\text{FOV}_{\text{object}}$		& $=$		& $r_{\text{chip}} / \text{M}^{\text{eff}}$				\\
+																			&																& $=$		& $p_{\text{object}} \cdot \#_{\text{pixels}}$			\\
+		Slit width on camera							& $s_{\text{camera}}$						& $=$		& $ p \cdot t_{\text{exp}} / t_{\text{shutter}} $			\\
+		Slit width in object space				& $s_{\text{object}}$						& $=$		& $ s_{\text{camera}}/ \text{M}^{\text{eff}}$			\\
+		Frame rate												& $\nu$													& $=$		& $1/(\#_{\text{horiz. lines}} \cdot t_{\text{shutter}} + t_{\text{exp}})$ \\\\
+
 		\end{tabular}
 \end{table}
-\end{landscape}
 
@@
 \acknowledgments
-workshop boys cause they are amazing.
+The authors are grateful to xy from the mechanics workshop at LENS for the their expertise in the conception and fabrication of the sample chamber.
+We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.
 Human Brain Project tutta la vita.
-GARR gave us a beautiful 10gb fiber to cineca
-CINECA for hosting us on pico
 
@@
 \bibitem{Huisken2009} J. Huisken and D. Y. Stainier, ``Selective plane illumination microscopy techniques in developmental biology," \emph{Development} \textbf{136}(12), 1963–1975 (2009).
+
+\bibitem{Keller2008a} P.
+J.
+Keller and E.
+H.
+K.
+Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light sheet fluorescence microscopy," \emph{urr.
+Opin.
+Neurobiol.} \textbf{18}(6), 624–632 (2008).
+
+\bibitem{Keller2008b} P.
+J.
+Keller, A.
+D.
+Schmidt, J.
+Wittbrodt, and E.
+H.
+K.
+Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
+
+\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light sheet microscopy with confocal slit detection," \emph{Optics express} \textbf{20}(19), 21805-21814 (2012).
 
@@
 
-\bibitem{Keller2008a} P.
-J.
-Keller and E.
-H.
-K.
-Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light sheet fluorescence microscopy," \emph{urr.
-Opin.
-Neurobiol.} \textbf{18}(6), 624–632 (2008).
-
-\bibitem{Keller2008b} P.
-J.
-Keller, A.
-D.
-Schmidt, J.
-Wittbrodt, and E.
-H.
-K.
-Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
-
-\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light sheet microscopy with confocal slit detection," \emph{Optics express} \textbf{20}(19), 21805-21814 (2012).
+\bibitem{Teich} M. C. Teich and B. E. A. Saleh, ``Fundamentals of photonics," \emph{Canada, Wiley Interscience} 3 (1991).
 
@@
 
-\bibitem{Frasconi2014} P. Frasconi, L. Silvestri, P. Soda, R. L. Cortini, F. S. Pavone and G. Iannello, ``" \emph{Bioinformatics} \textbf{30}(), i587-i593 (2014).
+\bibitem{castagna1997object} G. Castagna, \emph{``Object-Oriented Programming A Unified Foundation,"} Birkh{\"a}user, Boston (1997).
+
+\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
+
+\bibitem{Kovacevic2005} N.
+Kovacevic, J.
+T.
+Henderson, E.
+Chan, N.
+Lifshitz, J.
+Bishop, A.
+C.
+Evans, R.
+M.
+Henkelman, and X.
+J.
+Chen, "A Three-dimensional MRI Atlas of the Mouse Brain with Estimates of the Average and Variability", \emph{Cereb.
+Cortex} \textbf{15}(5), 639-45 (2005).
+
+%\bibitem{Frasconi2014} P. Frasconi, L. Silvestri, P. Soda, R. L. Cortini, F. S. Pavone and G. Iannello, ``" \emph{Bioinformatics} \textbf{30}(), i587-i593 (2014).
 
 \bibitem{Bria2012} A. Bria and G. Iannello,  ``TeraStitcher-A tool for fast automatic 3D-stitching of teravoxel-sized microscopy images,"  \emph{BMC bioinformatics} \textbf{13}(1), 316 (2012).
-
-\bibitem{castagna1997object} G. Castagna, \emph{``Object-Oriented Programming A Unified Foundation,"} Birkh{\"a}user, Boston (1997).
 
@@
 Pavone, \emph{submitted}.
-
-\bibitem{Kovacevic2005} N.
-Kovacevic, J.
-T.
-Henderson, E.
-Chan, N.
-Lifshitz, J.
-Bishop, A.
-C.
-Evans, R.
-M.
-Henkelman, and X.
-J.
-Chen, "A Three-dimensional MRI Atlas of the Mouse Brain with Estimates of the Average and Variability", \emph{Cereb.
-Cortex} \textbf{15}(5), 639-45 (2005).
-
-\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
 

### 2015-02-13 latex-style-files-spie-manuscript/manuscript_Leo.tex
- optical characterisation

@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging.}
+\keywords{Light sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging}
 
@@
 
-The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space.
-In particular, the radial (i.e.
-perpendicular to the detection axis) and axial (i.e.
-parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction.
-In a light sheet microscope, axial and radial resolutions are determined by the numerical aperture (NA) of the illumination and detection optics, respectively.
-The radial PSF is a standard Airy function, whose FWHM is given by:
-
-\begin{equation}
-\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
-\end{equation}
-
-$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
-
-The axial resolution is given by the thickness of the light sheet.
-If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
-The $1/e^2$ radius of the beam waist is given by:
-\begin{equation}
-w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
-\end{equation}
-where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index).
-Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
-The axial FWHM is then given by:
-\begin{equation}
-\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
-\end{equation}
-
-The thickness of the light sheet is not constant throughout the field of view due to the limited depth of focus of the Gaussian beam.
-This latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius is not bigger than $\sqrt{2} w_0$:
-\begin{equation}
-b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
-\end{equation}
-
-The need to have an almost uniform resolution in the camera field of view (FOV) imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
-In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq ???$, resulting in $b \simeq ???$ and $\text{FWHM}_{\text{axial}} \simeq?????$.
-
-An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}.
-The reader is referred to this table as a quick guide to tailor the apparatus to their specific needs.
-
-AND HERE THE AMMAZING OURS DATAS
-
 \begin{figure}
@@
 
+The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space.
+In particular, the radial (i.e.
+perpendicular to the detection axis) and axial (i.e.
+parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (see Fig.
+\ref{fig:origin}, A).
+In a light sheet microscope, axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics, respectively.
+The radial PSF is a standard Airy function, whose FWHM is given by:
+
+\begin{equation}
+\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
+\end{equation}
+
+$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
+The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the the depth of field of the detection objective.
+If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
+The radius of the beam waist is given by:
+
+\begin{equation}
+w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
+\end{equation}
+
+where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index).
+Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
+The axial FWHM is then given by:
+
+\begin{equation}
+\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
+\end{equation}
+
+The thickness of the light sheet is not constant throughout the field of view (FOV) due to the limited depth of focus of the Gaussian beam.
+The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:
+
+\begin{equation}
+b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
+\end{equation}
+
+The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 1.6mm$.
+An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}.
+The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.
+
 For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.
+To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles.
+By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner.
+A linear fit to this data yielded the precise amplitude and offset for each galvo scanner hereby taking into account the confocal slit width itself such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.
 
@@
 		Beam waist												&$w_0$													& $=$ 				& $ \lambda f_{\text{i}}^{\text{eff}} / \pi w$				\\
-		Axial resolution									&$\text{FWHM}_{\text{axial}}$		& $=$   & $1.177 w_0 $											\\
+		Axial resolution									&$\text{FWHM}_{\text{axial}}$		& $\approx$   & $ 1.17 w_0 $											\\
 		Confocal parameter								& b															& $=$  				& $2 \pi \omega_0^2 / \lambda$							\\
@@
 \acknowledgments
-The authors are grateful to xy from the mechanics workshop at LENS for the their expertise in the conception and fabrication of the sample chamber.
+The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for the their expertise in the conception and fabrication of the sample chamber.
 We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.

### 2015-02-13 latex-style-files-spie-manuscript/manuscript_Leo.tex
-even more optical characterisation

@@
 \section{Sample mounting and motion}
+\label{sec:mounting}
 %Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
@@
 
+\subsection{Theoretical considerations}
 \begin{figure}
@@
 The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
-In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 1.6mm$.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$.
 An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}.
 The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.
+
+\subsection{Experimental characterisation}
 
@@
 A linear fit to this data yielded the precise amplitude and offset for each galvo scanner hereby taking into account the confocal slit width itself such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.
+
+From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated.
+The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera.
+For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?) embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).
+The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at 40 °C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
+The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}.
+The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175-70 \micro m$ in the sample space.
+For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg.
+Fig.\ref{fig:origin},A) throughout the image stack.
+After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths.
+The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.\ref{fig:origin},B) and the lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14 \micro) m$ respectively.
+The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
+The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig.
+\ref{fig:origin},C).
+$0.61 \micro m$
 
@@
 
+\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} 12(4), 227–229 (1987).
+
+\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} 63(1), 18–22 (2004).
+
 \bibitem{Silvestri2012} L.

### 2015-02-15 latex-style-files-spie-manuscript/manuscript_Leo.tex
- method section to exclude sample preparation from optical characterisation paragraph - find out bead size and company

@@
 \author{M.
-Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b,f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
+Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
 Pavone,\supscr{a,b,c,d}  }
@@
 \supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
-\supscrsm{f}Distrio, Amsterdam, The Netherlands}
+%\supscrsm{f}Distrio, Amsterdam, The Netherlands
+}
 
@@
 The comprehensive mapping and quantification of neuronal connections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution.
-We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact, clarified, whole-mount mouse brains.
+We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains.
 Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software.
@@
 To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets.
-The meso-scale neuroanatomy imaged at micron-scale resolution allows characterization and quantification of neuronal connections in unsectioned mouse brains.
+The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal connections in unsectioned mouse brains.
 \end{abstract}
@@
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
-This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap.
+This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap.
 Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise.
@@
 Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
-Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces.
+Those challenges include fast cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces.
 The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
-On the other hand, the imaging of large, intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent.
+On the other hand, the imaging of large intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent.
 This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.
 
-Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains.
-The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples.
+Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large clarified and structurally intact mouse brains.
+The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples.
 After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days.
-In addition, a full description of the the control hardware and software is presented.
-The microscope software coordinates each and every microscope component and ensures critical timing and synchronisation between those components.
+In addition, a full description of the control hardware and software is presented.
+The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components.
 The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light sheet community.
@@
 To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.
+\textit{Include sentence about data if we show any.}
 
@@
 \subsection{Laser unit}		
-The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A).
-The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components).
+The custom-made confocal light sheet microscope is equipped with 5 linearly polarised cw lasers for fluorescence excitation (Fig.
+\ref{fig:excitation},A).
+The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components).
 The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series).
@@
 An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
-The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
-First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
-A digital line is used to switch to zero the output of the pre-amplifier, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
+The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
+First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
+A digital line is used to switch the output of the pre-amplifier to zero, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
 After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).
@@
 
-Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
-The galvos are on planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
+Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
+The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
 The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber.
@@
 
-In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector.
-Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
+In its simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector.
+We collect fluorescence with an objective that is specifically designed for immersion in clearing solutions.
 The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm).
@@
 The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$.
-With a 200mm tube lens the field of view in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).
+With a 200mm tube lens the field of view (FOV) in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).
 
-In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor.
+In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}.
 With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms.
@@
 
-The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave.
-The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also paragraph \ref{sec:timing} on synchronisation).
+The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for the DAQ board which was operated as slave.
+The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation).
 Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast.
@@
    \caption{\label{fig:frame2} Schematic of sample mounting and motion.
-(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
+(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
 (B) The custom-made sample chamber is assembled with silicone bellows and seal rings.
-The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D).
-(E) Mounting of a clarified, fluorescently labelled brain.
+The clarified fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D).
+(E) Mounting of a clarified fluorescently labelled brain.
 The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.}
@@
 
-We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains.
-The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B).
+We designed a cubic water-tight sample chamber (Fig.
+\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently-labelled mouse brains.
+The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig.
+\ref{fig:frame2},B).
 All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
-In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C).
+In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig.
+\ref{fig:frame2},C).
 The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
-To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed.
-A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D).
+To fill the entire volume of the sample chamber approximately 250ml clearing solution are needed.
+A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig.
+\ref{fig:frame2},D).
 Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.
 
-To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation.
+To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation.
 While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
@@
 
-For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},E).
+For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Fig.
+\ref{fig:frame2},E).
 The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip.
@@
 
-The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space.
+The optical properties of a microscope can be summarised by the point-spread function (PSF), which is the image of a point source in object space.
 In particular, the radial (i.e.
@@
 parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (see Fig.
-\ref{fig:origin}, A).
-In a light sheet microscope, axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics, respectively.
-The radial PSF is a standard Airy function, whose FWHM is given by:
+\ref{fig:origin},A).
+In a light sheet microscope axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics respectively.
+The radial PSF is a standard Airy function whose FWHM is given by:
 
@@
 $\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
-The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the the depth of field of the detection objective.
+The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective.
 If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
@@
 where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index).
-Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
+Note that for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
 The axial FWHM is then given by:
@@
 
-The thickness of the light sheet is not constant throughout the field of view (FOV) due to the limited depth of focus of the Gaussian beam.
+The thickness of the light sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam.
 The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:
@@
 In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$.
-An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}.
+An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table \ref{tab:resolution}.
 The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.
@@
 By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner.
-A linear fit to this data yielded the precise amplitude and offset for each galvo scanner hereby taking into account the confocal slit width itself such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.
-
+A linear fit to this data yielded the precise amplitude and offset for each galvo scanner.
+The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.
 From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated.
 The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera.
-For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?) embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).
-The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at 40 °C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
-The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}.
-The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175-70 \micro m$ in the sample space.
-For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg.
-Fig.\ref{fig:origin},A) throughout the image stack.
-After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths.
-The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.\ref{fig:origin},B) and the lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14 \micro) m$ respectively.
-The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
+
+For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?).
+The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.
+\ref{fig:origin},B).
+The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively.
 The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig.
 \ref{fig:origin},C).
-$0.61 \micro m$
 
@@
 The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre).
-The data flow scheme is summarized in Figure \ref{fig:DataFlow}.
+The data flow scheme is summarized in Fig.
+\ref{fig:DataFlow}.
 
@@
 For these reasons, we extended the Terastitcher functionalities introducing the two following additional features: i) stitching of a specimen partitioned in a number of overlapping layers for the hippocampus reconstruction and, ii) coping with images containing more than one channel for the human brain tomography.
-With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depicts in Fig.1 the adopted strategy.
+With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depict in Fig.1 the adopted strategy.
 First of all, the various input layers, each of which is composed of several parallel overlapping stacks, are separately stitched by using the existing Terastitcher tool.
@@
 
-	Everybody take a look at Figure\ref{fig:LSMdata} because it is the best we have.
+	Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
 
@@
 The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane.
-Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Figure\ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives.
+Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Fig.
+\ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives.
 In the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
@@
 Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be.
-The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Figure\ref{fig:alignment},B).
+The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Fig.
+\ref{fig:alignment},B).
 Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
-With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Figure\ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Figure\ref{fig:alignment},D).
+With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Fig.
+\ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Fig.
+\ref{fig:alignment},D).
 
@@
 The first excitation objective was placed into the beam path and brought to focus onto the sample mirror which was adjusted to reflect the light back into the same objective through the irises.
-Using a shear plate and a beam splitter cube the back reflected light was qualitatively adjusted for collimation using translation along the excitation axis of the objective mount (Figure\ref{fig:alignment2},B).
-The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C).
+Using a shear plate and a beam splitter cube the back reflected light was qualitatively adjusted for collimation using translation along the excitation axis of the objective mount (Fig.
+\ref{fig:alignment2},B).
+The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Fig.
+\ref{fig:alignment2},C).
 This time collimation was checked with the light going through both objectives and so their confocal placement was insured.
-Both excitation arms were then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source, alternating between the two modalities illustrated in Figure\ref{fig:alignment2},A.
-Finally, the sample mirror was positioned in deflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).
+Both excitation arms were then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source, alternating between the two modalities illustrated in Fig.
+\ref{fig:alignment2},A.
+Finally, the sample mirror was positioned in deflection mode and the detection objective was aligned (Fig.
+\ref{fig:alignment2},D).
+
+\subsection{Methods}
+
+The fluorescent beads (\textsl{company size etc.}) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).
+The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
+The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}.
+The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175 \micro m-70 \micro m$ in the sample space.
+For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg.
+Fig.
+\ref{fig:origin},A) throughout the depth of the image stack.
+After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths.
+The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
 

### 2015-02-16 latex-style-files-spie-manuscript/manuscript_Leo.tex
- coordinate vs cummulative adjectives and their commas :/ - other thingies

@@
 \subsection{Theoretical considerations}
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{origin.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:origin} Optical characterisation.
-(A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian.
-(B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged.
-(C) The signal to noise ratio.}
-\end{figure}
 
@@
 
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{origin.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:origin} Optical characterisation.
+(A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian.
+(B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged.
+(C) The signal to noise ratio.}
+\end{figure}
+
 For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.
@@
 For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?).
-The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.
+The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit width on the camera (Fig.
 \ref{fig:origin},B).
 The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively.
-The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig.
+The experimentally determined lateral FWHM is larger than the theoretically expected value by a factor of three and this increase is most likely due to The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig.
 \ref{fig:origin},C).
@@
 
-\listoffigures
+%\listoffigures
 %pannel1: optical pathway, drawing images from chamber, sample mirror photos
@@
 
-\listoftables
+%\listoftables
 
@@
 
+\subsubsection{Sample preparation for optical characterisation}
 The fluorescent beads (\textsl{company size etc.}) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).

### 2015-02-16 latex-style-files-spie-manuscript/manuscript_snellendo.tex
- Leo came, saw and reverted - everything

--- 2015-02-15 latex-style-files-spie-manuscript/manuscript_Leo.tex
@@
 
-\title{Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains}
+\title{Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains}
 
@@
 \begin{abstract}
-The comprehensive mapping and quantification of neuronal connections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution.
-We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains.
+The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution.
+We have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains.
 Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software.
 The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.
-It can easily be adapted and integrated to other microscope systems and has been made freely available to the light sheet community.
-The unprecedented amount of data routinely generated by light sheet microscopy further requires novel strategies for data handling and storage.
+It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community.
+The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage.
 To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets.
-The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal connections in unsectioned mouse brains.
+The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains.
 \end{abstract}
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging}
+\keywords{Light-sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging}
 
@@
 
-The highly ambitious project of mapping and understanding each and every neuronal connection in the whole brain has been moved from the realm of wishful longing to feasible reality by the recent advent of light sheet fluorescent microscopy (LSFM).
+The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM).
 With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition.
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
-This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap.
-Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise.
-Hence LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths.
+This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate perpendicularly oriented paths where the excitation light-sheet and the detection focal plane overlap.
+Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise.
 
 Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
-Those challenges include fast cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces.
-The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
-On the other hand, the imaging of large intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent.
-This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.
+Those challenges include fast cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, the storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces.
+The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
+On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent.
+Therefore technological advances in LSFM need to be matched by novel development in the area of information- and biotechnology.
 
-Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large clarified and structurally intact mouse brains.
-The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples.
+Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains.
+The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples.
 After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days.
@@
 The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components.
-The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light sheet community.
-We further give a systematic and robust approach to handle, store and analyse light sheet microscopy data of tens of terabytes.
+%The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community.
+We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of tens of terabytes.
 To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.
-\textit{Include sentence about data if we show any.}
+The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.
 
@@
    %\end{center}
-   %\caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.
-The sample is illuminated with a planar light sheet (blue) perpendicular to fluorescence detection (green).
+   %\caption{\label{fig:Panel0} (A) Schematic of light-sheet microscopy.
+The sample is illuminated with a planar light-sheet (blue) perpendicular to fluorescence detection (green).
 (B) Mounting of a clarified, fluorescently labelled brain.
@@
 LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter.
-Inset: detection path.
+Green dotted: detection path.
 (B) Oblique view of the microscope.
@@
 \subsection{Laser unit}		
-The custom-made confocal light sheet microscope is equipped with 5 linearly polarised cw lasers for fluorescence excitation (Fig.
+The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised cw lasers for fluorescence excitation (Fig.
 \ref{fig:excitation},A).
@@
 The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series).
-An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines.
+An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter and intensity modulator.
+%which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines.
 The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity.
@@
 An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
-The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
+%The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
 First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
-A digital line is used to switch the output of the pre-amplifier to zero, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
+A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
 After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).
@@
 The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
-The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber.
+The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber.
 A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent.
 A guide to align objectives to a common focus can be found in the supplementary information.
-The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective.
+The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective.
 This generates incoherent illumination resulting in fewer artefacts.
 %cite{StelzerNatMeth2014}.
-Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.
+Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.
 
@@
 
-In its simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector.
-We collect fluorescence with an objective that is specifically designed for immersion in clearing solutions.
-The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm).
-To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
+%In its simplest form, the fluorescence detection unit of a light-sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector.
+Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
+The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm).
+%To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
 A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels.
-In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
+%In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
 The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$.
@@
 With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms.
-Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in approx.
-$l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
-This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of
-
-\begin{equation}
-s_{\text{object}}=\frac{l p}{M_{\text{eff}}}= 7.2 \micro m 
-\end{equation}
-
-in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective.
-With the given values of line exposure and line read out time, the camera acquires images at a frame rate of
-
-\begin{equation}
-\nu = \frac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz. 
-\end{equation}
+Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
+This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective.
+With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(\#_{\text{horiz.
+lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.
 
@@
 The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation).
-Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast.
+%Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast.
 The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.
@@
    \caption{\label{fig:frame2} Schematic of sample mounting and motion.
-(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light sheet and the detection focal plane overlap.
+(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light-sheet and the detection focal plane overlap.
 (B) The custom-made sample chamber is assembled with silicone bellows and seal rings.
@@
 
-To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation.
-While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
-The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample.
-Most commonly the vertical direction is chosen.
+To elucidate neuronal projections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation.
+%While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light-sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
+The problem of sample mounting in a light-sheet microscope arises from the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample.
+%Most commonly the vertical direction is chosen.
 Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.
@@
 \ref{fig:origin},A).
-In a light sheet microscope axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics respectively.
+In a light-sheet microscope axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics respectively.
 The radial PSF is a standard Airy function whose FWHM is given by:
@@
 $\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
-The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective.
-If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
+The axial resolution is dominated by the thickness of the light-sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective.
+If Gaussian beams are used for illumination, the thickness of the light-sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
 The radius of the beam waist is given by:
@@
 
-The thickness of the light sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam.
+The thickness of the light-sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam.
 The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:
@@
 The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
-In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$.
-An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table \ref{tab:resolution}.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$.
+An overview of the relevant formulas concerning the optical properties of a light-sheet microscope is given in Table \ref{tab:resolution}.
 The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.
@@
 \subsection{Experimental characterisation}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{origin.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:origin} Optical characterisation.
+(A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian.
+(B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged.
+(C) The signal to noise ratio.}
+\end{figure}
 
@@
 The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.
-From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated.
-The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera.
+From the same data the average FWHM of the Gaussian excitation line over the FOV of the camera was calculated as $(8.60\pm0.67)\micro m$ (n= 14).
 
-For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?).
-The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.
+For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories).
+The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig.
 \ref{fig:origin},B).
-The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively.
-The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig.
-\ref{fig:origin},C).
+The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively (n=10).
+The experimentally determined lateral FWHM was larger than the theoretically expected value of $0.26 \micro m$ by a factor of four and this increase was most likely due to....
+The experimentally determined axial FWHM was in good agreement with our measured light-sheet thickness of $8.6\micro m$ and marginally larger than the theoretically expected value.
 
-\section{Microscope management software}
+The SNR increased with increasing slit width up to a maximum at a slit width of $7 \micro m$ (Fig. \ref{fig:origin},C).
 
-\subsection{General design principles}
-
-The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software.
-Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging.
-The overall architecture of the software and its practical implementation were chosen to satisfy several principles:
-
-\begin{itemize}
-\item{\emph{User-friendliness}.
-The light sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
-\item{\emph{Working in a distributed environment}.
-The apparatus should deal with many independent hardware components, and with several data streams (see below).
-Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
-\item{\emph{Robustness and ease of maintenance}.
-Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
-Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
-\item{\emph{Reusability and scalability}.
-When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time.
-Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
-\end{itemize}
-
-Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods.
-An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
-This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
-Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
-The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation.
-In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
-Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
-
-\subsection{Murmex}
-
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{murmex.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
-   \end{figure}
-
-To let the software operate efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used.
-This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardized programming scheme.
-
-Basically, Murmex creates distributed finite state machines.
-These are design patterns in which one component proceeds from one particular state to another based on the message it receives either from itself or from other components.
-For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middleware facilitating message shipment and receival.
-These layers of abstraction are mostly hidden for the developers.
-The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
-The message-based communication allows for buffered, asynchronous and reliable message communication between several software components.
-Messages are routed by the broker to the specific software component by its ID.
-The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
-
-Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states.
-Usually, just a few of this states are actually used in standard application.
-An example of a standard implementation of the Murmex state machine for the camera is shown in Fig.
-\ref{fig:murmex}.
-Each Murmex component streams information about its current status to its 'observers' which are other components specified in its configuration file.
-Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on any number of computers connected through a local connection or the Internet.
-A special component, named ServiceManager (also based on Murmex), which must be running on each computer, allows to start executables remotely in user-defined compositions of components.
-This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but operated from one computer.
-
-\subsection{System timing and software organization}
+\section{System timing}
 \label{sec:timing}
@@
 
-A schematic overview of the hardware architecture of our light sheet microscope is shown in Fig.
+A schematic overview of the hardware architecture of our light-sheet microscope is shown in Fig.
 \ref{fig:connectivity}.
@@
 
-Synchronization of the camera rolling shutter to the scanning of the light sheet is achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
+Synchronization of the camera rolling shutter to the scanning of the light-sheet is achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
 In particular, the HSYNC signal from the camera is used, providing a true-type-logic (TTL) pulse every time the rolling shutter steps from one line to the next one.
-This trigger signal is used as a clock by the DAQ board, so that the line producing the light sheet moves step by step with the rolling shutter.
+This trigger signal is used as a clock by the DAQ board, so that the line producing the light-sheet moves step by step with the rolling shutter.
 The same HSYNC signal is used to trigger the DAQ digital signal sent to the electro-optic laser modulator.
@@
 
-Each hardware component (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component.
-Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
-Beyond hardware-related software, two additional Murmex components (named Stack and Tomo) orchestrate the operation of the entire system.
-
-The Stack component is used to acquire single image stacks along the detection axis, here the $z$ direction, and to this aim sends specific messages to coordinate the Camera and the Stages components.
-Stacks are collected by moving continuously the sample along $z$ while keeping the camera acquiring in free run.
-The translation speed is calculated such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
-The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack.
-Note that the Camera component must write data to disk in perfect time, otherwise the nominal $z$ position is of each frame is no more coincident with the real $z$ position of the plane imaged.
-For this reason, we set the process executing the Camera code to be of highest priority.
-The Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
-The Stack component also specify the name and the path of the \emph{.cxd} file.
-
-The Tomo component is used to image the entire sample by collecting many adjacent, parallel, partially-overlapping stacks.
-To this aim it exchanges messages with the Stack and the Stages components.
-The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped, or by providing a text file with the list of stacks to be collected ($x$ and $y$ coordinates, starting and ending $z$s).
-The Tomo component also informs the experimenter about the state of the acquisition by sending an email when acquisition is finished or if any trouble is experienced.
-
-All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
-Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
-
 \section{Data Management}
 
-The volume of a mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
+The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
 Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size amounts to $0.234\times0.234\times2$ $\micro\text{m}^3$.
@@
 
-This unprecedented amount of data challenges the traditional way we interact with our data.
-Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
+This tremendous amount of data challenges the traditional way we interact with our data.
+Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light-sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
 
-\subsection{Data handling and storage}
+\subsection{Data handling, storage and stitching}
 
-The camera used in our light sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
+The camera used in our light-sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
 Although this is already a large and expensive system for the current SSD technology, it is much smaller than the size of the raw datasets produced in each tomography.
@@
 
-While transferring the data from the SSD to the NAS, we also perform a file conversion from the proprietary Hamamatsu format to a more manageable one.
-We chose the TIFF format among the others because it permits to store 3D image with lossless compression in a single file.
+%Indeed, one stack may consist of thousands of slices of 1024 x 1024 pixels and with a color depth of 16 bits, leading easily to files of tens of Gigabytes each.
+To efficiently store raw data and make them suited for further processing, we have developed a tool for on-the-fly conversion of files generated during sample acquisitions to multi-page compressed TIFF format.
+
+While transferring data from the SSD to the NAS, we perform on-the-fly conversion of files generated during sample acquisitions to a multi-page and lossless-compressed TIFF format.
+%The TIFF format was chosen because it permits storage of a 3D image with lossless compression in a single file.
 Furthermore, it is a flexible and platform-independent format supported by numerous image processing applications.
-We thus developed a conversion module that leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library.
+Our conversion module leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library.
 The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
 Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format is read slice by slice to minimize memory requirements.
-The module has also an option to downsample the image or save the input image at full or reduced resolution, in order to adapt to storage availability.
+The conversion module runs concurrently with the microscope controlling software and it synchronizes to convert stack files as soon as they are completed.
+The module provides options to downsample the image or to save the input image at full or reduced resolution in order to adapt to storage requirements.
 Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling unaltered.
-This kind of downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude.
+This downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude.
 Thus the parallelepiped volume containing the whole mouse brain can be represented using about 2-3 TB of disk space.
@@
 The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition.
-Thus, although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
-The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size:
-\begin{equation}
-R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}\,,
-\end{equation}
+Thus, although file conversion drastically reduces data size, in the current implementation it is slower than data production.
+The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
 where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.
@@
 
-\subsection{Stitching and visualisation}
+%relevant dimensions in typical acquisition sessions
 
-Given the limited field of view of the microscope, the acquisition of macroscopic specimens required many parallel image stacks to cover all the volume.
-Thus, in order to achieve a 3D image of the whole specimen from raw data, the Terastitcher\cite{Bria2012} has been recently proposed, i.e.
-a stitching tool capable to deal with teravoxel-sized images.
-However, the Terastitcher does not support input data acquired through the serial sectioning procedure, which leads to a specimen partitioned in different layers.
-Furthermore, only single channel images can be processed.
-For these reasons, we extended the Terastitcher functionalities introducing the two following additional features: i) stitching of a specimen partitioned in a number of overlapping layers for the hippocampus reconstruction and, ii) coping with images containing more than one channel for the human brain tomography.
-With respect to the first requirement, that is allowing a complete reconstruction of a multi-layered raw data, we schematically depict in Fig.1 the adopted strategy.
-First of all, the various input layers, each of which is composed of several parallel overlapping stacks, are separately stitched by using the existing Terastitcher tool.
-After this preliminary step,  leveraging the layer coordinates provided by the instrument, we import the processed layers as a new volume where each layer has a partial overlap with adjacent layers.
-Furthermore, each layer is organized in a non-overlapping tiled format, enabling the application of a multi MIP-NCC approach\cite{Bria2012}, which computes the displacement  between two adjacent layers along all of the three directions (Fig.
-1).
-When a displacement computation for each pair of adjacent layers has been computed, the overlapping regions are merged through a blending procedure which smooths the transition between layers, resembling once more the procedure used by Terastitcher for combining adjacent stacks.
-Finally, we note that due to the repositioning of each layer, the volume containing the reconstructed specimen might contain empty regions, which are thereby filled with black voxels.
-Turning our attention to the second additional feature, that is handling multi-channel images, the Terastitcher has been extended so that the MIP-NCC algorithm used for displacement computation can work on an image, which can be either
-the fusion of the input channels or one of the input channels.
-This permits to privilege the channel with more information content over the other channels as well as discard noisy channels.
-Note that the reconstructed 3D image can be produced with the same channel composition of raw data.
+After acquisition, the tiled raw image produced has to be stitched.
+To perform this operation we have used the TeraStitcher\cite{Bria2012}, a fully automated stitching designed to deal with tiled images of virtually unlimited size.
+TeraStitcher can run on machines with limited resources with a performance essentially determined only by the transfer rate towards secondary storage.
+TeraStitcher can be freely downloaded from https://github.com/abria/TeraStitcher.
 
@@
 
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[height=16cm]{LSMdata.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:LSMdata} Whole mouse brain tomography.
+	%\begin{figure}
+   %\begin{center}
+   %\begin{tabular}{c}
+   %\includegraphics[height=16cm]{LSMdata.eps}
+   %\end{tabular}
+   %\end{center}
+   %\caption{\label{fig:LSMdata} Whole mouse brain tomography.
 Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective).
@@
 Scale bar = 100 µm.}
-   \end{figure}
-
-	Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
+   %\end{figure}
+	%
+	%Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
 
 \section{Conclusion}
-summary
-Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a combination of unprecedented spatio-temporal scale.
-The impact of this unique measurement technique will continue to revolutionise the field of whole brain connectomics due to its ability to record millions of images over the course of days or even weeks.
+
+Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a extraordinary spatio-temporal scale.
+The impact of this measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks.
 The data produced in this fashion easily amounts several TB per data set and needs to be stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods.
-The latter need to be robust, standarised and fully automated processes yet allow for flexible, exploratory and tailored analysis.
+The latter need to be robust, standardised and fully automated processes yet allow for flexible, exploratory and tailored analysis.
 
@@
 
-\begin{table}[t!]
-	\centering
-		\caption[Main formulas]{Overview of the main formulas related to light sheet microscopy.
-In the table, $f_{\text{TL}}^{\text{design}}$ is the focal length of the tube lens for which the objective has been designed (200 mm for Leica and Nikon, 180 mm for Olympus and 165 mm for Zeiss), $f_{\text{TL}}^{\text{real}}$ the focal length of the tube lens actually employed, $\text{M}$ the nominal magnification of the objective, $n$ the refractive index of the immersion medium, $\lambda_0$ the wavelength in vacuum, $\lambda$ the wavelength in the medium, $w$ the $1/e^2$ radius of the Gaussian beam at the objective back focal plane, FN the field number of the objective, $p$ the physical pixel size, $r_{\text{chip}}$ the size of the camera chip, $t_{\text{shutter}}$ the pace of the rolling shutter (i.e.
-the time between exposure start in subsequent lines), $ t_{\text{exp}}$ the line exposure time.
-The subscripts $_i$ and $_d$ refers to illumination and detection, respectively.
-\label{tab:resolution}}
-		\begin{tabular}{lrcl}
-		\\
-		\multicolumn{4}{l}{General formulas for microscope objectives}\\\hline\hline 
-		Nominal focal length							& $f$ 													& $=$					& $f_{\text{TL}}^{\text{design}}/\text{M}$				\\	
-		Effective focal length						& $f^{\text{eff}}$							& $=$					& $nf$													\\
-		Effective magnification						& $\text{M}^{\text{eff}}$				& $=$					& $f_{\text{TL}}^{\text{real}}/f^{\text{eff}}$			\\\\
-		\multicolumn{4}{l}{Excitation (Gaussian)}\\\hline\hline	
-		Beam waist												&$w_0$													& $=$ 				& $ \lambda f_{\text{i}}^{\text{eff}} / \pi w$				\\
-		Axial resolution									&$\text{FWHM}_{\text{axial}}$		& $\approx$   & $ 1.17 w_0 $											\\
-		Confocal parameter								& b															& $=$  				& $2 \pi \omega_0^2 / \lambda$							\\
-																			&  															& $=$   			& $2 \lambda {(f_{\text{i}}^{\text{eff}})}^2 / \pi w^2 $	\\\\
-		\multicolumn{4}{l}{Detection}\\\hline\hline  
-		Radial resolution									&$\text{FWHM}_{\text{radial}}$	& $=$					& $0.5 \lambda_0 / \text{NA}_{d}$						\\
-		Objective field size							& S															& $=$					& $\text{FN}/{\text{M}}$								\\\\
-		\multicolumn{4}{l}{Camera}\\\hline\hline  
-		Pixel size object space						& $ p_{\text{object}}$					& $=$					& $p/  \text{M}^{\text{eff}}$							\\
-		Camera FOV object space						&$\text{FOV}_{\text{object}}$		& $=$					& $r_{\text{chip}} / \text{M}^{\text{eff}}$				\\
-																			&																& $=$					& $p_{\text{object}} \cdot \#_{\text{pixels}}$			\\
-		Slit width on camera							& $s_{\text{camera}}$						& $=$					& $ p \cdot t_{\text{exp}} / t_{\text{shutter}} $			\\
-		Slit width in object space				& $s_{\text{object}}$						& $=$					& $ s_{\text{camera}}/ \text{M}^{\text{eff}}$			\\
-		Frame rate												& $\nu$													& $=$					& $1/(\#_{\text{horiz. lines}} \cdot t_{\text{shutter}} + t_{\text{exp}})$ \\\\
-
-		\end{tabular}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 K.
-Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light sheet fluorescence microscopy," \emph{urr.
+Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light-sheet fluorescence microscopy," \emph{urr.
 Opin.
@@
 K.
-Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
+Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light-sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
 
-\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light sheet microscopy with confocal slit detection," \emph{Optics express} \textbf{20}(19), 21805-21814 (2012).
+\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light-sheet microscopy with confocal slit detection," \emph{Optics express} \textbf{20}(19), 21805-21814 (2012).
 
@@
 Weber and J.
-Huisken, ``Multilayer mounting enables long-term imaging of zebrafish development in a light sheet microscope," \emph{Development} \textbf{139}(17), 3242-3247 (2012).
+Huisken, ``Multilayer mounting enables long-term imaging of zebrafish development in a light-sheet microscope," \emph{Development} \textbf{139}(17), 3242-3247 (2012).
 
@@
 Huisken and P.
-Tomancak, ``OpenSPIM-an open access platform for light sheet microscopy," \emph{arXiv} reprint arXiv:1302.1987, 3242-3247 (2013).
+Tomancak, ``OpenSPIM-an open access platform for light-sheet microscopy," \emph{arXiv} reprint arXiv:1302.1987, 3242-3247 (2013).
 
@@
 S.
-Pavone,  ``Confocal light sheet microscopy: micron-scale neuroanatomy of the entire mouse brain," \emph{Opt Express} \textbf{20}(18), 20582-20598 (2012).
+Pavone,  ``Confocal light-sheet microscopy: micron-scale neuroanatomy of the entire mouse brain," \emph{Opt Express} \textbf{20}(18), 20582-20598 (2012).
 
@@
    \end{center}
-   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope.
+   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light-sheet microscope.
 AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises.
@@
 
-For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
+For light-sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
 The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane.
@@
 
-The fluorescent beads (\textsl{company size etc.}) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).
-The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
+\subsubsection{Sample preparation for optical characterisation}
+The fluorescent beads (CP01F, Bang Laboratories, $0.51 \micro m$ diameter) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).
+The low melting point agarose (A-4018, Sigma-Aldrich) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
 The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}.
@@
 
+\subsubsection{Sample preparation for whole brain imaging}
+
+\subsection{Software management}
+
+\subsubsection{General design}
+
+The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software written in the LabVIEW language (National Instruments, Austin, US).
+Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, stringent software design is a primary concern.
+The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance.
+This means, the apparatus should be able to deal with many independent hardware components, and with several data streams (see below).
+Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.
+Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of data.
+
+%\begin{itemize}
+%\item{\emph{User-friendliness}.
+The light-sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
+%\item{\emph{Working in a distributed environment}.
+The apparatus should deal with many independent hardware components, and with several data streams (see below).
+Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
+%\item{\emph{Robustness and ease of maintenance}.
+Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
+Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
+%\item{\emph{Reusability and scalability}.
+When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time.
+Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
+%\end{itemize}
+
+%Our microscope management software has been written in LabVIEW (), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. 
+An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
+This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
+Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
+%The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation.
+In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
+Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
+
+\subsubsection{Murmex}
+\label{sec:murmex}
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{murmex.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
+   \end{figure}
+
+To operate the software efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used.
+This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardized programming scheme.
+
+Murmex creates distributed finite state machines, design patterns in which one component proceeds from a particular state to another based on the message it receives either from itself or from other components.
+For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middle-ware, however, these layers of abstraction are mostly hidden from the developers.
+%The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
+Buffered, asynchronous and reliable communication between several software components is established by the routing of messages by the broker to the specific software component pinpointed by its ID.
+%The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
+Murmex has twelve pre-defined states (eg, Initialise, Configure, Start, Stop, Proceed, Update) and a generic state for implementing custom states.
+Usually, just a few of this states are actually used in standard application.
+An example of a standard implementation of the Murmex state machine for the camera is shown in Fig.
+\ref{fig:murmex}.
+Each Murmex component streams information about its current status to its 'observers' which are other components specified in its configuration file.
+Using this oberserver/observee hierarchy, it is possible to design a large and complex network of different components, running on various computers connected through a local connection or the internet while maintaining precise timing and synchronisation.
+%A special component, named ServiceManager (also based on Murmex), which must be running on each computer, allows to start executables remotely in user-defined compositions of components.
+This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but operated from one computer.
+
+\subsubsection{Microscope software}
+Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component (see supplementary information \ref{sec:murmex}).
+Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Beyond hardware-related software, two additional Murmex components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.
+
+The Stack component is used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
+Stacks are collected by continuously moving the sample along $z$ while keeping the camera acquiring in free run.
+The translation speed is calculated such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
+The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
+The Camera component must write data to disk with perfect synchronisation, otherwise the nominal $z$ position of each frame is no more coincident with the real $z$ position of the plane imaged.
+For this reason, we set the process executing the Camera code to be of highest priority.
+Additionally, the Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
+%The Stack component also specify the name and the path of the \emph{.cxd} file.
+
+The Tomo component is a high level component which coordinates the acquisition of adjacent, parallel, partially-overlapping stacks. %It exchanges messages with the Stack and the Stages components.
+The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a text file with the coordinates of individual stacks to be collected.
+The Tomo component informs the experimenter via email when the acquisition is terminated either cleanly or through errors.
+
+All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
+Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
+
+\subsection{Formulas}
+\begin{table}[t!]
+	\centering
+		\caption[Main formulas]{Overview of the main formulas related to light-sheet microscopy.
+In the table, $f_{\text{TL}}^{\text{design}}$ is the focal length of the tube lens for which the objective has been designed (200 mm for Leica and Nikon, 180 mm for Olympus and 165 mm for Zeiss), $f_{\text{TL}}^{\text{real}}$ the focal length of the tube lens actually employed, $\text{M}$ the nominal magnification of the objective, $n$ the refractive index of the immersion medium, $\lambda_0$ the wavelength in vacuum, $\lambda$ the wavelength in the medium, $w$ the $1/e^2$ radius of the Gaussian beam at the objective back focal plane, FN the field number of the objective, $p$ the physical pixel size, $r_{\text{chip}}$ the size of the camera chip, $t_{\text{shutter}}$ the pace of the rolling shutter (i.e.
+the time between exposure start in subsequent lines), $ t_{\text{exp}}$ the line exposure time.
+The subscripts $_i$ and $_d$ refers to illumination and detection, respectively.
+\label{tab:resolution}}
+		\begin{tabular}{lrcl}
+		\\
+		\multicolumn{4}{l}{General formulas for microscope objectives}\\\hline\hline 
+		Nominal focal length							& $f$ 													& $=$					& $f_{\text{TL}}^{\text{design}}/\text{M}$				\\	
+		Effective focal length						& $f^{\text{eff}}$							& $=$					& $nf$													\\
+		Effective magnification						& $\text{M}^{\text{eff}}$				& $=$					& $f_{\text{TL}}^{\text{real}}/f^{\text{eff}}$			\\\\
+		\multicolumn{4}{l}{Excitation (Gaussian)}\\\hline\hline	
+		Beam waist												&$w_0$													& $=$ 				& $ \lambda f_{\text{i}}^{\text{eff}} / \pi w$				\\
+		Axial resolution									&$\text{FWHM}_{\text{axial}}$		& $\approx$   & $ 1.17 w_0 $											\\
+		Confocal parameter								& b															& $=$  				& $2 \pi \omega_0^2 / \lambda$							\\
+																			&  															& $=$   			& $2 \lambda {(f_{\text{i}}^{\text{eff}})}^2 / \pi w^2 $	\\\\
+		\multicolumn{4}{l}{Detection}\\\hline\hline  
+		Radial resolution									&$\text{FWHM}_{\text{radial}}$	& $=$					& $0.5 \lambda_0 / \text{NA}_{d}$						\\
+		Objective field size							& S															& $=$					& $\text{FN}/{\text{M}}$								\\\\
+		\multicolumn{4}{l}{Camera}\\\hline\hline  
+		Pixel size object space						& $ p_{\text{object}}$					& $=$					& $p/  \text{M}^{\text{eff}}$							\\
+		Camera FOV object space						&$\text{FOV}_{\text{object}}$		& $=$					& $r_{\text{chip}} / \text{M}^{\text{eff}}$				\\
+																			&																& $=$					& $p_{\text{object}} \cdot \#_{\text{pixels}}$			\\
+		Slit width on camera							& $s_{\text{camera}}$						& $=$					& $ p \cdot t_{\text{exp}} / t_{\text{shutter}} $			\\
+		Slit width in object space				& $s_{\text{object}}$						& $=$					& $ s_{\text{camera}}/ \text{M}^{\text{eff}}$			\\
+		Frame rate												& $\nu$													& $=$					& $1/(\#_{\text{horiz. lines}} \cdot t_{\text{shutter}} + t_{\text{exp}})$ \\\\
+
+		\end{tabular}
+\end{table}
+
 %\end{spacing}

### 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo.tex
- added pics for dc controller and axis - shuffled data pic

@@
 
-	%\begin{figure}
-   %\begin{center}
-   %\begin{tabular}{c}
-   %\includegraphics[height=16cm]{LSMdata.eps}
-   %\end{tabular}
-   %\end{center}
-   %\caption{\label{fig:LSMdata} Whole mouse brain tomography.
-Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective).
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   \includegraphics[width=\textwidth]{data_panel.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:LSMdata} Whole mouse brain tomography.
+Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective.
 (A) 3D rendering of a parvalbumin-dTomato brain.
-(B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm.
-(C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C.
-Scale bar = 100 µm.}
-   %\end{figure}
-	%
-	%Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
+(B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$.
+(C,D,E) High resolution insert, of the stack corresponding to red boxes in C.
+Scale bar = $100 \micro m$.}
+   \end{figure}
+
+	To exemplify the imaging capabilities of our microscope see Fig. \ref{fig:LSMdata}.
 
@@
 %\listoftables
-
+\pagebreak
 \section{Supplementary information}

### 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
- merged with ludo: data text and data sample preparation - updated acknowledgement with copy pasta sentence and marco - new RS232 daisy chain in image - subdiffraction replaced with nanometric

--- 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo.tex
@@
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
-This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate perpendicularly oriented paths where the excitation light-sheet and the detection focal plane overlap.
+This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination.
 Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise.
+Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.
 
@@
 
-\section{Optical path}
+\section{Optical setup}
 
@@
 
-\section{Sample mounting and motion}
+\subsection{Sample mounting and motion}
 \label{sec:mounting}
@@
 
-\section{Optical characterisation}
+\subsection{Optical characterisation}
 
-\subsection{Theoretical considerations}
+\subsubsection{Theoretical considerations}
 
@@
 
-\subsection{Experimental characterisation}
+\subsubsection{Experimental characterisation}
 
@@
 
-For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories).
+For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories).
 The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig.
 \ref{fig:origin},B).
-The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively (n=10).
-The experimentally determined lateral FWHM was larger than the theoretically expected value of $0.26 \micro m$ by a factor of four and this increase was most likely due to....
-The experimentally determined axial FWHM was in good agreement with our measured light-sheet thickness of $8.6\micro m$ and marginally larger than the theoretically expected value.
+The lateral and axial FWHMs were $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively, averaged through stack depths and confocal slit widths.
+The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four while the experimentally determined axial FWHM was 1.6x larger than the theoretically calculated value of $5.13 \micro m$.
+The discrepancies, most notably in the lateral direction, are likely caused by aberrations introduced by the gel embedding the fluorescent beads.
 
-The SNR increased with increasing slit width up to a maximum at a slit width of $7 \micro m$ (Fig. \ref{fig:origin},C).
+Qualitatively, the SNR increased with increasing slit width up to a maximum around the $1/e^2$ illumination beam diameter of $8.6 \micro m$ and then decreased again with further increasing slit width (Fig.
+\ref{fig:origin},C) in agreement with previous observations\cite{Baumgart2012}.
 
-\section{System timing}
+\section{Microscope management software}
+
+\subsection{General design}
+The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software written in the LabVIEW language (National Instruments, Austin, US).
+Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, stringent software design is a primary concern.
+The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance.
+This means, the apparatus should be able to deal with many independent hardware components, and with several data streams (see below).
+Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.
+Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of data.
+
+%\begin{itemize}
+%\item{\emph{User-friendliness}.
+The light-sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
+The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
+%\item{\emph{Working in a distributed environment}.
+The apparatus should deal with many independent hardware components, and with several data streams (see below).
+Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
+%\item{\emph{Robustness and ease of maintenance}.
+Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
+Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
+%\item{\emph{Reusability and scalability}.
+When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time.
+Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
+%\end{itemize}
+
+%Our microscope management software has been written in LabVIEW (), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. 
+An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
+This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
+Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
+%The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation.
+In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
+Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
+
+\subsection{System timing}
 \label{sec:timing}
@@
 
+\subsection{Software organisation}
+Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component (see supplementary information \ref{sec:murmex}).
+Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Beyond hardware-related software, two additional Murmex components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.
+
+The Stack component is used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
+Stacks are collected by continuously moving the sample along $z$ while keeping the camera acquiring in free run.
+The translation speed is calculated such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
+The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
+The Camera component must write data to disk with perfect synchronisation, otherwise the nominal $z$ position of each frame is no more coincident with the real $z$ position of the plane imaged.
+For this reason, we set the process executing the Camera code to be of highest priority.
+Additionally, the Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
+%The Stack component also specify the name and the path of the \emph{.cxd} file.
+
+The Tomo component is a high level component which coordinates the acquisition of adjacent, parallel, partially-overlapping stacks. %It exchanges messages with the Stack and the Stages components.
+The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a text file with the coordinates of individual stacks to be collected.
+The Tomo component informs the experimenter via email when the acquisition is terminated either cleanly or through errors.
+
+All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
+Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
+
 \section{Data Management}
-
 The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
@@
 Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light-sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
-
-\subsection{Data handling, storage and stitching}
 
@@
 
-\section{Data}
+\section{Representative results}
 
@@
 (C,D,E) High resolution insert, of the stack corresponding to red boxes in C.
-Scale bar = $100 \micro m$.}
+Scale bar = $100 \micro m$.
+Modified with permission from \cite{Costantini}.}
    \end{figure}
 
-	To exemplify the imaging capabilities of our microscope see Fig. \ref{fig:LSMdata}.
+Some representative data produced by our microscope are reported in Fig.
+\ref{fig:LSMdata}.
+With the apparatus describe in this paper, whole mouse brains can be imaged in their entirety (Fig.
+\ref{fig:LSMdata}A), maintaining a high quality of the image also while going deep inside the specimen (Figs.
+\ref{fig:LSMdata}B).
+The resolution and contrast of the images allow distinguish axonal tracts (Fig.
+\ref{fig:LSMdata}C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labeled.
+GABAergic interneurons can be clearly identified using a GAD2-cre-dTomato mouse (Fig.
+\ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain.
+Such whole-brain dataset can be used to localize cellular distribution in three-dimensions using automatic cell-detection software \cite{Frasconi2014}.
 
@@
 
-Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a extraordinary spatio-temporal scale.
+%essential features of a good discussion:
+%• Try to present the principles, factual relationships and generalisations shown by the results. Discuss dont recapitulate.
+%• Noting strengths and limitations.
+Point out nay exceptions or any lack of correlation and define unsettled points.
+Never take the high-risk alternative of trying to cover up or fudge data that do not quite fit.
+%• Show how your results and interpretations agree (or contrast) with previously published work.
+%• Significance of the work: ..so what?
+Don’t be shy, discuss the theoretical implimication of your work, as well as any possible practical applications.
+The discussion should end with a short summary or conclusion regarding the significance of the work.
+Leave with a bang not a whimper.
+%• State your conclusions as clearly as possible.
+%• Summarise your evidence for each conclusion. Never assume anything.
+%• Introduction and discussion function as a pair: the intro should have posed one or more questions.
+The discussion should indicate what the findings say about the answers.
+Be sure the discussion answers what the intro asked.
+%• Reverse funnel structure: first restate the main findings, then discuss how they relate to findings in previous research, then note implications and applications, and then identify unanswered questions well suited for future research.
+
+Light sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale.
 The impact of this measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks.
-The data produced in this fashion easily amounts several TB per data set and needs to be stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods.
-The latter need to be robust, standardised and fully automated processes yet allow for flexible, exploratory and tailored analysis.
+Here we have presented a complete and detailed framework for whole mouse brain imaging.
+Starting with a full description of our double-sided light sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation.
+The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods.
+Here we have presented a comprehensive, robust and fully automated pipeline of data management starting from the streaming of raw images up to the stitching of 3D data sets.
+
+%clearing
+The mouse brains imaged in our microscope are intrinsically opaque and need to be clarified before imaging.
+A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
+A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
+Crucially for the high-throughput imaging of large samples that we aim for the protocol, however, is also fast, easy and cheap.
+We therefore development a versatile, simple, rapid and inexpensive clearing method described elsewhere\cite{Costantini} which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies.
+
+%ao
+We have noticed that significant aberrations degrade image quality, especially at depths towards the end of the stack, even in refractive index-matched samples.
+Recently objectives specifically conceived for LSFM have become commercially available\cite{Marx2014} which have been designed for use with clearing solutions and typically also feature a correction collar for the compensation of a certain amount of spherical aberration.
+A complete correction of system-induced aberrations, however, requires the ability to also correct for residual spherical aberration and higher-order aberrations introduced by the sample mount, immersion medium and slight misalignments of the optical system.
+Additionally aberrations introduced by the sample itself degrade image quality.
+Additionally another problem inherent to light sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths.
+Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012,Wang2014}.
+The prospect of high quality images is especially essential for high through-put imaging methods like light-sheet microscopy and whole brain 3D reconstruction because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}.
+The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data.
+We have mounted the camera on a separate breadboard which leaves us with a lot of free infinity-corrected space in the detection path.
+In a future paper we aim to implement adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate aberration corrected images for whole brain reconstructions.
+
+%Bessel beam
+Further improvements in image quality may be achieved with beam shaping in the illumination arm, for example by implementing Bessel beam illumination\cite{Fahrbach2010,Planchon2011,Gao2014}.
+Using these self-reconstructing, non-diffractive beams the optical sectioning capability can be improved over an extended field of view.
 
@@
 	\centering
-		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
+		\caption[Components]{Overview of microscope components.\label{tab:optomechanics}}
 		\begin{tabular}{llll}
@@
 \acknowledgments
-The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for the their expertise in the conception and fabrication of the sample chamber.
-We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.
-Human Brain Project tutta la vita.
+The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for fabrication of the sample chamber.
+We further thank Marco De Pas from the electronic workshop for his expertise in the fabrication of the custom-made amplification electronics.
+We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.\\
+The research leading to these results has received funding from the European Union Seventh Framework Program (FP7\slash2007-2013) under grant agreements no.
+604102 (Human Brain Project) and n$\degree$ 284464 (LASERLAB-EUROPE).
+The research has also been supported by the Italian Ministry for Education, University and Research in the framework of the Flagship Project NanoMAX, by  ``Ente Cassa di Risparmio di Firenze" (private foundation).
+Research activities were also supported by Regione Toscana in the program POR-CreO 2007-2013 (Linea di interventi 1.5.a - 1.6 - Bando Unico R\&S 2012) under grant agreement (CUP) n$\degree$ 6408.30122011.026000201.
+
+\section*{Conflict of interest}
+M.v.H has a financial interest in Murmex, Distrio, Amsterdam the Netherlands.
 
@@
 
-\bibitem{Chung2013} K.
-Chung, J.
-Wallace, S.
-Y.
-Kim, S.
-Kalyanasundaram, A.
-S.
-Andalman, T.
-J.
-Davidson and K.
-Deisseroth, ``Structural and molecular interrogation of intact biological systems," \emph{Nature} \textbf{497}(7449), 332–33 (2013).
-
-\bibitem{Tomer2014} R. Tomer, L. Ye, B. Hsueh and K. Deisseroth, ``Advanced CLARITY for rapid and high-resolution imaging of intact tissues," \emph{nature protocols} \textbf{9}(7), 1682-1697 (2014).
-
-\bibitem{Kaufmann2012} A.
+%\bibitem{Kaufmann2012} A.
 Kaufmann, M.
@@
 Huisken, ``Multilayer mounting enables long-term imaging of zebrafish development in a light-sheet microscope," \emph{Development} \textbf{139}(17), 3242-3247 (2012).
-
-\bibitem{Pitrone2013} P.
+%
+%\bibitem{Pitrone2013} P.
 Pitrone, J.
@@
 Tomancak, ``OpenSPIM-an open access platform for light-sheet microscopy," \emph{arXiv} reprint arXiv:1302.1987, 3242-3247 (2013).
-
-\bibitem{Olarte2012} O.
+%
+%\bibitem{Olarte2012} O.
 E.
@@
 
-\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} 12(4), 227–229 (1987).
-
-\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} 63(1), 18–22 (2004).
-
 \bibitem{Silvestri2012} L.
@@
 
-\bibitem{castagna1997object} G. Castagna, \emph{``Object-Oriented Programming A Unified Foundation,"} Birkh{\"a}user, Boston (1997).
+\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} 12(4), 227–229 (1987).
 
-\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
+\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} 63(1), 18–22 (2004).
+
+\bibitem{Booth2001} M.
+J.
+Booth and T.
+Wilson, ``Refractive-index-mismatch induced aberrations in single-photon and two-photon microscopy and the use of aberration correction," \emph{J.
+Biomed.
+Opt.} 6(3), 266–272 (2001).
+
+%\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
 
@@
 
-%\bibitem{Frasconi2014} P. Frasconi, L. Silvestri, P. Soda, R. L. Cortini, F. S. Pavone and G. Iannello, ``" \emph{Bioinformatics} \textbf{30}(), i587-i593 (2014).
+\bibitem{Bria2012} A. Bria and G. Iannello,  ``TeraStitcher-A tool for fast automatic 3D-stitching of teravoxel-sized microscopy images,"  \emph{BMC bioinformatics} \textbf{13}(1), 316 (2012).
 
-\bibitem{Bria2012} A. Bria and G. Iannello,  ``TeraStitcher-A tool for fast automatic 3D-stitching of teravoxel-sized microscopy images,"  \emph{BMC bioinformatics} \textbf{13}(1), 316 (2012).
+\bibitem{Chung2013} K.
+Chung, J.
+Wallace, S.
+Y.
+Kim, S.
+Kalyanasundaram, A.
+S.
+Andalman, T.
+J.
+Davidson and K.
+Deisseroth, ``Structural and molecular interrogation of intact biological systems," \emph{Nature} \textbf{497}(7449), 332–33 (2013).
+
+\bibitem{Tomer2014} R. Tomer, L. Ye, B. Hsueh and K. Deisseroth, ``Advanced CLARITY for rapid and high-resolution imaging of intact tissues," \emph{nature protocols} \textbf{9}(7), 1682-1697 (2014).
 
@@
 C.
-Muellenbroich, L.
+M\"{u}llenbroich, L.
 Onofri, V.
@@
 Pavone, \emph{submitted}.
+
+\bibitem{Marx2014} V. Marx, ``Microscopy: seeing through tissue," \emph{Nat Meth} \textbf{11}(12), 1209–1214 (2014).
+
+\bibitem{Booth2007} M. J. Booth, ``Adaptive optics in microscopy," \emph{Transactions of the Royal Society A} \textbf{365}(1861), 2829-2843 (2007).
+
+\bibitem{Jorand2012} R.
+Jorand, G.
+Corre, J.
+Andilla, A.
+Maandhui, C.
+Frongia, V.
+Lobjois, B.
+Ducommun, and C.
+Lorenzo, ``Deep and Clear Optical Imaging of Thick Inhomogeneous Samples," \emph{PLoS ONE} \textbf{7}(4), (2012).
+
+\bibitem{Wang2014} K.
+Wang, D.
+E.
+Milkie, A.
+Saxena, P.
+Engerer, T.
+Misgeld, M.
+E.
+Bronner, J.
+Mumm, and E.
+Betzig, ``Rapid adaptive optical recovery of optimal resolution over large volumes," \emph{nature methods} 11(6), 625–628, (2014).
+
+\bibitem{Frasconi2014} P.
+Frasconi, L.
+Silvestri, P.
+Soda, R.
+L.
+Cortini, F.
+S.
+Pavone and G.
+Iannello, ``Large-scale automated identification of mouse brain cells in confocal light sheet microscopy images," \emph{Bioinformatics} \textbf{30}(17), i587-i593 (2014).
+
+\bibitem {Fahrbach2010} F. Fahrbach and A. Rohrbach, ``A line scanned light-sheet microscope with phase shaped self-reconstructing beams," \emph{Optics Express} \textbf{18}(23), 780–785 (2010).
+
+\bibitem {Planchon2011} T.
+Planchon, L.
+Gao, D.
+Milkie, M.
+Davidson, J.
+Galbraith, C.
+Galbraith, and E.
+Betzig, ``Rapid three-dimensional isotropic imaging of living cells using Bessel beam plane illumination," \emph{Nature Methods} \textbf{8}(5), 417–423 (2011).
+
+\bibitem {Gao2014} L.
+Gao, L.
+Shao, B.-C.
+Chen, and E.
+Betzig, ``3D live fluorescence imaging of cellular dynamics using Bessel beam plane illumination microscopy," \emph{Nature Protocols} \textbf{9}(5), 1083–1101 (2014).
+
+\bibitem{castagna1997object} G. Castagna, \emph{``Object-Oriented Programming A Unified Foundation,"} Birkh{\"a}user, Boston (1997).
 
@@
 After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths.
-The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
+The SNR was calculated according to $\text{SNR} = \nicefrac{(y_0 + A)}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
 
 \subsubsection{Sample preparation for whole brain imaging}
-
-\subsection{Software management}
-
-\subsubsection{General design}
-
-The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software written in the LabVIEW language (National Instruments, Austin, US).
-Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, stringent software design is a primary concern.
-The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance.
-This means, the apparatus should be able to deal with many independent hardware components, and with several data streams (see below).
-Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.
-Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of data.
-
-%\begin{itemize}
-%\item{\emph{User-friendliness}.
-The light-sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
-%\item{\emph{Working in a distributed environment}.
-The apparatus should deal with many independent hardware components, and with several data streams (see below).
-Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
-%\item{\emph{Robustness and ease of maintenance}.
-Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
-Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
-%\item{\emph{Reusability and scalability}.
-When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time.
-Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
-%\end{itemize}
-
-%Our microscope management software has been written in LabVIEW (), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. 
-An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
-This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
-Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
-%The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation.
-In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
-Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
+Mouse brains were processed using the CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
+Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS.
+We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at 4°C for 3 days.
+Afterwards, we degassed the samples and increased their temperature to 37 °C to initiate polymerization.
+The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at 37 °C through gentle shaking.
+To perform electrophoretic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber.
+The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at 37 °C for several days.
+After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at 37 °C for 2 days to remove the clearing solution.
+As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at 37°C while gently shaking.
+The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.
 
@@
 
-\subsubsection{Microscope software}
-Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component (see supplementary information \ref{sec:murmex}).
-Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
-Beyond hardware-related software, two additional Murmex components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.
+\subsection{Formulas}
 
-The Stack component is used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
-Stacks are collected by continuously moving the sample along $z$ while keeping the camera acquiring in free run.
-The translation speed is calculated such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
-The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
-The Camera component must write data to disk with perfect synchronisation, otherwise the nominal $z$ position of each frame is no more coincident with the real $z$ position of the plane imaged.
-For this reason, we set the process executing the Camera code to be of highest priority.
-Additionally, the Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
-%The Stack component also specify the name and the path of the \emph{.cxd} file.
-
-The Tomo component is a high level component which coordinates the acquisition of adjacent, parallel, partially-overlapping stacks. %It exchanges messages with the Stack and the Stages components.
-The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a text file with the coordinates of individual stacks to be collected.
-The Tomo component informs the experimenter via email when the acquisition is terminated either cleanly or through errors.
-
-All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
-Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
-
-\subsection{Formulas}
-\begin{table}[t!]
-	\centering
-		\caption[Main formulas]{Overview of the main formulas related to light-sheet microscopy.
 In the table, $f_{\text{TL}}^{\text{design}}$ is the focal length of the tube lens for which the objective has been designed (200 mm for Leica and Nikon, 180 mm for Olympus and 165 mm for Zeiss), $f_{\text{TL}}^{\text{real}}$ the focal length of the tube lens actually employed, $\text{M}$ the nominal magnification of the objective, $n$ the refractive index of the immersion medium, $\lambda_0$ the wavelength in vacuum, $\lambda$ the wavelength in the medium, $w$ the $1/e^2$ radius of the Gaussian beam at the objective back focal plane, FN the field number of the objective, $p$ the physical pixel size, $r_{\text{chip}}$ the size of the camera chip, $t_{\text{shutter}}$ the pace of the rolling shutter (i.e.
@@
 The subscripts $_i$ and $_d$ refers to illumination and detection, respectively.
-\label{tab:resolution}}
+
+\begin{table}[t!]
+	\centering
+		\caption[Main formulas]{Overview of the main formulas related to light-sheet microscopy. \label{tab:resolution}}
 		\begin{tabular}{lrcl}

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript1.1_Ludo.tex
commit

--- 2015-01-20 latex-style-files-spie-manuscript/manuscript1.1_Ludo.tex
@@
 The translation speed is such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
-The stack component also specify the name of the file where data are saved.
+The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack.
+The name of this file and the path to it is specified by the Stack component.
 
@@
 Since the clearing procedure with CLARITY produces a linear expansion of about $1.2\times$ \cite{Costantini}, the volume of a clarified mouse brain can be estimated as $\simeq 0.9$ $\text{cm}^3$, while that of a parallelepiped encompassing the sample is expanded to $\simeq 1.6$ $\text{cm}^3$.
-Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.26\times0.26\times2$ $\mu\text{m}^3$.
-This means that a cleared mouse brain will be represented with about 6 TeraVoxels, while a parallelepiped encompassing the brain will result in 10.8 TeraVoxels.
-Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 12 TB for the whole brain "alone" and 21.6 TB for the parallelepiped (see Table XXXX).
+Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$.
+This means that a cleared mouse brain will be represented with about 7.4 TeraVoxels, while a parallelepiped encompassing the brain will result in 13.3 TeraVoxels.
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 14.8 TB for the whole brain "alone" and 26.6 TB for the parallelepiped (see Table XXXX).
+However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching.
+This redundancy expands the size of raw data to 18.3 TB and 32.8 TB, respectively.
 
@@
 We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable.
-The NAS operates in a safer data modality (RAID 5) with 32 TB of useful disk space.
+The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space.
 The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main italian supercomputing center).
+The data flow scheme is summarized in Figure \ref{fig:DataFlow}.
 
-The camera used in our light sheet microscope has a dedicated work station with a CameraLink card and 10.9TB of SSD space in RAID 0 configuration.
-This finite storage capacity is further expanded by a network-attached storage (NAS) of 32.4TB (Figure\ref{fig:DataFlow}).
-The SSDs and the NAS are connected via a 10Gb bandwidth connection using a 10Gb switch and a 10Gb optical fibre connects our lab to the supercomputing centre CINECA in Bologna.
-Mention PICO system/storage analysis capacity there?
-Mention graphical processing unit and cores/processors/RAM of work station?
+While transferring the data from the SSD to the NAS, we also perform a file conversion from the proprietary Hamamatsu format to a more manageable one.
+We chose the TIFF format among the others because it permits to store 3D image with lossless compression in a single file.
+Furthermore, it is a flexible and platform-independent format supported by numerous image processing applications.
+We thus developed a conversion module that leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library.
+The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
+Since the output of the Hamamatsu camera may exceed tens of Gbytes, the image in proprietary format is read slice by slice to minimize memory requirements.
+The module has also an option to downsample the image on save the input image at full or reduced resolution, in order to adapt to storage availability.
+Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling as usual.
+This kind of downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude.
+Thus the parallelepid volume cointaining the whole mouse brain can be represented using about 2-3 TB of disk space.
 
-With the size of a single image of 8MB and a stack made up of say 3900 frames a single stack amounts to 30.4GB of disc space (see Table\ref{tab:dataproduction} for an overview of the values).
-Based on a frame rate of 44Hz each stack takes approximately 1.5 minutes to acquire and the SSD RAID fills up with a data writing rate of 1.2TB/h.
-If no further measures are taken the SSD RAID of 10.9TB would be filled up in just 9h.
-A custom compression script written in Python serves the triple purpose of translating the images from the proprietary Hamamatsu file format to 3D tif, to transfer the data from the SSD RAID to a network attached storage (NAS) and to reduce the raw data size by first, digitally downsampling the image resolution and second, applying a lossless compression to the tif images.
-This leads to a overall reduction of data size by a factor of ten, each stack now taking up only 3GB of disc space, albeit at a much slower conversion rate (-0.7TB/h) than the rate at which data is written to the SSD thus representing the most serious bottleneck to our data production pipeline.
-The SSD RAID fills up at a rate of 0.5TB/h which means the total acquisition time is limited to less than 24h and a total tomo size of just over 25TB.
-After this time acquisition has to be halted until the slower conversion process has caught up and freed the SSD RAID before data acquisition can start again.
-A whole mouse brain tomography would take 3 days of uninterrupted measuring yet with the necessary breaks for data transfer this time is easily doubled to tripled.
+Although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
+The Camera component flushes data on the SSD with a rate $R_{data}$ dependent on frame rate $R_{frame}$ and on the image size:
+\begin{equation}
+R_{data} [\text{Bytes}] = 2\times R_{frame} \times \#_{pixels}\,,
+\end{equation}
+where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{volume} = 0.5 R_{data} \times \text{Voxel size}$.
+
+With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
+The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h.
+Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB.
+Taking into accont the 10\% linear superposition between adjacent stacks, the maximum size of a sample that can be imaged in a single session is about 1.2 $\text{cm}^3$, which is larger than a cleared mouse brain, but smaller than the estimate size of a parallelepiped volume encompassing the entire volume.
+Therefore imaging should be limited to the portion of the volume where the brain is with rational selection of stacks.
+Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
 

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo_Ludo.tex
commit

--- 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo.tex
@@
 
-%\bibitem{Frasconi2014} P. Frasconi, L. Silvestri, P. Soda, R. L. Cortini, F. S. Pavone and G. Iannello, ``" \emph{Bioinformatics} \textbf{30}(), i587-i593 (2014).
+\bibitem{Frasconi2014} P.
+Frasconi, L.
+Silvestri, P.
+Soda, R.
+L.
+Cortini, F.
+S.
+Pavone and G.
+Iannello, "Large-scale automated identification of mouse brain cells in confocal light sheet microscopy images" \emph{Bioinformatics} \textbf{30}(17), i587-i593 (2014).
 
@@
 \subsubsection{Sample preparation for whole brain imaging}
+Mouse brains were processed using the CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
+Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS.
+We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at 4°C for 3 days.
+Afterwards, we degassed the samples and increased their temperature to 37 °C to initiate polymerization.
+The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at 37 °C through gentle shaking.
+To perform electroforetic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber.
+The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at 37 °C for several days.
+After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at 37 °C for 2 days to remove the clearing solution.
+As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at 37°C while gently shaking.
+The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.
 

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
commit

--- 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
@@
 \author{M.
-Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
+Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{a} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S.
 Pavone,\supscr{a,b,c,d}  }
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light-sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging}
+\keywords{Light-sheet microscopy, whole brain, data management, software management, imaging pipeline, high-throughput imaging}
 
@@
 
-The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM).
-With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition.
+The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}.
+With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal features in time scales which are no longer the bottle neck of high-throughput acquisition.
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
@@
 Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
-Those challenges include fast cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, the storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces.
+Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces.
 The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
@@
 %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community.
-We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of tens of terabytes.
+We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of several terabytes.
 To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.
@@
 \subsection{Laser unit}		
-The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised cw lasers for fluorescence excitation (Fig.
+The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised, continuous-wave lasers for fluorescence excitation (Fig.
 \ref{fig:excitation},A).
@@
 A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
-After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).
 
@@
 The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber.
-A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent.
+A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the clearing agent.
 A guide to align objectives to a common focus can be found in the supplementary information.
@@
 Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
-The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm).
+The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm, working distance 8mm).
 %To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
-A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels.
+A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels.
 %In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
 The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$.
-With a 200mm tube lens the field of view (FOV) in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).
+With a 200mm tube lens the field of view (FOV) in the sample is $(480\micro m)^2$ (see also Table \ref{tab:resolution} for relevant formulas).
 
@@
 With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms.
-Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
+For instance, setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
 This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective.
-With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(\#_{\text{horiz.
+With the given values of line exposure and line read out time, the camera acquires images at a frame rate of  $R_{\text{frame}} = \nicefrac{1}{(\#_{\text{horiz.
 lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.
 
-The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for the DAQ board which was operated as slave.
+The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as an output trigger for the DAQ board which was operated as slave.
 The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation).
@@
 \ref{fig:frame2},B).
-All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
+Connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders.
 In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig.
 \ref{fig:frame2},C).
-The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.
-To fill the entire volume of the sample chamber approximately 250ml clearing solution are needed.
-A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig.
+The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $\approx 1.45$\cite{Costantini}.
+To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed.
+A motorized x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig.
 \ref{fig:frame2},D).
@@
 \begin{equation}
-\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
+\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}},
 \end{equation}
-
 $\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
@@
 \begin{equation}
-w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
+w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w},
 \end{equation}
-
 where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index).
@@
 \begin{equation}
-\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
+\text{FWHM}_{\text{axial}} \simeq 1.177 w_0.
 \end{equation}
-
 The thickness of the light-sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam.
@@
 \begin{equation}
-b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
+b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}.
 \end{equation}
-
 The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
-In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$ (assuming $\lambda_0 = 0.5 \micro m$).
 An overview of the relevant formulas concerning the optical properties of a light-sheet microscope is given in Table \ref{tab:resolution}.
@@
 From the same data the average FWHM of the Gaussian excitation line over the FOV of the camera was calculated as $(8.60\pm0.67)\micro m$ (n= 14).
+The disagreement with the theoretical value of $5.13 \micro m$ is likely attributed to the refractive index mismatch introduced in the excitation arm by the protective coverslip and by the optical path inside a medium with a refractive index different from air, both causing spherical aberrations\cite{Booth2001}.
 
@@
 The lateral and axial FWHMs were $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively, averaged through stack depths and confocal slit widths.
-The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four while the experimentally determined axial FWHM was 1.6x larger than the theoretically calculated value of $5.13 \micro m$.
-The discrepancies, most notably in the lateral direction, are likely caused by aberrations introduced by the gel embedding the fluorescent beads.
+The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four.
+The discrepancy is likely caused by higher order aberrations introduced by the gel embedding the fluorescent beads exacerbated by the high NA of our detection objective\cite{Schwertner2004,Schwertner2007}.
 
@@
 Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
+The Murmex software development kit (see supplementary information \ref{sec:murmex}) was used to operated the software efficiently and synchronously on different computers.
 
@@
 \subsection{Software organisation}
-Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component (see supplementary information \ref{sec:murmex}).
+Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own software component (see supplementary information \ref{sec:murmex}).
 Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
-Beyond hardware-related software, two additional Murmex components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.
+Beyond hardware-related software, two additional software components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.
 
@@
 \section{Data Management}
+
 The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
@@
 Thus, although file conversion drastically reduces data size, in the current implementation it is slower than data production.
-The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
+The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size: $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
 where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.
 
-With a standard image size of $2048\times 2048$ pixels, and $R_{\text{frame}}=44$ Hz, data are produced at a rate $R_{\text{data}}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2\times 10^7$ $\micro\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
-The conversion module can empty the SSD with an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h.
-Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB.
+With a standard image size of $2048 \times 2048$ pixels, and $R_{\text{frame}}=50$ Hz, data are produced at a rate $R_{\text{data}}=400$ MB/s $\approx 1.37$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2.3 \times 10^7$ $\micro\text{m}^3/s$ $\approx 0.08$ $\text{cm}^3$/h.
+The conversion module can empty the SSD with an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.67 TB/h.
+Imaging sessions should thus be shorter than 16.3 hours: this limits the maximum amount of raw data being acquired continuously to approximately 22.3 TB.
 This is well above the disk space needed to image the parallelepiped volume encompassing a whole mouse brain.
@@
 SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
-Different colours (red, yellow and green) indicate the time-sensitivity (higher to lower) of each data movement.
+Different colours (red, yellow and green) indicate the time-criticality (higher to lower) of each data movement.
 (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
@@
 		Voxel size																								& $0.234 \times 0.234 \times 2$	& $\micro\text{m}^3$ 	\\
-		Frame rate																								& 44														& Hz								\\
+		Frame rate																								& 50														& Hz								\\
 		Frame size																								& $2048 \times 2048$ 						& pixels						\\
 		Frame disk size																						& 8									 						& MB								\\
-		Data production rate																			& 1.2								 						& TB/h 							\\
+		Data production rate																			& 1.37							 						& TB/h 							\\
 		Data conversion rate																			& 0.7								 						& TB/h 							\\
-		Net SSD filling rate																			& 0.5								 						& TB/h 							\\
+		Net SSD filling rate																			& 0.67							 						& TB/h 							\\
 		SSD RAID size																							& 10.9							 						& TB								\\
-		Max acquisition time to fill up SSDs											& 21.8							 						& h									\\
-		Max raw data size that can be acquired continuously				& 25.4							 						& TB								\\
-		Max volume that can be imaged 														& 1.24							 						& $\text{cm}^3$ 		\\
+		Max acquisition time to fill up SSDs											& 16.3							 						& h									\\
+		Max raw data size that can be acquired continuously				& 22.3							 						& TB								\\
+		Max volume that can be imaged 														& 1.04							 						& $\text{cm}^3$ 		\\
 		(considering 10\% superposition between adjacent stacks)	&										 						&										\\
@@
 \ref{fig:LSMdata}B).
-The resolution and contrast of the images allow distinguish axonal tracts (Fig.
+The resolution and contrast of the images allow to distinguish axonal tracts (Fig.
 \ref{fig:LSMdata}C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labeled.
@@
 \ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain.
-Such whole-brain dataset can be used to localize cellular distribution in three-dimensions using automatic cell-detection software \cite{Frasconi2014}.
+Such whole-brain datasets can be used to localize cell distributions in 3D using automatic cell-detection software \cite{Frasconi2014}.
 
-\section{Conclusion}
-
-%essential features of a good discussion:
-%• Try to present the principles, factual relationships and generalisations shown by the results. Discuss dont recapitulate.
-%• Noting strengths and limitations.
-Point out nay exceptions or any lack of correlation and define unsettled points.
-Never take the high-risk alternative of trying to cover up or fudge data that do not quite fit.
-%• Show how your results and interpretations agree (or contrast) with previously published work.
-%• Significance of the work: ..so what?
-Don’t be shy, discuss the theoretical implimication of your work, as well as any possible practical applications.
-The discussion should end with a short summary or conclusion regarding the significance of the work.
-Leave with a bang not a whimper.
-%• State your conclusions as clearly as possible.
-%• Summarise your evidence for each conclusion. Never assume anything.
-%• Introduction and discussion function as a pair: the intro should have posed one or more questions.
-The discussion should indicate what the findings say about the answers.
-Be sure the discussion answers what the intro asked.
-%• Reverse funnel structure: first restate the main findings, then discuss how they relate to findings in previous research, then note implications and applications, and then identify unanswered questions well suited for future research.
+\section{Discussion and conclusion}
 
 Light sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale.
-The impact of this measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks.
+This measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks.
 Here we have presented a complete and detailed framework for whole mouse brain imaging.
 Starting with a full description of our double-sided light sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation.
-The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods.
+The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved andF processed necessitating the concurrent development of novel computational interface and analysis methods.
 Here we have presented a comprehensive, robust and fully automated pipeline of data management starting from the streaming of raw images up to the stitching of 3D data sets.
@@
 Crucially for the high-throughput imaging of large samples that we aim for the protocol, however, is also fast, easy and cheap.
-We therefore development a versatile, simple, rapid and inexpensive clearing method described elsewhere\cite{Costantini} which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies.
+We therefore developed a versatile, simple, rapid and inexpensive clearing method described elsewhere\cite{Costantini} which in combination with CLARITY allows for the optical clearing of entire mouse brains or portions of human tissue.
 
@@
 A complete correction of system-induced aberrations, however, requires the ability to also correct for residual spherical aberration and higher-order aberrations introduced by the sample mount, immersion medium and slight misalignments of the optical system.
-Additionally aberrations introduced by the sample itself degrade image quality.
+Of course, aberrations introduced by the sample itself degrade image quality and it is those aberrations that are most difficult to correct in at run-time due to their modal complexity, large amplitude and high spatial variability\cite{Wang2014}.
+
 Additionally another problem inherent to light sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths.
@@
 The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data.
-We have mounted the camera on a separate breadboard which leaves us with a lot of free infinity-corrected space in the detection path.
-In a future paper we aim to implement adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate aberration corrected images for whole brain reconstructions.
+We have mounted the camera on a separate breadboard which leaves us with a lot of free, infinity-corrected space in the detection path.
+The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole brain reconstructions will be considered in the future.
 
@@
 Using these self-reconstructing, non-diffractive beams the optical sectioning capability can be improved over an extended field of view.
+
+The streamlining of high-throughput imaging of entire mouse brains, starting from the live animal up to quantifiable data sets, requires tight integration of all aspects of the work flow.
+Even if the brains we image are transparent, their large size means that even comparatively small heterogenities in the refractive index matching sum up to large optical path differences and therefore strong aberrations at large imaging depth.
+The microscope used for whole brain imaging needs to be developed and adapted bearing those imaging circumstances in mind and sample preparation methods, imaging technology and data management schemes have to work as a unit in order to deliver on the highly anticipated, quantifiable data sets of whole brain neuronal projections.
 
@@
 We further thank Marco De Pas from the electronic workshop for his expertise in the fabrication of the custom-made amplification electronics.
-We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.\\
+We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting our data.\\
 The research leading to these results has received funding from the European Union Seventh Framework Program (FP7\slash2007-2013) under grant agreements no.
@@
 \section*{Conflict of interest}
-M.v.H has a financial interest in Murmex, Distrio, Amsterdam the Netherlands.
+M.v.H has a financial interest in Murmex by Distrio, Amsterdam the Netherlands.
 
@@
 \begin{thebibliography}{0}
+
+\bibitem{Huisken2004} J.
+Huisken, J.
+Swoger, F.
+Bene, J.
+Wittbrodt, and E.
+Stelzer, ``Optical Sectioning Deep Inside Live Embryos by Selective Plane Illumination Microscopy," \emph{Science} \textbf{305}(5686), 1007–1009 (2004).
+
+\bibitem{Keller2012} P. Keller and H.-U. Dodt, ``Light sheet microscopy of living or cleared specimens," \emph{Curr. Opin. Neurobiol.} \textbf{22}(1), 138–43 (2012).
+
+\bibitem{Dodt2007} H.-U.
+Dodt, U.
+Leischner, A.
+Schierloh, N.
+J\"{a}hrling, C.
+Mauch, K.
+Deininger, J.
+Deussing, M.
+Eder, W.
+Zieglg\"{a}nsberger, et al., ``Ultramicroscopy: three-dimensional visualization of neuronal networks in the whole mouse brain," \emph{Nat.
+Methods} \textbf{4}(4), 331–336 (2007).
 
@@
 Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light-sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
+
+\bibitem{Costantini} I.
+Costantini, J.-P.
+Ghobril, A.
+P.
+Di Giovanna, A.
+L.
+Allegra Mascaro, L.
+Silvestri, M.
+C.
+M\"{u}llenbroich, L.
+Onofri, V.
+Conti, F.
+Vanzi, L.
+Sacconi, R.
+Guerrini, H.
+Markram, G.
+Iannello, and F.
+S.
+Pavone, \emph{submitted}.
 
@@
 
-\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} 12(4), 227–229 (1987).
-
-\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} 63(1), 18–22 (2004).
-
 \bibitem{Booth2001} M.
@@
 Opt.} 6(3), 266–272 (2001).
+
+\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} 12(4), 227–229 (1987).
+
+\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} 63(1), 18–22 (2004).
+
+\bibitem{Schwertner2004} M.
+Schwertner, M.
+J.
+Booth, and T.
+Wilson, ``Characterizing specimen induced aberrations for high NA adaptive optical microscopy," \emph{Optics express} \textbf{12}(26), 6540–6552 (2004).
+
+\bibitem{Schwertner2007} M. Schwertner, M. J. Booth, and T. Wilson, ``Specimen‐induced distortions in light microscopy," \emph{Journal of microscopy} \textbf{228}(1) 97-102 (2007).
 
@@
 \bibitem{Tomer2014} R. Tomer, L. Ye, B. Hsueh and K. Deisseroth, ``Advanced CLARITY for rapid and high-resolution imaging of intact tissues," \emph{nature protocols} \textbf{9}(7), 1682-1697 (2014).
-
-\bibitem{Costantini} I.
-Costantini, J.-P.
-Ghobril, A.
-P.
-Di Giovanna, A.
-L.
-Allegra Mascaro, L.
-Silvestri, M.
-C.
-M\"{u}llenbroich, L.
-Onofri, V.
-Conti, F.
-Vanzi, L.
-Sacconi, R.
-Guerrini, H.
-Markram, G.
-Iannello, and F.
-S.
-Pavone, \emph{submitted}.
 
@@
 
-\subsection{Methods}
-
-\subsubsection{Sample preparation for optical characterisation}
-The fluorescent beads (CP01F, Bang Laboratories, $0.51 \micro m$ diameter) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS).
-The low melting point agarose (A-4018, Sigma-Aldrich) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
+\subsection{Sample preparation for optical characterisation}
+The fluorescent beads (CP01F, Bang Laboratories, $0.51 \micro m$ diameter) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 63\%TDE in PBS).
+The low melting point agarose (A-4018, Sigma-Aldrich) was dissolved at $\approx 40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
 The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}.
@@
 
-\subsubsection{Sample preparation for whole brain imaging}
-Mouse brains were processed using the CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
+\subsection{Sample preparation for whole brain imaging}
+Mouse brains were processed using a modified CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
 Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS.
-We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at 4°C for 3 days.
-Afterwards, we degassed the samples and increased their temperature to 37 °C to initiate polymerization.
-The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at 37 °C through gentle shaking.
+We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at $4 \degree$ C for 3 days.
+Afterwards, we degassed the samples and increased their temperature to $37 \degree$ C to initiate polymerization.
+The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at $37 \degree $ C through gentle shaking.
 To perform electrophoretic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber.
-The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at 37 °C for several days.
-After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at 37 °C for 2 days to remove the clearing solution.
-As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at 37°C while gently shaking.
+The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at $37 \degree$ C for several days.
+After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at $37 \degree$ C for 2 days to remove the clearing solution.
+As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at $37 \degree$ C while gently shaking.
 The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.
 
-\subsubsection{Murmex}
+\subsection{Murmex}
 \label{sec:murmex}

### 2015-03-25 latex-style-files-spie-manuscript/manuscript_submission.tex
bob

--- 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
@@
 
-\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
+\affiliation{\supscrsm{a}European Laboratory for Non-Linear Spectroscopy (LENS), University of Florence, Italy\\
 \supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
@@
 \supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
-%\supscrsm{f}Distrio, Amsterdam, The Netherlands
 }
@@
 The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution.
-We have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains.
+To this end, we have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains.
 Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software.
@@
 The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage.
-To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets.
+To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from streaming of raw images up to stitching of 3D data sets.
 The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains.
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light-sheet microscopy, whole brain, data management, software management, imaging pipeline, high-throughput imaging}
+\keywords{Light-sheet microscopy, whole brain imaging, data management, software management, imaging pipeline, high-throughput imaging}
 
 %>>>> Include contact information for corresponding author
-{\noindent \footnotesize{\bf Address all correspondence to}: First author, University Name, Faculty Group, Department, Street Address, City, Country, Postal Code; Tel: +1 555-555-5555; Fax: +1 555-555-5556; E-mail:  \linkable{myemail@university.edu} }
+{\noindent \footnotesize{\bf Address all correspondence to}: Francesco S.
+Pavone, LENS, University of Florence, Via Nello Carrara 1, 50019 Sesto Fiorentino (FI), Italy; Tel: +39 055 457 2480; E-mail:  \linkable{francesco.pavone@unifi.it} }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\begin{spacing}{2}   % use double spacing for rest of manuscript
+\begin{spacing}{2}   % use double spacing for rest of manuscript
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}%funnel shape
+\section{Introduction}
 \label{sect:intro}
@@
 The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}.
-With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal features in time scales which are no longer the bottle neck of high-throughput acquisition.
+With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic and axonal features in time scales which are no longer the bottle neck of high-throughput acquisition.
 In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}.
@@
 Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks.
-Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces.
-The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation.
-On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent.
+Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces\cite{Freeman2014,Burns2014}.
+The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated, scalable post-processing, for example, to do blood vessel segmentation or cell counting\cite{Frasconi2014}.
+On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent\cite{Chung2013,Tomer2014}.
 Therefore technological advances in LSFM need to be matched by novel development in the area of information- and biotechnology.
 
-Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains.
+Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of clarified and structurally intact mouse brains.
 The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples.
-After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days.
+After briefly introducing the optical setup we explain how to prepare and mount the samples for stable 3D imaging for several days.
 In addition, a full description of the control hardware and software is presented.
 The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components.
-%The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community.
-We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of several terabytes.
-To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.
+We further give a systematic and robust approach to handle and store light-sheet microscopy data of several terabytes.
+To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching of large 3D data sets.
 The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.
-
-%\begin{figure}
-   %\begin{center}
-   %\begin{tabular}{c}
-   %\includegraphics[width=\textwidth]{PanelSampel.eps}
-   %\end{tabular}
-   %\end{center}
-   %\caption{\label{fig:Panel0} (A) Schematic of light-sheet microscopy.
-The sample is illuminated with a planar light-sheet (blue) perpendicular to fluorescence detection (green).
-(B) Mounting of a clarified, fluorescently labelled brain.
-The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.}
-   %\end{figure}
 
@@
    \end{center}
-   \caption{\label{fig:excitation} (A) Topview of the excitation path.
+   \caption{\label{fig:excitation} (A) Schematic of the light path.
 The galvo scanners are mounted above periscopes.
@@
 \subsection{Laser unit}		
-The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised, continuous-wave lasers for fluorescence excitation (Fig.
+The custom-made confocal light-sheet microscope is equipped with five linearly polarised, continuous-wave lasers for fluorescence excitation (Fig.
 \ref{fig:excitation},A).
-The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components).
-The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series).
+The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of microscope components).
+The beam from each laser is first collimated and expanded with a telescope made of singlet lenses (f140, f200) and then combined into a common path with a mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series).
+From here on all lenses are achromatic doublets coated for the visible spectrum.
 An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter and intensity modulator.
-%which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines.
-The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity.
 Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output.
 The zero order light is blocked by an iris.
+A 1:1 telescope (f150,f150) is used to re-collimate the beam after the AOTF.
 An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
-%The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
-First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
 A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).
@@
 The beam diameter is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo).
-Both galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.
+Both galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages (Fig.
+\ref{fig:excitation},B).
 
 Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).
+The focal lengths of the doublets making up the telescope have been chosen for space considerations and to achieve a $1/e^2$ beam radius of 0.73mm at the back focal plane resulting in an effective NA of 0.025 (see also section \ref{sec:characterisation}).
 The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
@@
 This generates incoherent illumination resulting in fewer artefacts.
-%cite{StelzerNatMeth2014}.
-Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.
+Additionally each line in the specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.
 
@@
 
-%In its simplest form, the fluorescence detection unit of a light-sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector.
 Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
 The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm, working distance 8mm).
-%To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
 A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels.
-%In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other.
 The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$.
-With a 200mm tube lens the field of view (FOV) in the sample is $(480\micro m)^2$ (see also Table \ref{tab:resolution} for relevant formulas).
+With a 200mm tube lens the field of view (FOV) in the sample is $(480\micro m)^2$ (see also Table \ref{tab:resolution} in the supplementary information for relevant formulas).
 
-In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}.
+In the camera's rolling shutter acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}.
 With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms.
-For instance, setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
+Setting the line exposure time to $t_{\text{exp}}=0.3ms$, for instance, results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time.
 This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective.
-With the given values of line exposure and line read out time, the camera acquires images at a frame rate of  $R_{\text{frame}} = \nicefrac{1}{(\#_{\text{horiz.
+With the given values of line exposure and line read out time, the camera acquires images at a full-frame rate of  $R_{\text{frame}} = \nicefrac{1}{(\#_{\text{horiz.
 lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.
 
-The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as an output trigger for the DAQ board which was operated as slave.
-The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation).
-%Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast.
-The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.
+The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as an output trigger for a DAQ board (NI PCIe-6353, National Instruments) which was operated as slave.
+The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection (see also section \ref{sec:timing} on synchronisation).
 
@@
 \label{sec:mounting}
-%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering.
-Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices.
-Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque.
-In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed.
-These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
-%
-%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
-A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
-Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap.
-Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies.
-With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.
 
@@
 We designed a cubic water-tight sample chamber (Fig.
-\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently-labelled mouse brains.
+\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently labelled mouse brains.
 The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig.
@@
 \ref{fig:frame2},C).
-The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $\approx 1.45$\cite{Costantini}.
+The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $n \approx 1.45$\cite{Costantini}.
 To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed.
@@
 To elucidate neuronal projections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation.
-%While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light-sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes.
 The problem of sample mounting in a light-sheet microscope arises from the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample.
-%Most commonly the vertical direction is chosen.
-Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.
+Stable mounting is hereby a key concern as a whole-brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.
 
-For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Fig.
+For the acquisition of whole-brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Fig.
 \ref{fig:frame2},E).
@@
 \subsection{Optical characterisation}
-
+\label{sec:characterisation}
 \subsubsection{Theoretical considerations}
 
-The optical properties of a microscope can be summarised by the point-spread function (PSF), which is the image of a point source in object space.
-In particular, the radial (i.e.
+The optical properties of a microscope can be quantified by the point-spread function (PSF), which is the image of a point source in object space.
+The radial (i.e.
 perpendicular to the detection axis) and axial (i.e.
-parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (see Fig.
+parallel to the detection axis) resolution of the microscope are most commonly described by the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (Fig.
 \ref{fig:origin},A).
@@
 $\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
-The axial resolution is dominated by the thickness of the light-sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective.
-If Gaussian beams are used for illumination, the thickness of the light-sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
+The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective.
+If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}.
 The radius of the beam waist is given by:
@@
 \end{equation}
-The thickness of the light-sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam.
+The thickness of the light sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam.
 The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{origin.eps}
+   \includegraphics[width=\textwidth]{frame3.eps}
    \end{tabular}
@@
    \caption{\label{fig:origin} Optical characterisation.
-(A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian.
-(B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged.
-(C) The signal to noise ratio.}
+(A) Exemplary lateral and axial intensity profiles of nanometric beads and fits to Gaussian curves.
+(B) FWHM of the Gaussian fits with confocal slit width.
+Each data point is the average of 10 bead profiles.
+(C) Signal to noise ratio (SNR) as a function of slit width.}
 \end{figure}
@@
 
-For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories).
+For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories) were acquired.
 The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig.
@@
 The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance.
-This means, the apparatus should be able to deal with many independent hardware components, and with several data streams (see below).
+This means, the apparatus should be able to deal with many independent hardware components and with several data streams (see below).
 Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.
-Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of data.
+Any kind of hardware failure, from timing delays to complete system crash, must be automatically handled to avoid loss of data.
 
-%\begin{itemize}
-%\item{\emph{User-friendliness}.
-The light-sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment.
-The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
-%\item{\emph{Working in a distributed environment}.
-The apparatus should deal with many independent hardware components, and with several data streams (see below).
-Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
-%\item{\emph{Robustness and ease of maintenance}.
-Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data.
-Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
-%\item{\emph{Reusability and scalability}.
-When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time.
-Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
-%\end{itemize}
-
-%Our microscope management software has been written in LabVIEW (), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. 
-An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules.
+An object-oriented programming framework \cite{castagna1997object} has been used for software development, dividing the entire project into well-defined self-contained modules.
 This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability.
-Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
-%The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation.
-In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
-Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
-The Murmex software development kit (see supplementary information \ref{sec:murmex}) was used to operated the software efficiently and synchronously on different computers.
+Code was stored on GitHub (www.github.org) to help multiple users developing software simultaneously.
+The Murmex software development kit (see supplementary information \ref{sec:murmex}) was used to operate the software efficiently and synchronously on different computers.
 
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{connectivity.eps}
+   \includegraphics[width=\textwidth]{frame4.eps}
    \end{tabular}
@@
 
-A schematic overview of the hardware architecture of our light-sheet microscope is shown in Fig.
+A schematic overview of the hardware architecture of our LSFM is shown in Fig.
 \ref{fig:connectivity}.
-One personal computer (Precision T5600, Dell, Round Rock, USA, see also Table \ref{tab:optomechanics}) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section).
-Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).
+One personal computer (Precision T5600, Dell, see also Table \ref{tab:optomechanics}) controlled all the remote hardware components with the exception of the camera, which was controlled by a second, dedicated computer (Precision T7500, Dell) to handle and manage the enormous streams of data produced (see also section \ref{sec:dataflow}).
+Various instrumentations were addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by the DAQ board.
 
-Synchronization of the camera rolling shutter to the scanning of the light-sheet is achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
-In particular, the HSYNC signal from the camera is used, providing a true-type-logic (TTL) pulse every time the rolling shutter steps from one line to the next one.
-This trigger signal is used as a clock by the DAQ board, so that the line producing the light-sheet moves step by step with the rolling shutter.
-The same HSYNC signal is used to trigger the DAQ digital signal sent to the electro-optic laser modulator.
-In this case, since at each position of the scanning line the modulator should go trough at least two states (vertical polarization and horizontal polarization), HSYNC is used as a trigger while the clock used is the (much faster) internal clock of the DAQ board.
+Synchronization of the camera rolling shutter to the scanning of the light sheet was achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
+The HSYNC signal from the camera was used which provided true-type-logic (TTL) pulse every time the rolling shutter stepped from one line to the next one.
+This trigger signal was used as a clock by the DAQ board so that the line producing the light sheet moved step by step with the rolling shutter.
+The same HSYNC signal was also used to trigger the DAQ digital signal sent to the laser modulator.
+Since at each position of the scanning line the modulator should go trough at least two states (vertical and horizontal polarization), HSYNC was used as a trigger while the the much faster internal clock of the DAQ board served as clock.
 
 \subsection{Software organisation}
-Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own software component (see supplementary information \ref{sec:murmex}).
-Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
-Beyond hardware-related software, two additional software components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.
+Each hardware component in the LSFM was managed through its own software component (see supplementary information \ref{sec:murmex}).
+Since the galvo scanners and the electro-optical modulator were not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sent analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Beyond hardware-related software, two additional software components, the Stack and Tomo components orchestrated the operation of the entire system.
 
-The Stack component is used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
+The Stack component was used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
 Stacks are collected by continuously moving the sample along $z$ while keeping the camera acquiring in free run.
-The translation speed is calculated such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI.
-The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
+The translation speed was calculated such that in the time needed to collect a single frame the specimen was moved by a $z$ step specified in the GUI.
+The Camera component used low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
 The Camera component must write data to disk with perfect synchronisation, otherwise the nominal $z$ position of each frame is no more coincident with the real $z$ position of the plane imaged.
-For this reason, we set the process executing the Camera code to be of highest priority.
-Additionally, the Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
-%The Stack component also specify the name and the path of the \emph{.cxd} file.
+For this reason, the process executing the Camera code was set to highest priority.
+Additionally, the Stack component checked the timing of data production, in order to re-acquire the image stack if the camera had encountered a timing issue.
 
-The Tomo component is a high level component which coordinates the acquisition of adjacent, parallel, partially-overlapping stacks. %It exchanges messages with the Stack and the Stages components.
-The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a text file with the coordinates of individual stacks to be collected.
+The Tomo component is a high-level component which coordinated the acquisition of adjacent, parallel, partially-overlapping stacks.
+The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a \textit{.txt} file with the coordinates of individual stacks to be collected.
 The Tomo component informs the experimenter via email when the acquisition is terminated either cleanly or through errors.
@@
 \section{Data Management}
-
-The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
-Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size amounts to $0.234\times0.234\times2$ $\micro\text{m}^3$.
-This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels.
-Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table \ref{tab:dataproduction}).
-However, image stacks are acquired with a 10\% of linear superposition, which is later used for image stitching.
-This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.
-
-This tremendous amount of data challenges the traditional way we interact with our data.
-Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, data management in light-sheet microscopy requires the development of a robust data management infrastructure, and of novel software tools to process the images in order to extract meaningful information.
-
-The camera used in our light-sheet microscope (Hamamatsu Orca Flash 4.0 v2) flushes the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
-Although this is already a large and expensive system for the current SSD technology, it is much smaller than the size of the raw datasets produced in each tomography.
-We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable.
-The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space.
-The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre).
-The data flow scheme is summarized in Fig.
-\ref{fig:DataFlow}.
-
-%Indeed, one stack may consist of thousands of slices of 1024 x 1024 pixels and with a color depth of 16 bits, leading easily to files of tens of Gigabytes each.
-To efficiently store raw data and make them suited for further processing, we have developed a tool for on-the-fly conversion of files generated during sample acquisitions to multi-page compressed TIFF format.
-
-While transferring data from the SSD to the NAS, we perform on-the-fly conversion of files generated during sample acquisitions to a multi-page and lossless-compressed TIFF format.
-%The TIFF format was chosen because it permits storage of a 3D image with lossless compression in a single file.
-Furthermore, it is a flexible and platform-independent format supported by numerous image processing applications.
-Our conversion module leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library.
-The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
-Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format is read slice by slice to minimize memory requirements.
-The conversion module runs concurrently with the microscope controlling software and it synchronizes to convert stack files as soon as they are completed.
-The module provides options to downsample the image or to save the input image at full or reduced resolution in order to adapt to storage requirements.
-Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling unaltered.
-This downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude.
-Thus the parallelepiped volume containing the whole mouse brain can be represented using about 2-3 TB of disk space.
-
-The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition.
-Thus, although file conversion drastically reduces data size, in the current implementation it is slower than data production.
-The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size: $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
-where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.
-
-With a standard image size of $2048 \times 2048$ pixels, and $R_{\text{frame}}=50$ Hz, data are produced at a rate $R_{\text{data}}=400$ MB/s $\approx 1.37$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2.3 \times 10^7$ $\micro\text{m}^3/s$ $\approx 0.08$ $\text{cm}^3$/h.
-The conversion module can empty the SSD with an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.67 TB/h.
-Imaging sessions should thus be shorter than 16.3 hours: this limits the maximum amount of raw data being acquired continuously to approximately 22.3 TB.
-This is well above the disk space needed to image the parallelepiped volume encompassing a whole mouse brain.
-Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
+\label{sec:dataflow}
 
@@
 (A) Data streaming on the microscope.
-SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
-Different colours (red, yellow and green) indicate the time-criticality (higher to lower) of each data movement.
-(B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
+SSD: solid-state disk, RAID: redundant array of independent disks.
+Colours indicate the time-criticality (red: higher to green: lower) of each data stream.
+(B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.
+NAS: network-attached storage}
    \end{figure}
+
+The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors determined that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
+Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size amounts to $0.234\times0.234\times2$ $\micro\text{m}^3$.
+This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels.
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB solely for the whole brain and 14.8 TB for the encompassing parallelepiped (see Table \ref{tab:dataproduction}).
+However, image stacks are acquired with 10\% of linear superposition, which is later used for image stitching.
+This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.
+
+This tremendous amount of data challenges the traditional way we interact with our data.
+Having far passed the point of taking your data home with you on a hard drive at the end of the experiment, the handling of data in light-sheet microscopy requires the development of a robust data management infrastructure and of novel software tools to process the images in order to extract meaningful information.
+
+The camera flushed the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB.
+Although this was already a large and expensive system for the current SSD technology, it was much smaller than the size of the raw datasets produced in each tomography.
+We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable.
+The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space.
+The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre).
+The data flow scheme is summarized in Fig.
+\ref{fig:DataFlow}.
+
+While transferring data from the SSDs to the NAS, we perform on-the-fly conversion of files generated during sample acquisitions to a losslessly compressed multi-page TIFF format.
+Our conversion module leveraged the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library.
+The module read a single \textit{.cxd} 3D image and wrote it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
+Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format was read slice by slice to minimize memory requirements.
+The conversion module ran concurrently with the microscope controlling software and was synchronized to convert stack files as soon as they are completed.
+The module provided options to downsample the image or to save the input image at full or reduced resolution in order to adapt to storage requirements.
+Usually we downsampled the image in the XY plane by a factor 2 and left the Z sampling unaltered.
+This downsampling, in combination with the lossless compression offered by the TIFF format, reduced data size by about one order of magnitude.
+Thus the parallelepiped volume containing the whole mouse brain took up about 2-3 TB of disk space.
+
+The process executing the file conversion was set to low priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition.
+Although file conversion drastically reduces data size, in the current implementation it was slower than data production.
+The camera flushed data to the SSDs with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size: $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
+where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{voxel size}$.
+
+With a standard image size of $2048 \times 2048$ pixels, and $R_{\text{frame}}=50$ Hz, data were produced at a rate $R_{\text{data}}=400$ MB/s $\approx 1.37$ TB/h, which resulted in a volumetric rate $R_{\text{volume}} \approx 2.3 \times 10^7$ $\micro\text{m}^3/s$ $\approx 0.08$ $\text{cm}^3$/h.
+The conversion module freed the SSDs with an average rate of $\approx$ 0.7 TB/h, meaning that the SSDs were actually filled up during imaging at a rate of $\approx$ 0.67 TB/h.
+Imaging sessions needed thus to be shorter than 16.3 hours which limited the maximum amount of raw data being acquired continuously to $\approx$ 22.3 TB.
+However, this was well above the disk space needed to image the parallelepiped volume encompassing a whole mouse brain.
+Larger specimens, as rat brain or portions of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
 
@@
 
-%relevant dimensions in typical acquisition sessions
-
-After acquisition, the tiled raw image produced has to be stitched.
-To perform this operation we have used the TeraStitcher\cite{Bria2012}, a fully automated stitching designed to deal with tiled images of virtually unlimited size.
+After acquisition, the tiled raw images produced had to be stitched to a 3D data set.
+To perform this operation we used the TeraStitcher\cite{Bria2012}, a fully automated stitching tool designed to deal with tiled images of virtually unlimited size.
 TeraStitcher can run on machines with limited resources with a performance essentially determined only by the transfer rate towards secondary storage.
@@
 (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$.
-(C,D,E) High resolution insert, of the stack corresponding to red boxes in C.
+(C,D,E) High resolution insert, of the stack corresponding to red boxes in B.
 Scale bar = $100 \micro m$.
@@
 \ref{fig:LSMdata}.
-With the apparatus describe in this paper, whole mouse brains can be imaged in their entirety (Fig.
-\ref{fig:LSMdata}A), maintaining a high quality of the image also while going deep inside the specimen (Figs.
-\ref{fig:LSMdata}B).
-The resolution and contrast of the images allow to distinguish axonal tracts (Fig.
-\ref{fig:LSMdata}C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labeled.
+With the apparatus described in this paper, whole mouse brains could be imaged in their entirety (Fig.
+\ref{fig:LSMdata},A), maintaining a high quality of the image also when going deep inside the specimen (Figs.
+\ref{fig:LSMdata},B).
+The resolution and contrast of the images allowed to distinguish axonal tracts (Fig.
+\ref{fig:LSMdata},C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labelled.
 GABAergic interneurons can be clearly identified using a GAD2-cre-dTomato mouse (Fig.
-\ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain.
+\ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain (Fig.
+\ref{fig:LSMdata},E).
 Such whole-brain datasets can be used to localize cell distributions in 3D using automatic cell-detection software \cite{Frasconi2014}.
@@
 
-Light sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale.
-This measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks.
+Light-sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data of high spatio-temporal scale.
+This measurement technique will continue to have a high impact in the field of whole-brain imaging due to its ability to record millions of images over the course of days or even weeks.
 Here we have presented a complete and detailed framework for whole mouse brain imaging.
-Starting with a full description of our double-sided light sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation.
-The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved andF processed necessitating the concurrent development of novel computational interface and analysis methods.
+Starting with a full description of our double-sided light-sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation.
+The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved and processed necessitating the concurrent development of novel computational interface and analysis methods.
 Here we have presented a comprehensive, robust and fully automated pipeline of data management starting from the streaming of raw images up to the stitching of 3D data sets.
@@
 A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
-Crucially for the high-throughput imaging of large samples that we aim for the protocol, however, is also fast, easy and cheap.
+Crucially for the high-throughput imaging of large samples that we aim for, the protocol, however, is also fast, easy and cheap.
 We therefore developed a versatile, simple, rapid and inexpensive clearing method described elsewhere\cite{Costantini} which in combination with CLARITY allows for the optical clearing of entire mouse brains or portions of human tissue.
@@
 %ao
-We have noticed that significant aberrations degrade image quality, especially at depths towards the end of the stack, even in refractive index-matched samples.
+Even in refractive index-matched samples we have noticed that significant aberrations degrade image quality, especially at depths towards the end of the stack.
 Recently objectives specifically conceived for LSFM have become commercially available\cite{Marx2014} which have been designed for use with clearing solutions and typically also feature a correction collar for the compensation of a certain amount of spherical aberration.
 A complete correction of system-induced aberrations, however, requires the ability to also correct for residual spherical aberration and higher-order aberrations introduced by the sample mount, immersion medium and slight misalignments of the optical system.
-Of course, aberrations introduced by the sample itself degrade image quality and it is those aberrations that are most difficult to correct in at run-time due to their modal complexity, large amplitude and high spatial variability\cite{Wang2014}.
+Of course, aberrations introduced by the sample itself also degrade image quality and it is those aberrations that are most difficult to correct at run-time due to their modal complexity, large amplitude and high spatial variability\cite{Wang2014}.
 
-Additionally another problem inherent to light sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths.
-Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012,Wang2014}.
-The prospect of high quality images is especially essential for high through-put imaging methods like light-sheet microscopy and whole brain 3D reconstruction because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}.
+Additionally another problem inherent to light-sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light sheet and the detection FOV when large samples are imaged at depths.
+Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012}.
+The prospect of high quality images is especially essential for high through-put imaging methods for whole-brain 3D reconstructions because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}.
 The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data.
 We have mounted the camera on a separate breadboard which leaves us with a lot of free, infinity-corrected space in the detection path.
-The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole brain reconstructions will be considered in the future.
+The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole-brain reconstructions will be considered in the future.
 
@@
 Further improvements in image quality may be achieved with beam shaping in the illumination arm, for example by implementing Bessel beam illumination\cite{Fahrbach2010,Planchon2011,Gao2014}.
-Using these self-reconstructing, non-diffractive beams the optical sectioning capability can be improved over an extended field of view.
+Using these self-reconstructing, non-diffractive beams the optical sectioning capability can be improved over an extended FOV.
 
 The streamlining of high-throughput imaging of entire mouse brains, starting from the live animal up to quantifiable data sets, requires tight integration of all aspects of the work flow.
-Even if the brains we image are transparent, their large size means that even comparatively small heterogenities in the refractive index matching sum up to large optical path differences and therefore strong aberrations at large imaging depth.
-The microscope used for whole brain imaging needs to be developed and adapted bearing those imaging circumstances in mind and sample preparation methods, imaging technology and data management schemes have to work as a unit in order to deliver on the highly anticipated, quantifiable data sets of whole brain neuronal projections.
+Even if the brains we image are transparent, their large size means that also comparatively small heterogenities in the refractive index matching sum up to large optical path differences and therefore strong aberrations at large imaging depth.
+The microscope used for whole-brain imaging needs to be developed and adapted bearing those imaging circumstances in mind and sample preparation methods, imaging technology and data management schemes have to work as a unit in order to deliver on the highly anticipated, quantifiable data sets of whole-brain neuronal projections.
 
@@
 
+\bibitem{Freeman2014} J.
+Freeman, N.
+Vladimirov, T.
+Kawashima, Y.
+Mu, N.
+Sofroniew, D.
+Bennett, J.
+Rosen, C.-T.
+Yang, L.
+Looger, et al., ``Mapping brain activity at scale with cluster computing," \emph{Nat.
+Methods} \emph{11}(9), 941–950 (2014).
+
+\bibitem{Burns2014} R. Burns, J. Vogelstein, and A. Szalay, ``From Cosmos to Connectomes: The Evolution of Data-Intensive Science," \emph{Neuron} \emph{83}(6), 1249-1252 (2014).
+
+\bibitem{Frasconi2014} P.
+Frasconi, L.
+Silvestri, P.
+Soda, R.
+L.
+Cortini, F.
+S.
+Pavone and G.
+Iannello, ``Large-scale automated identification of mouse brain cells in confocal light sheet microscopy images," \emph{Bioinformatics} \textbf{30}(17), i587-i593 (2014).
+
+\bibitem{Chung2013} K.
+Chung, J.
+Wallace, S.
+Y.
+Kim, S.
+Kalyanasundaram, A.
+S.
+Andalman, T.
+J.
+Davidson and K.
+Deisseroth, ``Structural and molecular interrogation of intact biological systems," \emph{Nature} \textbf{497}(7449), 332–33 (2013).
+
+\bibitem{Tomer2014} R. Tomer, L. Ye, B. Hsueh and K. Deisseroth, ``Advanced CLARITY for rapid and high-resolution imaging of intact tissues," \emph{Nat. Protoc.} \textbf{9}(7), 1682-1697 (2014).
+
 \bibitem{Keller2008a} P.
@@
 K.
-Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light-sheet fluorescence microscopy," \emph{urr.
+Stelzer, ``Quantitative in vivo imaging of entire embryos with digital scanned laser light-sheet fluorescence microscopy," \emph{Curr.
 Opin.
@@
 K.
-Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light-sheet microscopy," \emph{Sciences} \textbf{322}(5904), 1065–1069 (20108).
+Stelzer, ``Reconstruction of zebrafish early embryonic development by scanned light-sheet microscopy," \emph{Science} \textbf{322}(5904), 1065–1069 (2008).
 
@@
 
-\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light-sheet microscopy with confocal slit detection," \emph{Optics express} \textbf{20}(19), 21805-21814 (2012).
+\bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light-sheet microscopy with confocal slit detection," \emph{Opt. Express} \textbf{20}(19), 21805-21814 (2012).
 
@@
 S.
-Pavone,  ``Confocal light-sheet microscopy: micron-scale neuroanatomy of the entire mouse brain," \emph{Opt Express} \textbf{20}(18), 20582-20598 (2012).
+Pavone,  ``Confocal light-sheet microscopy: micron-scale neuroanatomy of the entire mouse brain," \emph{Opt.
+Express} \textbf{20}(18), 20582-20598 (2012).
 
@@
 Biomed.
-Opt.} 6(3), 266–272 (2001).
+Opt.} \textbf{6}(3), 266–272 (2001).
 
-\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} 12(4), 227–229 (1987).
+\bibitem{Wilson1987} T. Wilson and A. R. Carlini, ``Size of the detector in confocal imaging systems," \emph{Opt. Lett.} \textbf{12}(4), 227–229 (1987).
 
-\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} 63(1), 18–22 (2004).
+\bibitem{Cox2004} G. Cox and C. J. Sheppard, ``Practical limits of resolution in confocal and non-linear microscopy," \emph{Microsc. Res. Tech.} \textbf{63}(1), 18–22 (2004).
 
@@
 Booth, and T.
-Wilson, ``Characterizing specimen induced aberrations for high NA adaptive optical microscopy," \emph{Optics express} \textbf{12}(26), 6540–6552 (2004).
+Wilson, ``Characterizing specimen induced aberrations for high NA adaptive optical microscopy," \emph{Opt.
+Express} \textbf{12}(26), 6540–6552 (2004).
 
-\bibitem{Schwertner2007} M. Schwertner, M. J. Booth, and T. Wilson, ``Specimen‐induced distortions in light microscopy," \emph{Journal of microscopy} \textbf{228}(1) 97-102 (2007).
+\bibitem{Schwertner2007} M. Schwertner, M. J. Booth, and T. Wilson, ``Specimen‐induced distortions in light microscopy," \emph{J. Microsc.} \textbf{228}(1), 97-102 (2007).
 
@@
 
-\bibitem{Chung2013} K.
-Chung, J.
-Wallace, S.
-Y.
-Kim, S.
-Kalyanasundaram, A.
-S.
-Andalman, T.
-J.
-Davidson and K.
-Deisseroth, ``Structural and molecular interrogation of intact biological systems," \emph{Nature} \textbf{497}(7449), 332–33 (2013).
-
-\bibitem{Tomer2014} R. Tomer, L. Ye, B. Hsueh and K. Deisseroth, ``Advanced CLARITY for rapid and high-resolution imaging of intact tissues," \emph{nature protocols} \textbf{9}(7), 1682-1697 (2014).
-
-\bibitem{Marx2014} V. Marx, ``Microscopy: seeing through tissue," \emph{Nat Meth} \textbf{11}(12), 1209–1214 (2014).
+\bibitem{Marx2014} V. Marx, ``Microscopy: seeing through tissue," \emph{Nat. Methods} \textbf{11}(12), 1209–1214 (2014).
 
@@
 Ducommun, and C.
-Lorenzo, ``Deep and Clear Optical Imaging of Thick Inhomogeneous Samples," \emph{PLoS ONE} \textbf{7}(4), (2012).
+Lorenzo, ``Deep and Clear Optical Imaging of Thick Inhomogeneous Samples," \emph{PLoS ONE} \textbf{7}(4), e35795 (2012).
 
@@
 Mumm, and E.
-Betzig, ``Rapid adaptive optical recovery of optimal resolution over large volumes," \emph{nature methods} 11(6), 625–628, (2014).
+Betzig, ``Rapid adaptive optical recovery of optimal resolution over large volumes," \emph{Nat.
+Methods} \textbf{11}(6), 625–628 (2014).
 
-\bibitem{Frasconi2014} P.
-Frasconi, L.
-Silvestri, P.
-Soda, R.
-L.
-Cortini, F.
-S.
-Pavone and G.
-Iannello, ``Large-scale automated identification of mouse brain cells in confocal light sheet microscopy images," \emph{Bioinformatics} \textbf{30}(17), i587-i593 (2014).
-
-\bibitem {Fahrbach2010} F. Fahrbach and A. Rohrbach, ``A line scanned light-sheet microscope with phase shaped self-reconstructing beams," \emph{Optics Express} \textbf{18}(23), 780–785 (2010).
+\bibitem {Fahrbach2010} F. Fahrbach and A. Rohrbach, ``A line scanned light-sheet microscope with phase shaped self-reconstructing beams," \emph{Opt. Express} \textbf{18}(23), 780–785 (2010).
 
@@
 Galbraith, and E.
-Betzig, ``Rapid three-dimensional isotropic imaging of living cells using Bessel beam plane illumination," \emph{Nature Methods} \textbf{8}(5), 417–423 (2011).
+Betzig, ``Rapid three-dimensional isotropic imaging of living cells using Bessel beam plane illumination," \emph{Nat.
+Methods} \textbf{8}(5), 417–423 (2011).
 
@@
 Chen, and E.
-Betzig, ``3D live fluorescence imaging of cellular dynamics using Bessel beam plane illumination microscopy," \emph{Nature Protocols} \textbf{9}(5), 1083–1101 (2014).
+Betzig, ``3D live fluorescence imaging of cellular dynamics using Bessel beam plane illumination microscopy," \emph{Nat.
+Protoc.} \textbf{9}(5), 1083–1101 (2014).
 
@@
 
-%\listoffigures
-%pannel1: optical pathway, drawing images from chamber, sample mirror photos
-%pannel2: software scheme
-%panel3: hardware connection scheme
-%panel4: data pipeline, graph data amount/time
-%panel5: experiment pipeline
-%panel6: images, tomos
-
-%\listoftables
 \pagebreak
@@
 
-For light-sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
-The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane.
-Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Fig.
+For LSFM it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
+The objectives need to be perfectly confocal so that the fluorescence generated in the swept excitation beam also falls within the detection objective's focal plane.
+Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart (Fig.
 \ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives.
 In the detection path, the camera chip needs to be positioned in an image plane of the detection objective.
-Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as a pair with recursive dependence.
+Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned with respect to themselves but function as a pair with recursive dependence.
 
-Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be.
+Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber.
 The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Fig.
 \ref{fig:alignment},B).
-Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
+Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
 With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Fig.
@@
 \subsection{Sample preparation for optical characterisation}
-The fluorescent beads (CP01F, Bang Laboratories, $0.51 \micro m$ diameter) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 63\%TDE in PBS).
-The low melting point agarose (A-4018, Sigma-Aldrich) was dissolved at $\approx 40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
-The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}.
-The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175 \micro m-70 \micro m$ in the sample space.
-For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg.
-Fig.
-\ref{fig:origin},A) throughout the depth of the image stack.
+
+The fluorescent beads (CP01F, Bang Laboratories, $0.51 \micro m$ diameter) used for quantitative analysis of spatial resolution and signal to noise ratio (SNR) were embedded in low- melting point agarose (4\% agarose in 63\%TDE in PBS).
+The agarose (A9793, Sigma-Aldrich) was dissolved then mixed with a diluted bead solution and left to polymerise over night on a coverslip.
+The coverslip was mounted inside the sample chamber as described in section \ref{sec:mounting}.
+The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from $0.175 \micro m-70 \micro m$ in the sample space.
+For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ throughout the depth of the image stack.
 After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths.
@@
 
-\subsection{Sample preparation for whole brain imaging}
+\subsection{Sample preparation for whole-brain imaging}
+
 Mouse brains were processed using a modified CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
@@
 %The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
-Buffered, asynchronous and reliable communication between several software components is established by the routing of messages by the broker to the specific software component pinpointed by its ID.
+Buffered, asynchronous and reliable communication between several software components is established by routing of messages by the broker to the specific software component pinpointed by its ID.
 %The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
@@
 
-%\end{spacing}
+\end{spacing}
 \end{document}

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript1.2_Ludo.tex

--- 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript1.1_Ludo.tex
@@
    \end{center}
-   \caption{\label{fig:connectivity} Connectivity scheme} 
+   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively.
+The software architecture scheme clarifies the hierachic structure of the Murmex components.
+AO analog output, DO digital output, DI digital input.}
    \end{figure}
@@
 In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided.
-Both GUIs and code are developed according to the LabVIEW Style Guide \cite{}.
+Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
 
@@
 Usually, just a few of this states are actually used in standard application.
-An example of a standard implementation of the Murmex state machines for a scanning system is shown in Fig.
+An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig.
 BLABLA.
@@
 BLABLA, respectively.
-One personal computer (Dell XXXXX) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Dell YYYYY) to handle and manage the enormous streams of data produced (see next section).
-Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI XXXX, National Instruments, Austin, USA).
+One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section).
+Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).
 
@@
 The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
-Since the clearing procedure with CLARITY produces a linear expansion of about $1.2\times$ \cite{Costantini}, the volume of a clarified mouse brain can be estimated as $\simeq 0.9$ $\text{cm}^3$, while that of a parallelepiped encompassing the sample is expanded to $\simeq 1.6$ $\text{cm}^3$.
 Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$.
-This means that a cleared mouse brain will be represented with about 7.4 TeraVoxels, while a parallelepiped encompassing the brain will result in 13.3 TeraVoxels.
-Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 14.8 TB for the whole brain "alone" and 26.6 TB for the parallelepiped (see Table XXXX).
+This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels.
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table XXXX).
 However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching.
-This redundancy expands the size of raw data to 18.3 TB and 32.8 TB, respectively.
+This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.
 
@@
 Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB.
-Taking into accont the 10\% linear superposition between adjacent stacks, the maximum size of a sample that can be imaged in a single session is about 1.2 $\text{cm}^3$, which is larger than a cleared mouse brain, but smaller than the estimate size of a parallelepiped volume encompassing the entire volume.
-Therefore imaging should be limited to the portion of the volume where the brain is with rational selection of stacks.
+This is well above the disk space needed to image the parallelepieped volume encompassing a whole mouse brain.
 Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
@@
 (A) Data streaming on the microscope.
-The data is written through the CameraLink connection onto the SSD.
-From there the data can be transferred via a 10Gb connection to the NAS or to the supercomputing centre CINECA in Bologna.
 SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
@@
 
+\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
+
 \end{thebibliography}

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_Leo.tex

--- 2015-02-15 latex-style-files-spie-manuscript/manuscript_Leo.tex
@@
 The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
-In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$.
 An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table \ref{tab:resolution}.
@@
 The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.
-From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated.
-The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera.
+From the same data the average FWHM of the Gaussian excitation line over the FOV of the camera was calculated as $(8.60\pm0.67)\micro m$ (n= 14).
 
-For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?).
-The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.
+For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories).
+The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig.
 \ref{fig:origin},B).
-The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively.
-The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig.
-\ref{fig:origin},C).
+The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively (n=10).
+The experimentally determined lateral FWHM was larger than the theoretically expected value of $0.26 \micro m$ by a factor of four and this increase was most likely due to....
+The experimentally determined axial FWHM was in good agreement with our measured light-sheet thickness of $8.6\micro m$ and marginally larger than the theoretically expected value.
+
+The SNR increased with increasing slit width up to a maximum at a slit width of $7 \micro m$ (Fig. \ref{fig:origin},C).
 
@@
 Scale bar = 100 µm.}
-   \end{figure}
-
-	Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
+   %\end{figure}
+	%
+	%Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
 
 \section{Conclusion}
-summary
+
 Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a combination of unprecedented spatio-temporal scale.

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_merged_Ludo.tex

--- 2015-02-05 latex-style-files-spie-manuscript/manuscript_merged.tex
@@
 
-\title{Robust data management for high through-put light sheet microscopy of whole mouse brains}
+\title{Comprehensive optical and data management infrastructure for high through-put light sheet microscopy of whole mouse brains}
 
@@
 The zero order light is blocked by an iris.
-An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
-The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system.
+An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$.
+The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system.
 First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier.
-A digital line is used to electronically control the frequency with which the polarisation is changed.
+A digital line is used to switch to zero the output of the pre-amplifier, allowing control of the frequency with which the polarisation is changed.
 After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).
@@
 Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions.
-The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP).
+The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm).
 To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging.
@@
 \section{Optical characterisation}
-An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.
+
+The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space.
+In particular, the radial (i.e.
+perpendicular to the detection axis) and axial (i.e.
+parallel to the detection axis) resolutions of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction.
+In a light sheet microscope, axial and radial resolutions are determined by the NA of the illumination and detection optics, respectively.
+The radial PSF is a standard Airy function, whose FWHM is given by:
+\begin{equation}
+\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
+\end{equation}
+$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.
+
+The axial resolution is given by the thickness of the light sheet.
+If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics \cite{something}.
+The $1/e^2$ radius of the beam waist is given by:
+\begin{equation}
+w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
+\end{equation}
+where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index).
+Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from 1 \cite{Silvestri2012}.
+The axial FWHM is then given by:
+\begin{equation}
+\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
+\end{equation}
+
+The thickness of the light sheet is not constant throughout the field of view due to the limited depth of focus of the Gaussian beam.
+This latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius is not bigger than $\sqrt{2} w_0$:
+\begin{equation}
+b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
+\end{equation}
+
+The need to have an almost uniform resolution in the camera field of view (FOV) imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution.
+In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq ???$, resulting in $b \simeq ???$ and $\text{FWHM}_{\text{axial}} \simeq?????$.
+
+An overview of the relevant formulas for the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}.
+The reader could refer to this table as a quick guide to tailor the apparatus to her specific needs.
+
+AND HERE THE AMMAZING OURS DATAS
 
@@
    \end{center}
-   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively.
-The software architecture scheme clarifies the hierachic structure of the Murmex components.
-AO analog output, DO digital output, DI digital input.}
+   \caption{\label{fig:connectivity} Schematic view of the hardware architecture of the microscope. Different kind of physical connections are depicted with different colors.} 
    \end{figure}
@@
    \end{center}
-   \caption{\label{fig:murmex} This graph needs a caption.} 
+   \caption{\label{fig:murmex} Schematic view of the workflow of a representative Murmex component operating a camera.} 
    \end{figure}
@@
 An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig.
-BLABLA.
+\ref{fig:murmex}.
 Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file.
@@
 
-A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig.
-BLABLA, respectively.
+A schematic overview of the hardware architecture of our light sheet microscope is shown in Fig.
+\ref{fig:connectivity}.
 One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section).
@@
 The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack.
-The name of this file and the path to it is specified by the Stack component.
+Note that the Camera component must write data to disk in perfect time, otherwise the nominal $z$ position is of each frame is no more coincident with the real $z$ position of the plane imaged.
+For this reason, we set the process executing the Camera code to be of highest priority.
+The Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time.
+The Stack component also specify the name and the path of the \emph{.cxd} file.
 
@@
 The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$.
-Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$.
+Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size results $0.234\times0.234\times2$ $\micro\text{m}^3$.
 This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels.
-Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table XXXX).
+Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table \ref{tab:dataproduction}).
 However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching.
@@
 The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
-Since the output of the Hamamatsu camera may exceed tens of Gbytes, the image in proprietary format is read slice by slice to minimize memory requirements.
+Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format is read slice by slice to minimize memory requirements.
 The module has also an option to downsample the image on save the input image at full or reduced resolution, in order to adapt to storage availability.
@@
 
-Although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
-The Camera component flushes data on the SSD with a rate $R_{data}$ dependent on frame rate $R_{frame}$ and on the image size:
+The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition.
+Thus, although file conversion drastically reduces data size, in the current implementation it is quite slower than data production.
+The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on frame rate $R_{\text{frame}}$ and on the image size:
 \begin{equation}
-R_{data} [\text{Bytes}] = 2\times R_{frame} \times \#_{pixels}\,,
+R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}\,,
 \end{equation}
-where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{volume} = 0.5 R_{data} \times \text{Voxel size}$.
+where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.
 
-With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
+With a standard image size of $2048\times 2048$ pixels, and $R_{\text{frame}}=44$ Hz, data are produced at a rate $R_{\text{data}}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2\times 10^7$ $\micro\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h.
 The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h.
@@
 SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage.
+Different colors (red, yellow and green) indicate the time-sensitivity (higher to lower) of each data movement.
 (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.}
@@
 	\centering
-		\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
+		\caption[Data production]{Data production rates for typical camera operation.\label{tab:dataproduction}}
 		\begin{tabular}{lrl}
-		frame rate																	& 44			& Hz	\\
-		size of 1 frame															& 8				& MB	\\
-		frames per stack														& 3900		& 		\\
-		size of original stack											& 30.4		& GB	\\
-		size of converted stack											& 3				& GB	\\
-		stack acquisition time											& 88.6		& s		\\
-		stack conversion time												& 140			& s		\\
-		time ratio conversion/ acquisition					& 1.6			& 		\\
-		data production rate												& +1.2		&	TB/h\\
-		data conversion rate												& -0.7		&	TB/h\\
-		net rate																		& +0.5		&	TB/h\\
-		SSD RAID																		& 10.9		& TB	\\
-		max acquisition time to fill up SSDs				& 21			& h		\\
-		max tomo size to fill up SSDs								& 25.4		& TB	\\
+		\\
+		Voxel size											& $0.234 \times 0.234 \times 2$	& $\micro\text{m}^3$ 	\\
+		Frame rate											& 44							& Hz					\\
+		Frame size											& $2048 \times 2048$ 			& pixels					\\
+		Frame disk size										& 8								& MB					\\
+		Data production rate									& 1.2							& TB/h 					\\
+		Data conversion rate									& 0.7							& TB/h 					\\
+		Net SSD filling rate									& 0.5							& TB/h 					\\
+		SSD RAID size										& 10.9							& TB					\\
+		Max acquisition time to fill up SSDs					& 21.8							& h						\\
+		Max raw data size that can be acquired continuously	& 25.4							& TB					\\
+		Max volume that can be imaged 						& 1.24							& $\text{cm}^3$ 		\\
+		(considering 10\% superposition between adjacent stacks)	&							&						\\
 		\end{tabular}
@@
 \section{Outlook}
-where are we going next with this? ask Leo Onofri and Giulio to contribute to this, issues data mangament, aberration correction
-mapping of complementary data sets obtained in the same system, eg structural connectivity, morphology and gene expression.
+%where are we going next with this? ask Leo Onofri and Giulio to contribute to this, issues data mangament, aberration correction
+%mapping of complementary data sets obtained in the same system, eg structural connectivity, morphology and gene expression.
 
@@
 		Component			&	Manufacturer								& Part\# 				& Specifications 														\\\hline\hline
-		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\
-																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																	\\
-																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised														\\
-																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
-																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
-		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
+		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden}	& MLD		& 405nm,  80mW, s-polarised											\\
+							&												& MLD					& 445nm, 50mW, s-polarised											\\
+							&   												& Calypso				& 491nm, 50mW, s-polarised											\\
+							&												& Fandango				& 515nm, 50mW, s-polarised											\\
+							&												& Jive					& 561nm, 50mW, s-polarised											\\\hline
+		AOTF				& AA Opto-Electronic, France						&AOTFnC-400.650-TN 	&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
 		Laser modulator 		& Qioptiq	GmbH, Germany						& LM 0202 VIS ADP		& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V			\\\hline
@@
 							&												& M-116 				& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
-		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
+		Camera 				& Hamamatsu, Japan								& Orca Flash4.0 	V2.0	& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
 		DAQ board			& National Instruments, USA						& NI PCIe-6353			& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
-		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
+		Workstation 1		& Dell, USA										& T7500					&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, OS Windows 7 64 bit}\\
+		Workstation 2		& Dell, USA										& T5600					&  \pbox[t]{10.5cm}{8GB RAM, Intel Xeon Processor E5-2620 @ 2 GHz, OS Windows 7 64 bit}\\
 		\end{tabular}
@@
 
-\begin{landscape}
 \begin{table}[t!]
 	\centering
-		\caption[Resolution]{Imaging properties and derived quantities.
-The thickness of the light sheet is approximately of the same size as the depth of field of the high NA detection lens.\label{tab:resolution}}
-		\begin{tabular}{lrlrl}
-		\multicolumn{5}{l}{Detection}\\\hline\hline  
-		wavelength																	&	$\lambda$				&																																					& 0.5			& $\mu m$	\\
-		refractive index														&	n								&																																					& 1.45		& 				\\
-		numerical aperture 													&	$\text{NA}_d$		&																																					& 1				& 				\\
-		%angular aperture 													& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
-		magnification 															& $M_{\text{eff}}$&	$= \nicefrac{f_{\text{TL}}}{\text{EFL}}$																& 27.8		&					\\
-		tube lens 																	& $f_{\text{TL}}$	&																																					& 200			&	$mm$		\\
-		effective focal length objective						& EFL							& $=\nicefrac{f_{\text{TL}}}{M}$																					& 7.2			& $mm$		\\
-		diameter back focal plane										& BFP							& $= 2\cdot \text{EFL} \cdot \text{NA}_d$																	& 14.4		& $mm$		\\
-		field number																& FN							&																																					& 18			& $mm$		\\
-		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.65		& $mm$		\\
-		depth of field															& $\Delta$				& $=\nicefrac{\lambda \cdot n}{(\text{NA}_d)^2}+ \nicefrac{n \cdot e}{M \cdot \text{NA}_d}$	& 1.06 		& $\mu m$	\\ 
-		Airy radius lat.														& $r_A$						& $=\nicefrac{0.61 \lambda}{\text{NA}_d}$																	& 0.31		& $\mu m$	\\\\
-		\multicolumn{5}{l}{Excitation}\\\hline\hline
-		numerical aperture 													&	$\text{NA}_e$		&																																					& 0.3			& 				\\
-		magnification,	nominal											& m								&																																					& 10			&					\\
-		tube lens 																	& $f_{\text{tl}}$	&																																					& 100			&	$mm$		\\
-		effective focal length, objective						& efl							& $=\nicefrac{f_{\text{tl}}}{m}$																					& 20			& $mm$		\\
-		magnification, effective										& $m_e$						&	$=\nicefrac{f_{\text{tl}}}{\text{efl}}$																	& 5				&					\\
-		refractive index														&	$\eta$					&																																					& 1				& 				\\
-		beam radius																	& $\omega$				&																																					& 4.5			& $mm$		\\
-		%Airy radius lat.														& $r_a$						& $=\nicefrac{0.61 \lambda}{\text{NA}_e}$																	& 1.02		& $\mu m$	\\
-		min light sheet waist												& $\omega_0$			& $=\nicefrac{\lambda \text{efl}}{\pi \omega}$														& 1.41		& $\mu m$	\\
-		confocal parameter													& b								& $=\nicefrac{2 \pi \omega_0^2}{\lambda}$																	& 25.15		& $\mu m$	\\\\
-		\multicolumn{5}{l}{Camera}\\\hline\hline
-		cell size																		& e								&																																					& 6.5			&	$\mu m$	\\
-		effective area 															& $r^2$						&																																					& $13.3^2$	&	$\text{mm}^2$	\\
-		line read out time													& t								&																																					& 9.7			&	$\mu s$	\\
-		line exposure time													& l								&																																					& 3				&	ms			\\
-		slit width, camera space										& $d_c$						& $=\nicefrac{l \cdot e}{t} $																							& 2				&	mm	\\
-		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 0.72		&	mm	\\
-		frame rate																	& $\nu$						&	$=\nicefrac{1}{(2048 \cdot t + l})$																			& 43.6		& Hz\\
+		\caption[Main formulas]{Overview of the main formulas related to light sheet microscopy.
+In the table, $f_{\text{TL}}^{\text{design}}$ is the focal length of the tube lens for which the objective has been designed (200 mm for Leica and Nikon, 180 mm for Olympus and 165 mm for Zeiss), $f_{\text{TL}}^{\text{real}}$ the focal length of the tube lens actually used, $\text{M}$ the nominal magnification of the objective, $n$ the refractive index of the immersion medium, $\lambda_0$ the wavelength in vacuum, $\lambda$ the wavelength in the medium, $w$ the $1/e^2$ radius of the Gaussian beam at the objective back focal plane, FN the field number of the objective, $p$ the physical pixel size, $l_{\text{chip}}$ the size of the camera chip, $t_{\text{shutter}}$ the pace of the rolling shutter (i.e.
+the time between exposure start in subsequent lines), $ t_{\text{exp}}$ the line exposure time.
+The subscripts $_i$ and $_d$ refers to illumination and detection, respectively.
+\label{tab:resolution}}
+		\begin{tabular}{lrcl}
+		\\
+		\multicolumn{4}{l}{General formulas for microscope objectives}\\\hline\hline 
+		Nominal focal length				& $f$ 							& $=$	& $f_{\text{TL}}^{\text{design}}/\text{M}$				\\	
+		Effective focal length				& $f^{\text{eff}}$				& $=$	& $nf$													\\
+		Effective magnification			& $\text{M}^{\text{eff}}$		& $=$	& $f_{\text{TL}}^{\text{real}}/f^{\text{eff}}$			\\\\
+		\multicolumn{4}{l}{Excitation (Gaussian)}\\\hline\hline
+		Beam waist						&$w_0$							& $=$ 	& $ \lambda f_{\text{i}}^{\text{eff}} / \pi w$				\\
+		Axial resolution					&$\text{FWHM}_{\text{axial}}$	& $=$   & $1.177 w_0 $											\\
+		Confocal parameter				& b								& $=$   & $2 \pi \omega_0^2 / \lambda$							\\
+										& b								& $=$   & $2 \lambda {(f_{\text{i}}^{\text{eff}})}^2 / \pi w^2 $	\\\\
+		\multicolumn{4}{l}{Detection}\\\hline\hline  
+		Radial resolution					&$\text{FWHM}_{\text{radial}}$	& $=$	& $0.5 \lambda_0 / \text{NA}_{d}$						\\
+		Objective field size				& S								& $=$	& $\text{FN}/{\text{M}}$								\\\\
+		\multicolumn{4}{l}{Camera}\\\hline\hline  
+		Pixel size in object space			& $ p_{\text{object}}$			& $=$	& $p/  \text{M}^{\text{eff}}$							\\
+		Camera FOV in object space		&$\text{FOV}_{\text{object}}$	& $=$	& $l_{\text{chip}} / \text{M}^{\text{eff}}$				\\
+										&$\text{FOV}_{\text{object}}$	& $=$	& $p_{\text{object}} \cdot \#_{\text{pixels}}$			\\
+		Slit width on the camera			& $s_{\text{camera}}$			& $=$	& $ p \cdot t_{\text{shutter}} / t_{\text{exp}} $			\\
+		Slit width in object space			& $s_{\text{object}}$			& $=$	& $ s_{\text{camera}}/ \text{M}^{\text{eff}}$			\\
+		Frame rate						& $\nu$							& $=$	& $1/(\#_{\text{vert. pixels}} \cdot t_{\text{exp}} + t_{\text{shutter}})$ \\\\
+
 		\end{tabular}
 \end{table}
-\end{landscape}
 

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo.tex

--- 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
@@
 
-\section{Representative results}
+\section{Data}
 
@@
 (C,D,E) High resolution insert, of the stack corresponding to red boxes in C.
-Scale bar = $100 \micro m$.
-Modified with permission from \cite{Costantini}.}
+Scale bar = $100 \micro m$.}
    \end{figure}
 
-Some representative data produced by our microscope are reported in Fig.
-\ref{fig:LSMdata}.
-With the apparatus describe in this paper, whole mouse brains can be imaged in their entirety (Fig.
-\ref{fig:LSMdata}A), maintaining a high quality of the image also while going deep inside the specimen (Figs.
-\ref{fig:LSMdata}B).
-The resolution and contrast of the images allow distinguish axonal tracts (Fig.
-\ref{fig:LSMdata}C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labeled.
-GABAergic interneurons can be clearly identified using a GAD2-cre-dTomato mouse (Fig.
-\ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain.
-Such whole-brain dataset can be used to localize cellular distribution in three-dimensions using automatic cell-detection software \cite{Frasconi2014}.
+	To exemplify the imaging capabilities of our microscope see Fig. \ref{fig:LSMdata}.
 
@@
 \acknowledgments
-The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for fabrication of the sample chamber.
+The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for the conception and fabrication of the sample chamber.
 We further thank Marco De Pas from the electronic workshop for his expertise in the fabrication of the custom-made amplification electronics.
-We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.\\
-The research leading to these results has received funding from the European Union Seventh Framework Program (FP7\slash2007-2013) under grant agreements no.
-604102 (Human Brain Project) and n$\degree$ 284464 (LASERLAB-EUROPE).
-The research has also been supported by the Italian Ministry for Education, University and Research in the framework of the Flagship Project NanoMAX, by  ``Ente Cassa di Risparmio di Firenze" (private foundation).
-Research activities were also supported by Regione Toscana in the program POR-CreO 2007-2013 (Linea di interventi 1.5.a - 1.6 - Bando Unico R\&S 2012) under grant agreement (CUP) n$\degree$ 6408.30122011.026000201.
+We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.
+Human Brain Project tutta la vita and also Ludo's long sentence copy pasta.
 
@@
 \subsubsection{Sample preparation for whole brain imaging}
-Mouse brains were processed using the CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
-Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS.
-We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at 4°C for 3 days.
-Afterwards, we degassed the samples and increased their temperature to 37 °C to initiate polymerization.
-The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at 37 °C through gentle shaking.
-To perform electrophoretic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber.
-The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at 37 °C for several days.
-After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at 37 °C for 2 days to remove the clearing solution.
-As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at 37°C while gently shaking.
-The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.
 

### 2015-03-27 Neurophotonics/Stuff/manuscript1.1_Caro.tex
commit before revision process

--- 2015-01-20 latex-style-files-spie-manuscript/manuscript1.0.tex
@@
    \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.
-Excitation (blue) and fluorescence detection (green) occur on independent, perpendicular axes.
+The sample is illuminated with a planar light sheet (blue) perpendicular to fluorescence detection (green).
 (B) Mounting of a clarified, fluorescently labelled brain.
@@
 
-To acquire whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B).
+For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B).
 The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip.
@@
 The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective.
-%This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
+This generates incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
+Additionally each line is specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.
 
-\subsection{Detection}
+\subsection{Detection unit}
 		%objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
 		%exposure time of single line affects how many are exposed at same time, confocality by synchronisation- not exactly
+
+		%mention cell size, new paragraph explain option to go confocal
 

### 2015-03-27 Neurophotonics/Stuff/manuscript_snellendo_merged.tex
commit before revision process

--- 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
@@
 The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage.
-To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets.
+To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching of 3D data sets.
 The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains.
@@
 %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community.
-We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of several terabytes.
-To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.
+We further give a systematic and robust approach to handle and store light-sheet microscopy data of several terabytes.
+To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching of large 3D data sets.
 The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.
@@
 
-Light sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale.
+Light-sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale.
 This measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks.
 Here we have presented a complete and detailed framework for whole mouse brain imaging.
-Starting with a full description of our double-sided light sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation.
-The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved andF processed necessitating the concurrent development of novel computational interface and analysis methods.
+Starting with a full description of our double-sided light-sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation.
+The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved and processed necessitating the concurrent development of novel computational interface and analysis methods.
 Here we have presented a comprehensive, robust and fully automated pipeline of data management starting from the streaming of raw images up to the stitching of 3D data sets.
@@
 
-Additionally another problem inherent to light sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths.
+Additionally another problem inherent to light-sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths.
 Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012,Wang2014}.

### 2015-05-13 Neurophotonics/Submitted files/manuscript_revision.tex
commit after submission of revised manuscript

--- 2015-03-25 latex-style-files-spie-manuscript/manuscript_submission.tex
@@
 To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from streaming of raw images up to stitching of 3D data sets.
-The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains.
+The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterisation and quantification of neuronal projections in unsectioned mouse brains.
 \end{abstract}
@@
 %>>>> Include a list of up to six keywords after the abstract
-\keywords{Light-sheet microscopy, whole brain imaging, data management, software management, imaging pipeline, high-throughput imaging}
+\keywords{Light-sheet microscopy, selective plane illumination microscopy, whole brain imaging, data management, software management, high-throughput imaging}
 
@@
 
-		\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame1.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:excitation} (A) Schematic of the light path.
-The galvo scanners are mounted above periscopes.
-LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter.
-Green dotted: detection path.
-(B) Oblique view of the microscope.
-A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages.
-A second breadboard is used for the camera.}
-   \end{figure}
-
 \subsection{Laser unit}		
@@
 The focal lengths of the doublets making up the telescope have been chosen for space considerations and to achieve a $1/e^2$ beam radius of 0.73mm at the back focal plane resulting in an effective NA of 0.025 (see also section \ref{sec:characterisation}).
-The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
+The galvos are in planes conjugated with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen.
 The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber.
@@
 
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame2.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:frame2} Schematic of sample mounting and motion.
-(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light-sheet and the detection focal plane overlap.
-(B) The custom-made sample chamber is assembled with silicone bellows and seal rings.
-The clarified fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D).
-(E) Mounting of a clarified fluorescently labelled brain.
-The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.}
-   \end{figure}
-
 We designed a cubic water-tight sample chamber (Fig.
@@
 To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed.
-A motorized x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig.
+A motorised x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig.
 \ref{fig:frame2},D).
@@
 
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame3.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:origin} Optical characterisation.
-(A) Exemplary lateral and axial intensity profiles of nanometric beads and fits to Gaussian curves.
-(B) FWHM of the Gaussian fits with confocal slit width.
-Each data point is the average of 10 bead profiles.
-(C) Signal to noise ratio (SNR) as a function of slit width.}
-\end{figure}
-
 For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.
@@
 The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software written in the LabVIEW language (National Instruments, Austin, US).
-Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, stringent software design is a primary concern.
+Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronisation, stringent software design is a primary concern.
 The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance.
@@
 
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame4.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:connectivity} Schematic view of the hardware architecture of the microscope. Different kind of physical connections are depicted with different colours.} 
-   \end{figure}
-
 A schematic overview of the hardware architecture of our LSFM is shown in Fig.
@@
 
-Synchronization of the camera rolling shutter to the scanning of the light sheet was achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
+Synchronisation of the camera rolling shutter to the scanning of the light sheet was achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers.
 The HSYNC signal from the camera was used which provided true-type-logic (TTL) pulse every time the rolling shutter stepped from one line to the next one.
@@
 The same HSYNC signal was also used to trigger the DAQ digital signal sent to the laser modulator.
-Since at each position of the scanning line the modulator should go trough at least two states (vertical and horizontal polarization), HSYNC was used as a trigger while the the much faster internal clock of the DAQ board served as clock.
-
-\subsection{Software organisation}
-Each hardware component in the LSFM was managed through its own software component (see supplementary information \ref{sec:murmex}).
-Since the galvo scanners and the electro-optical modulator were not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sent analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
-Beyond hardware-related software, two additional software components, the Stack and Tomo components orchestrated the operation of the entire system.
-
-The Stack component was used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
-Stacks are collected by continuously moving the sample along $z$ while keeping the camera acquiring in free run.
-The translation speed was calculated such that in the time needed to collect a single frame the specimen was moved by a $z$ step specified in the GUI.
-The Camera component used low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
-The Camera component must write data to disk with perfect synchronisation, otherwise the nominal $z$ position of each frame is no more coincident with the real $z$ position of the plane imaged.
-For this reason, the process executing the Camera code was set to highest priority.
-Additionally, the Stack component checked the timing of data production, in order to re-acquire the image stack if the camera had encountered a timing issue.
-
-The Tomo component is a high-level component which coordinated the acquisition of adjacent, parallel, partially-overlapping stacks.
-The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a \textit{.txt} file with the coordinates of individual stacks to be collected.
-The Tomo component informs the experimenter via email when the acquisition is terminated either cleanly or through errors.
-
-All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
-Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
+Since at each position of the scanning line the modulator should go trough at least two states (vertical and horizontal polarisation), HSYNC was used as a trigger signal while the the much faster internal clock of the DAQ board served as clock.
 
@@
 \label{sec:dataflow}
-
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{DataFlow.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:DataFlow} Scheme of the data flow.
-(A) Data streaming on the microscope.
-SSD: solid-state disk, RAID: redundant array of independent disks.
-Colours indicate the time-criticality (red: higher to green: lower) of each data stream.
-(B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.
-NAS: network-attached storage}
-   \end{figure}
 
@@
 The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre).
-The data flow scheme is summarized in Fig.
+The data flow scheme is summarised in Fig.
 \ref{fig:DataFlow}.
@@
 The module read a single \textit{.cxd} 3D image and wrote it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file.
-Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format was read slice by slice to minimize memory requirements.
-The conversion module ran concurrently with the microscope controlling software and was synchronized to convert stack files as soon as they are completed.
+Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format was read slice by slice to minimise memory requirements.
+The conversion module ran concurrently with the microscope controlling software and was synchronised to convert stack files as soon as they are completed.
 The module provided options to downsample the image or to save the input image at full or reduced resolution in order to adapt to storage requirements.
@@
 
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{data_panel.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:LSMdata} Whole mouse brain tomography.
-Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective.
-(A) 3D rendering of a parvalbumin-dTomato brain.
-(B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$.
-(C,D,E) High resolution insert, of the stack corresponding to red boxes in B.
-Scale bar = $100 \micro m$.
-Modified with permission from \cite{Costantini}.}
-   \end{figure}
-
 Some representative data produced by our microscope are reported in Fig.
@@
 With the apparatus described in this paper, whole mouse brains could be imaged in their entirety (Fig.
-\ref{fig:LSMdata},A), maintaining a high quality of the image also when going deep inside the specimen (Figs.
+\ref{fig:LSMdata},A), maintaining a high quality of the image also when going deep inside the specimen (Fig.
 \ref{fig:LSMdata},B).
-The resolution and contrast of the images allowed to distinguish axonal tracts (Fig.
+The resolution and contrast of the images allowed to clearly distinguish axonal tracts (Fig.
 \ref{fig:LSMdata},C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labelled.
-GABAergic interneurons can be clearly identified using a GAD2-cre-dTomato mouse (Fig.
-\ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain (Fig.
-\ref{fig:LSMdata},E).
-Such whole-brain datasets can be used to localize cell distributions in 3D using automatic cell-detection software \cite{Frasconi2014}.
+Lateral and axial intensity profiles through a fine axonal projection were used to estimate resolution in a brain data set in terms of the FWHM in the lateral and axial directions (Fig.
+\ref{fig:LSMdata},D).
+The lateral and axial FWHM were $1.7 \micro m$ and $8.5 \micro m$ respectively, in agreement with the measurements on fluorescent beads.
+Whole-brain datasets as presented here can be used to localise cell distributions in 3D using automatic cell-detection software \cite{Frasconi2014}.
 
@@
 A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining.
-A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form.
+A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridised, lipid-free form.
 Crucially for the high-throughput imaging of large samples that we aim for, the protocol, however, is also fast, easy and cheap.
@@
 Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012}.
-The prospect of high quality images is especially essential for high through-put imaging methods for whole-brain 3D reconstructions because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}.
+The prospect of high quality images is especially essential for high through-put imaging methods for whole-brain 3D reconstructions because the size of data sets is so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}.
 The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data.
@@
 S.
-Pavone, \emph{submitted}.
+Pavone, ``A versatile clearing agent for multi-modal brain imaging," \emph{Sci.
+Rep.} \textbf{5}(9808), (2015).
 
 \bibitem{Baumgart2012} E. Baumgart and U. Kubitscheck, ``Scanned light-sheet microscopy with confocal slit detection," \emph{Opt. Express} \textbf{20}(19), 21805-21814 (2012).
-
-%\bibitem{Kaufmann2012} A.
-Kaufmann, M.
-Mickoleit, M.
-Weber and J.
-Huisken, ``Multilayer mounting enables long-term imaging of zebrafish development in a light-sheet microscope," \emph{Development} \textbf{139}(17), 3242-3247 (2012).
-%
-%\bibitem{Pitrone2013} P.
-Pitrone, J.
-Schindelin, L.
-Stuyvenberg, S.
-Preibisch, M.
-Weber, K.
-W.
-Eliceiri, J.
-Huisken and P.
-Tomancak, ``OpenSPIM-an open access platform for light-sheet microscopy," \emph{arXiv} reprint arXiv:1302.1987, 3242-3247 (2013).
-%
-%\bibitem{Olarte2012} O.
-E.
-Olarte, J.
-Licea-Rodriguez, J.
-A.
-Palero, E.
-J.
-Gualda, D.
-Artigas, J.
-Mayer and P.
-Loza-Alvarez, ``Image formation by linear and nonlinear digital scanned light-sheet fluorescence microscopy with Gaussian and Bessel beam profiles," \emph{Biomedical optics express} \textbf{3}(7), 1492-1505 (2012).
 
@@
 \bibitem{Schwertner2007} M. Schwertner, M. J. Booth, and T. Wilson, ``Specimen‐induced distortions in light microscopy," \emph{J. Microsc.} \textbf{228}(1), 97-102 (2007).
-
-%\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).
 
@@
 
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel3.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light-sheet microscope.
-AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises.
-(B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.
-(C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm.
-(D) The alignment mirror can be rotated to precisely reflect by $90\degree$.}
-   \end{figure}
-
 For LSFM it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast.
@@
 Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror.
-With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Fig.
+With this ``sample mirror" three different positions can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Fig.
 \ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Fig.
 \ref{fig:alignment},D).
-
-\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel4.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront.
-Right: inverted light path, a focal spot in the back aperture creates a collimated output.
-(B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.}
-   \end{figure}
 
@@
 Mouse brains were processed using a modified CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}.
-Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS.
+Adult mice (post-natal day 56) were anaesthetised with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS.
 We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at $4 \degree$ C for 3 days.
-Afterwards, we degassed the samples and increased their temperature to $37 \degree$ C to initiate polymerization.
+Afterwards, we degassed the samples and increased their temperature to $37 \degree$ C to initiate polymerisation.
 The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at $37 \degree $ C through gentle shaking.
@@
 After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at $37 \degree$ C for 2 days to remove the clearing solution.
-As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at $37 \degree$ C while gently shaking.
+As a final step, murine brains were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at $37 \degree$ C while gently shaking.
 The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.
+The experimental protocols involving animals were designed in accordance with the laws of the Italian Ministry of Health.
+All experimental protocols were approved by the Italian Ministry of Health.
 
@@
 \label{sec:murmex}
-	\begin{figure}
-   \begin{center}
-   \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{murmex.eps}
-   \end{tabular}
-   \end{center}
-   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
-   \end{figure}
 
 To operate the software efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used.
-This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardized programming scheme.
+This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardised programming scheme.
 
@@
 For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middle-ware, however, these layers of abstraction are mostly hidden from the developers.
-%The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network.
 Buffered, asynchronous and reliable communication between several software components is established by routing of messages by the broker to the specific software component pinpointed by its ID.
-%The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
 Murmex has twelve pre-defined states (eg, Initialise, Configure, Start, Stop, Proceed, Update) and a generic state for implementing custom states.
-Usually, just a few of this states are actually used in standard application.
+Usually, just a few of this states are actually used in standard applications.
 An example of a standard implementation of the Murmex state machine for the camera is shown in Fig.
@@
 Using this oberserver/observee hierarchy, it is possible to design a large and complex network of different components, running on various computers connected through a local connection or the internet while maintaining precise timing and synchronisation.
-%A special component, named ServiceManager (also based on Murmex), which must be running on each computer, allows to start executables remotely in user-defined compositions of components.
-This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but operated from one computer.
+
+%\subsection{Software organisation}
+Each hardware component in the LSFM was managed through its own software component (see supplementary information \ref{sec:murmex}).
+Since the galvo scanners and the electro-optical modulator were not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sent analog and digital waveforms to an additional intermediate component responsible for DAQ board management.
+Beyond hardware-related software, two additional software components, the Stack and Tomo components orchestrated the operation of the entire system.
+
+The Stack component was used to acquire image stacks along the detection axis, here the $z$ direction, and coordinates the Camera and the Stages components.
+Stacks are collected by continuously moving the sample along $z$ while keeping the camera acquiring in free run.
+The translation speed was calculated such that in the time needed to collect a single frame the specimen was moved by a $z$ step specified in the GUI.
+The Camera component used low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (the proprietary, non-compressed, tiff-like format from Hamamatsu) for each image stack.
+The Camera component must write data to disk with perfect synchronisation, otherwise the nominal $z$ position of each frame is no more coincident with the real $z$ position of the plane imaged.
+For this reason, the process executing the Camera code was set to highest priority.
+Additionally, the Stack component checked the timing of data production, in order to re-acquire the image stack if the camera had encountered a timing issue.
+
+The Tomo component is a high-level component which coordinated the acquisition of adjacent, parallel, partially-overlapping stacks.
+The user can specify the volume to be imaged either by inserting the minimum and maximum $x$, $y$ and $z$ coordinates of a parallelepiped or by providing a \textit{.txt} file with the coordinates of individual stacks to be collected.
+The Tomo component informs the experimenter via email when the acquisition is terminated either cleanly or through errors.
+
+All the software described here can be freely downloaded from \href{https://github.com/marcelvanthoff/Giorgio}{GitHub}.
+Due to its modular structure and of the extensive documentation, it can be easily integrated and adapted in other microscopy systems.
 
@@
 
+\newpage
+\pagebreak
+
+		\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{panel1.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:excitation} (A) Schematic of the light path.
+The galvo scanners are mounted above periscopes.
+LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter.
+Green dotted: detection path.
+(B) Oblique view of the microscope.
+A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages.
+A second breadboard is used for the camera.}
+   \end{figure}
+
+	\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{panel2.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:frame2} Schematic of sample mounting and motion.
+(A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light-sheet and the detection focal plane overlap.
+(B) The custom-made sample chamber is assembled with silicone bellows and seal rings.
+The clarified fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D).
+(E) Mounting of a clarified fluorescently labelled brain.
+The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.}
+   \end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{panel3.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:origin} Optical characterisation.
+(A) Exemplary lateral and axial intensity profiles of nanometric beads and fits to Gaussian curves.
+(B) FWHM of the Gaussian fits with confocal slit width.
+Each data point is the average of 10 bead profiles.
+(C) Signal to noise ratio (SNR) as a function of slit width.}
+\end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{panel4.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:connectivity} Schematic view of the hardware architecture of the microscope. Different kind of physical connections are depicted with different colours.} 
+   \end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{panel5.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:DataFlow} Scheme of the data flow.
+(A) Data streaming on the microscope.
+SSD: solid-state disk, RAID: redundant array of independent disks.
+Colours indicate the time-criticality (red: higher to green: lower) of each data stream.
+(B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.
+NAS: network-attached storage}
+   \end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{panel6.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:LSMdata} Whole mouse brain tomography.
+Imaging of whole transgenic mouse brain treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective.
+(A) 3D rendering of a parvalbumin-dTomato brain.
+(B) 3D rendering of a stack from PV-dTomato mouse brain, scale bar = $400 \micro m$.
+(C) High resolution insert showing axonal projections.
+Scale bar = $100 \micro m$.
+(D) Lateral and axial FWHM of the intensity profiles through single axon.
+Modified with permission from \cite{Costantini}.}
+   \end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{SOI1.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light-sheet microscope.
+AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises.
+(B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.
+(C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm.
+(D) The alignment mirror can be rotated to precisely reflect by $90\degree$.}
+   \end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{SOI2.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront.
+Right: inverted light path, a focal spot in the back aperture creates a collimated output.
+(B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.}
+   \end{figure}
+
+\begin{figure}
+   \begin{center}
+   \begin{tabular}{c}
+   %\includegraphics[width=\textwidth]{SOI3.eps}
+   \end{tabular}
+   \end{center}
+   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
+   \end{figure}
+
+%\listoffigures
 \end{spacing}

### 2015-05-13 Neurophotonics/Submitted files/manuscript_submission.tex
commit before revision process
commit after submission of revised manuscript

--- 2015-03-25 latex-style-files-spie-manuscript/manuscript_submission.tex
@@
 
-\begin{spacing}{2}   % use double spacing for rest of manuscript
+%\begin{spacing}{2}   % use double spacing for rest of manuscript
 
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame1.eps}
+   \includegraphics[width=\textwidth]{panel1.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame2.eps}
+   \includegraphics[width=\textwidth]{panel2.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame3.eps}
+   \includegraphics[width=\textwidth]{panel3.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{frame4.eps}
+   \includegraphics[width=\textwidth]{panel4.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{DataFlow.eps}
+   \includegraphics[width=\textwidth]{panel5.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{data_panel.eps}
+   \includegraphics[width=\textwidth]{panel6a.eps}
    \end{tabular}
@@
 (A) 3D rendering of a parvalbumin-dTomato brain.
-(B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$.
-(C,D,E) High resolution insert, of the stack corresponding to red boxes in B.
-Scale bar = $100 \micro m$.
+(B) 3D rendering of a stack from PV-dTomato mouse brain, scale bar = $400 \micro m$.
+(C) High resolution insert showing the axon (arrow) used for resolution estimation.
+Scale bar = $50 \micro m$.
+(D) Lateral and axial FWHM of the intensity profiles through axon indicated in C.
 Modified with permission from \cite{Costantini}.}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel3.eps}
+   \includegraphics[width=\textwidth]{SOI1.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{Panel4.eps}
+   \includegraphics[width=\textwidth]{SOI2.eps}
    \end{tabular}
@@
    \begin{tabular}{c}
-   \includegraphics[width=\textwidth]{murmex.eps}
+   \includegraphics[width=\textwidth]{SOI3.eps}
    \end{tabular}
@@
 
-\end{spacing}
+%\end{spacing}
 \end{document}
